### 2020-01-13 paper.tex
Initial Overleaf Import

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\usepackage{hyperref}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
\newtheorem{defi}[theorem]{Definition}
%
%\title{G2GML: Graph to Graph Mapping Language for Interoperable Use of RDF and Property Graphs}
\title{Graph to Graph Mapping Framework for Interoperable Use of RDF and Property Graphs}
%
\titlerunning{Graph to Graph Mapping Framework}
%\titlerunning{Interoperable Use of RDF and Property Graph}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Hirokazu Chiba\inst{1} \and Ryota Yamanaka\inst{2} \and Shota Matsumoto\inst{3}}
%
\authorrunning{H. Chiba {\itshape et al.}}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{
Database Center for Life Science, Chiba 277-0871, Japan\\
\email{chiba@dbcls.rois.ac.jp}
\and
Oracle Corporation, Bangkok 10500, Thailand\\
\email{ryota.yamanaka@oracle.com}
\and
Lifematics Inc., Tokyo 101-0041, Japan\\
\email{shota.matsumoto@lifematics.co.jp}
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
% The abstract should briefly summarize the contents of the paper in 15--250 words.
Increasing amounts of scientific and social data are described as graphs. In addition to the standardized Resource Description Framework (RDF) model, the property graph model has been attracting increasing attention in the context of graph analysis. 
However, interoperable management of such graph data is challenging due to the differences in existing models and formats depending on various implementations. Here, we redefine the property graph model incorporating the differences in existing models and propose exchangeable serialization formats for property graphs, which can be converted into specific formats for each of the databases. 
The serialization formats independent of certain database implementations will increase the interoperability of graph databases and will make it easier for users to import accumulated graph data.
We further propose a framework for mapping RDF graphs to property graphs on the basis of the Graph to Graph Mapping Language (G2GML). Using this framework, accumulated graph data described in RDF can be converted to property graphs, which can then be loaded into several graph database engines for further analysis. 
%This work provides interoperability not only between property graph formats but also between RDF and proper graphs.
%Future works include implementing and utilizing graph algorithms to make the most of the accumulated data in various analytical engines.

\keywords{RDF \and Property Graph \and Graph Database}
\end{abstract}

\section{Introduction}
% Please note that the first paragraph of a section or subsection is not indented. The first paragraph that follows a table, figure, equation etc. does not need an indent, either.

Increasing amounts of scientific and social data are described as graphs. 
As a standard data model, the standardized Resource Description Framework (RDF)~\cite{rdf} is widely used. 
% Although RDF data can be queried using the SPARQL language~\cite{sparql} in a flexible way, SPARQL is not dedicated to traversal of graphs and has a limitation in implementing graph analysis algorithms.
Recently, the property graph model~\cite{angles1,angles2} have been attracting increasing attention in the context of graph analysis; various graph database engines, including Neo4j~\cite{neo4j}, Oracle Labs PGX~\cite{pgx}, and Amazon Neptune~\cite{neptune}, adopt this model. These graph database engines support algorithms for traversing or analyzing graphs. However, currently not many datasets are consistently described in the property graph model, so the application of these powerful engines are limited.

Considering this situation, it is valuable to develop a method to transform RDF into property graphs. One of the practical issues is the lack of a standardized model for property graphs. 
Another issue is that transformation between them is not straightforward due to the differences between RDF and property graph models. 
In RDF graphs, all information is expressed as the triple (node-edge-node), whereas in property graphs, arbitrary information can be contained in each of the nodes and edges as the key-value form. 
Although this issue has been previously addressed on the basis of predefined transformations~\cite{hartig},
users still cannot control the mapping for their specific use cases.

Here, we redefine the property graph model incorporating the differences in existing models and also propose serialization formats based on the data model. We further propose a graph to graph mapping framework on the basis of the Graph to Graph Mapping Language (G2GML). Using this mapping framework, accumulated graph data described in RDF can be converted into property graphs, which can then be loaded into several graph database engines for further analysis.

\section{The Property Graph Model}
Here we define the property graph model independent of specific graph database implementations. For the purpose of interoperability, we incorporate differences in property graph models, taking into consideration multiple labels or property values for nodes and edges, as well as mixed graphs with both of directed and undirected edges. The property graph model we redefine here requires the following characteristics:

\begin{itemize}
    \item A property graph contains nodes and edges.
    \item Each of the nodes and edges can have zero or more labels.
    \item Each of the nodes and edges can have properties (key-value pairs).
    \item Each property can have multiple values.
    \item Each edge can be directed or undirected.
\end{itemize}
More formally, we define the property graph model as follows.

\begin{defi}[Property Graph Model]
\leavevmode \vspace{1mm} \\
A \emph{Property Graph} is a tuple
$PG = \langle N, E_d, E_u, S, V, P, e, l_n, l_e, p_n, p_e\rangle$, where:
\begin{enumerate}
    \item $N$ is a set of nodes.
    \item $E_d$ is a set of directed edges.
    \item $E_u$ is a set of undirected edges.
    \item $E$ is a set of edges where $E = E_d \cup E_u$.
    \item $S$ is a set of strings.
    \item $V$ is a set of values of arbitrary data types.
    \item $P$ is a set of properties. Each property has the form $p = \langle k,v \rangle$, where $k \in S$ and $v \in 2^V$.
    \item $e: E \to \langle N \times N \rangle$ is a function which yields the endpoints of each directed or undirected edge (if the edge is directed, the first node is the source and the second node is the destination).
    \item $l_n : N \to 2^S$ is a function mapping each node to its multiple labels.
    \item $l_e : E \to 2^S$ is a function mapping each edge to its multiple labels.
    \item $p_n : N \to 2^P$ is a function used to assign nodes to their multiple properties.
    \item $p_e : E \to 2^P$ is a function used to assign edges to their multiple properties.
\end{enumerate}
\end{defi}

\section{Serializing Property Graphs}
According to our definition of the property graph model, we propose serialization in flat text and JSON. The flat text format (PG) is better for human readability and line-oriented processing, while the JSON format (JSON-PG) is best used for server-client communication.

The flat text PG format has the following characteristics, and an example is given in Figure~\ref{fig:example-pg}.

\begin{itemize}
    \item Each line describes a node or an edge.
    \item All elements in each line are separated by space or tab.
    \item In each of the node lines, the first column contains the node ID.
    \item In each of the edge lines, the first three columns contain the source node ID, the direction, and the destination node ID.
    \item Each line can contain an arbitrary number of labels.
    \item Each line can contain an arbitrary number of properties (key-value pairs).
\end{itemize}

More formally, we describe the PG format in the EBNF notation as follows.

\begin{defi}[PG Format]
\leavevmode \vspace{1mm} \\
\emph{EBNF notation of the PG format.}
\begin{scriptsize}
\begin{verbatim}
    PG         ::= (Node | Edge)+
    Node       ::= NODE_ID Labels Properties NEWLINE
    Edge       ::= NODE_ID Direction NODE_ID Labels Properties NEWLINE
    Labels     ::= Label*
    Properties ::= Property*
    Label      ::= ':' STRING
    Property   ::= STRING ':' Value
    Value      ::= STRING | NUMBER
    Direction  ::= '--' | '->'
\end{verbatim}
\end{scriptsize}
\end{defi}

Next, we describe the JSON-PG format which follows the JSON syntax in addition to the above definition of the property graph model. The JSON-PG format has the following characteristics, and an example of the format is shown in Figure~\ref{fig:example-json}. It is to be noted that, whereas the set of labels or property values are represented as arrays in JSON, those elements are supposed to have no specific order according to the property graph model.

\begin{itemize}
    \item Nodes and edges are listed under \texttt{nodes} and \texttt{edges} elements, respectively.
    \item Edge direction is defined with the boolean element \texttt{undirected}. By default it is false (directed).
    \item Labels are listed under the \texttt{labels} element.
    \item Properties (key-value pairs) are listed under the \texttt{properties} element.
\end{itemize}

Furthermore, we have implemented command-line tools to convert between PG and JSON-PG, as well as to transform them into formats for well-known graph databases such as Neo4j, Oracle Labs PGX, and Amazon Neptune. The practical use cases of our tools demonstrate that the proposed data model and formats have the capability to describe property graph data begin used in existing graph databases (see \url{https://github.com/g2glab/pg}).

\begin{figure}[!t]
\begin{scriptsize}
\begin{verbatim}
# NODES
101  :Person  name:Alice  age:15  country:"United States"
102  :Person  :Student  name:Bob  country:Japan  country:Germany

# EDGES
101 -- 102  :sameSchool  :sameClass  since:2012
102 -> 101  :likes  since:2015
\end{verbatim}
\end{scriptsize}
\caption{Example of PG}
\label{fig:example-pg}
\end{figure}

\begin{figure}[!t]
\begin{scriptsize}
\begin{verbatim}
{
  "nodes":[
    {
     "id":101,
     "labels":["Person"],
     "properties":{"name":["Alice"], "age":[15], "country":["United States"]}
    },
    {
     "id":102,
     "labels":["Person", "Student"],
     "properties":{"name":["Bob"], "country":["Japan", "Germany"]}
    }
  ],https://ja.overleaf.com/project/5d6e87b11a254100014e487d
  "edges":[
    {
     "from":101,
     "to":102,
     "undirected":true,
     "labels":["sameSchool", "sameClass"],
     "properties":{"since":[2012]}
    },
    {
     "from":102,
     "to":101,
     "labels":["likes"],
     "properties":{"since":[2015]}
    }
  ]
}
\end{verbatim}
\end{scriptsize}
\caption{Example of JSON-PG}
\label{fig:example-json}
\end{figure}

\section{Mapping RDF Graphs to Property Graphs}

Here we describe a framework for mapping RDF graphs to property graphs.
Figure~\ref{fig:dataflow} shows the overview of the framework.
In this framework, users can specify mappings from RDF to property graphs in G2GML.
This mapping is processed by a tool called G2G Mapper, which was implemented by authors (available on \url{https://github.com/g2glab/g2g}). This tool can convert RDF data retrieved from SPARQL endpoints or from local files into PG format and then into specific formats for each of the database implementations.

The G2GML is a declarative language which consists of pairs of RDF graph patterns and property graph patterns. 
An intuitive meaning of a G2GML description is mapping RDF subgraphs that matches the specified patterns to specified components of property graphs.

%In this section, we briefly explain the syntax of G2GML with an example.

\begin{figure}
\center
\includegraphics[width=1.0\textwidth]{dataflow.png}
\caption{Overview of the graph to graph mapping}
\label{fig:dataflow}
\end{figure}

%\subsection{Usecase}

Figure~\ref{fig:conversion} schematically shows an example of the G2G mapping to convert RDF data retrieved from DBpedia into property graph data. 
When we focus on a relationships where two musicians (\texttt{?m1} and \texttt{?m2}) belong to the same group, such information can be represented in the property graph shown in the right side of the figure.

\begin{figure}
\center
\includegraphics[width=1.0\textwidth]{example.jpg}
\caption{Schematic example of the graph to graph mapping}
\label{fig:conversion}
\end{figure}

The mapping rule for the above example is specified in G2GML shown in Figure~\ref{fig:g2gml}. Following the prefix declaration for URIs used to write mappings, each mapping pattern is defined by a combination of a property graph pattern in an unindented line and an RDF graph pattern in indented lines. The property graph pattern is specified in a syntax like Cypher (the query language of Neo4j), whereas the RDF graph pattern is specified using a SPARQL code pattern. 
Variables in each mapping pattern are associated by their names across the different data models. 
In G2G mapping, execution of the edge mappings is dependent on the node mappings, which means that edges are generated iff both nodes' patterns and edges' patterns are matched with RDF graphs. 
The example contains node mapping for \texttt{Musician} entities and edge mapping for \texttt{same\_group} relationships.
In each of the specified property graph patterns, \texttt{\{m, n, h\}} and \texttt{\{m1, m2, n, s\}} are used as variables to reconstruct resources and literals extracted from RDF graphs. 
%In this example, RDF literals are mapped to property values.
%As a result, the specified RDF resources are reconstructed as nodes and edges in property graphs, while literals are mapped to property values.

%# Prefixes
\begin{figure}[!t]
\vspace{2mm}
\begin{scriptsize}
\begin{verbatim}
PREFIX rdf: <http://www.w3.org/1999/02/22-rdf-syntax-ns#>
PREFIX rdfs: <http://www.w3.org/2000/01/rdf-schema#>
PREFIX schema: <http://schema.org/>
PREFIX dbo: <http://dbpedia.org/ontology/>
PREFIX foaf: <http://xmlns.com/foaf/0.1/>

# Node mapping
(m:Musician {name:n, hometown:h})                            # PG Pattern
    ?m rdf:type foaf:Person , dbo:MusicalArtist .            # RDF Pattern
    ?m rdfs:label ?n . FILTER(lang(?n) = "en") .
    OPTIONAL { ?m dbo:hometown / rdfs:label ?h . FILTER(lang(?h) = "en") }

# Edge mapping
(m1:Musician)-[:same_group {name:n, since:s}]-(m2:Musician)  # PG Pattern
    ?g rdf:type schema:MusicGroup ;                          # RDF Pattern
       dbo:bandMember ?m1 , ?m2 . FILTER(?m1 != ?m2)
    OPTIONAL { ?g rdfs:label ?n . FILTER(lang(?n) = "en")}
    OPTIONAL { ?g dbo:activeYearsStartYear ?s }
\end{verbatim}
\end{scriptsize}
\caption{Example of G2GML}
\label{fig:g2gml}
\end{figure}

\begin{figure}[!t]
\vspace{2mm}
\begin{scriptsize}
\begin{verbatim}
# SPARQL
PREFIX rdf: <http://www.w3.org/1999/02/22-rdf-syntax-ns#>
PREFIX rdfs: <http://www.w3.org/2000/01/rdf-schema#>
PREFIX schema: <http://schema.org/>
PREFIX dbo: <http://dbpedia.org/ontology/>
PREFIX foaf: <http://xmlns.com/foaf/0.1/>

SELECT DISTINCT ?nam1 ?nam2
WHERE {
    ?mus1 rdf:type foaf:Person , dbo:MusicalArtist .
    ?mus2 rdf:type foaf:Person , dbo:MusicalArtist .
    ?mus1 rdfs:label ?nam1 . FILTER(lang(?nam1) = "ja") .
    ?mus1 rdfs:label ?nam2 . FILTER(lang(?nam2) = "ja") .
    ?grp a schema:MusicGroup ;
         dbo:bandMember ?mus1 , ?mus2 .
    FILTER(?mus1 != ?mus2)
}

# PGQL
SELECT DISTINCT m1.name, m2.name WHERE (m1)-[:same_group]-(m2)
\end{verbatim}
\end{scriptsize}
\caption{Example of SPARQL and PGQL queries}
\label{fig:sparql}
\end{figure}

Figure~\ref{fig:sparql} shows the SPARQL query to retrieve the pairs of musicians who are in the same group. After the G2G mapping, we can load the generated property graph data into graph databases, such as Oracle Labs PGX, and the query can be written in PGQL~\cite{pgql} (the query language of PGX).

\section{Discussion}
Recently, the graph data have been attracting increasing attention, leading to plethora of database implementations. 
%So far, there have been implementations of graph databases on the basis of various data models and query languages. 
%So far, there are differences in data models and query languages based on the implementations of graph databases.
So far, there have been different data models and query languages for these graph database implementations.
Thus, there have been community-based activities for standardizing graph query language for interoperable use of property graph databases~\cite{angles3}. Similarly, standardization of the property graph model of various database implementations will enhance the interoperable use of graph data. In fact, there is a need for graph standardization in the community and graph data standardization was recently discussed in a W3C workshop~\cite{w3c}; there were similar proposals for property graph model and serialization~\cite{tomaszuk} including ours and it is noteworthy that the two independent approaches have converged to the similar solution. 
In particular, our serialization has implementation for some of the major database engines and also has a potential to cover further various implementations. %However, it requires developing a converter for each format. 
%This work provides a basis of an interoperable platform for creating, exchanging, and utilizing property graph data.
%Specifically, our model and serialization are independent of specific implementations and provides a basis 
%Specifically, it provides the basis for mapping of our G2GML mapping. 
The serialization formats independent of certain database implementations will increase the interoperability of graph databases and will make it easier for users to import accumulated graph data.
%In G2G mapping, PG format works as a gateway from RDF to property graphs.

As a preceding work for converting existing data into graph data, there was an effort to convert relational to graph databases~\cite{virgilio1}. 
However, given that RDF has now prevailed as a standardized data model in scientific communities, considering the mapping on the basis of the RDF model is crucial. There have been discussions about the interoperability of RDF and property graphs~\cite{hartig,angles4,das,thakkar} and efforts were made to develop methods to convert RDF into property graphs~\cite{tomaszuk1,virgilio}. However, considering the flexibility of what kind of information can be expressed by each edge in property graphs, a novel method for controlling the mapping is necessary.
To the best of our knowledge, this is the first attempt to develop a framework for controlled mapping between RDF and property graphs. 
Notably, the G2GML we have designed is a declarative mapping language. 
As a merit of the declarative description, we can concentrate on the core logic of mappings. In the sense that the mapping process generates new graph data on the basis of existing graph data, it has close relation to the semantic inference. Similar concept can be found in SPARQL CONSTRUCT queries. While the SPARQL CONSTRUCT clause defines mapping on the same data model, G2GML defines mapping between different data models. 
%Currently, it is limited to the mapping from RDF to property graphs, it can be extended to the mapping from property graph to RDF. However, if mapping includes the SPARQL pattern that are not declarative, it is not applicable for generating RDF triples.
Thus, G2GML can be considered as a specific extension of the SPARQL CONSTRUCT clause for generation or inference of property graph data.
%Future works include further analysis of the converted graph data on the database engines adopting the property graph model.

\section{Conclusion}
Here we redefined the property graph model independent of specific graph database implementations and also proposed serialization formats based on the data model.
We further designed G2GML for mapping RDF graphs to property graphs and implemented a converter on the basis of G2GML.
Our data model and mapping framework will increase the interoperability of existing graph databases and make it easier for users to create, exchange, and utilize graph data.

\section*{Acknowledgements}
Part of the work was conducted through the BioHackathon meetings (\url{http://www.biohackathon.org}). We thank Yuka Tsujii for helping creating figures. We thank Ramona Roess for careful review of the manuscript and useful comments.

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}

\bibitem{rdf}
RDF 1.1 Concepts and Abstract Syntax, W3C Recommendation 25 February 2014. \url{http://www.w3.org/TR/rdf11-concepts/}

%\bibitem{sparql}
%SPARQL 1.1 Query Language, W3C Recommendation 21 March 2013. \url{http://www.w3.org/TR/sparql11-query/}

\bibitem{angles1}
Angles, R., Gutierrez, C.: An introduction to Graph Data Management. arXiv preprint arXiv:1801.00036 (2017)

\bibitem{angles2}
Angles, R., Arenas, M., Barceló, P., Hogan, A., Reutter, J., Vrgoc, D.: Foundations of Modern Query Languages for Graph Databases. ACM Computing Surveys (CSUR), 50(5), 68. (2017)

\bibitem{neo4j}
The Neo4j Graph Platform. \url{https://neo4j.com/}

\bibitem{pgx}
Oracle Labs Parallel Graph AnalytiX (PGX). \url{https://www.oracle.com/technetwork/oracle-labs/parallel-graph-analytix/overview/index.html}

\bibitem{neptune}
Amazon Neptune. \url{https://aws.amazon.com/neptune/}

\bibitem{hartig}
Hartig, O.: Reconciliation of RDF* and property graphs. arXiv preprint arXiv:1409.3288 (2014)

\bibitem{pgql}
van Rest, O., Hong, S., Kim, J., Meng, X., Chafi, H.: PGQL: a property graph query language. In Proceedings of the Fourth International Workshop on Graph Data Management Experiences and Systems, p. 7. ACM (2016)

\bibitem{angles3}
Angles, R., Arenas, M., Barceló, P., Boncz, P., Fletcher, G., Gutierrez, C., {\itshape et al.}: G-CORE: A core for future graph query languages. In Proceedings of the 2018 International Conference on Management of Data, pp. 1421--1432. (2018)

\bibitem{w3c}
W3C Workshop on Web Standardization for Graph Data. \url{https://www.w3.org/Data/events/data-ws-2019/}

\bibitem{tomaszuk}
Tomaszuk D., Angles R., Szeremeta L., Litman K., Cisterna D.:
Serialization for property graphs. International Conference: Beyond Databases, Architectures and Structures, pp. 57--69. (2019)

\bibitem{virgilio1}
De Virgilio, R., Maccioni, A., Torlone, R.: Converting relational to graph databases. In First International Workshop on Graph Data Management Experiences and Systems, p. 1. ACM (2013)

\bibitem{angles4}
Angles, R., Thakkar, H., Tomaszuk, D.: RDF and Property Graphs Interoperability: Status and Issues. Proceedings of the 13th Alberto Mendelzon International Workshop on Foundations of Data Management. (2019)

\bibitem{das}
Das, S., Srinivasan, J., Perry, M., Chong, E. I., Banerjee, J.: A Tale of Two Graphs: Property Graphs as RDF in Oracle. In EDBT, pp. 762--773. (2014)

\bibitem{thakkar}
Thakkar, H., Punjani, D., Keswani, Y., Lehmann, J., Auer, S.: A Stitch in Time Saves Nine--SPARQL querying of Property Graphs using Gremlin Traversals. arXiv preprint arXiv:1801.02911 (2018)

\bibitem{tomaszuk1}
Tomaszuk, D.: RDF data in property graph model. In Research Conference on Metadata and Semantics Research, pp. 104--115. (2016)

\bibitem{virgilio}
De Virgilio, R.: Smart RDF data storage in graph databases. In 2017 17th IEEE/ACM International Symposium on Cluster, Cloud and Grid Computing, pp. 872--881. IEEE (2017)

% \bibitem{ref_article1}
% Author, F.: Article title. Journal \textbf{2}(5), 99--110 (2016)

% \bibitem{ref_lncs1}
% Author, F., Author, S.: Title of a proceedings paper. In: Editor,
% F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
% Springer, Heidelberg (2016). \doi{10.10007/1234567890}

% \bibitem{ref_book1}
% Author, F., Author, S., Author, T.: Book title. 2nd edn. Publisher,
% Location (1999)

% \bibitem{ref_proc1}
% Author, A.-B.: Contribution title. In: 9th International Proceedings
% on Proceedings, pp. 1--2. Publisher, Location (2010)

% \bibitem{ref_url1}
% LNCS Homepage, \url{http://www.springer.com/lncs}. Last accessed 4
% Oct 2017
\end{thebibliography}
\end{document}

### 2020-01-27 paper.tex
Change title
Updates from Overleaf

@@
 %
-%\title{G2GML: Graph to Graph Mapping Language for Interoperable Use of RDF and Property Graphs}
-\title{Graph to Graph Mapping Framework for Interoperable Use of RDF and Property Graphs}
+\title{G2G: Graph to Graph Mapping Framework for Interoperable Use of RDF and Property Graphs}
 %
-\titlerunning{Graph to Graph Mapping Framework}
+\titlerunning{G2G: Graph to Graph Mapping Framework}
 %\titlerunning{Interoperable Use of RDF and Property Graph}
@@
 Using this mapping framework, accumulated graph data described in RDF can be converted into property graphs, which can then be loaded into several graph database engines for further analysis.
+We will show several use cases where publicly available RDF data is extracted and convert to property graphs and also evaluate the performance.
+This work provides the foundation of interoperability of knowledge graphs.
 
-\section{The Property Graph Model}
+The contribution of this paper is 1) development of Graph to Graph Mapping Lauguage 2) proposal of common propergy graph model and serialization 3) development of G2G mapper 4) construction of knowledge graph resources in a common format as Graph Archive.
+
+%%%%%%%%%%%%%%%%%%%%%%%
+\section{G2G Framework}
+
+\subsection{Overview}
+
+Here we illustrate the overview of the framework.
+G2G is framework to describe mapping between RDF and property graphs for interoperable use of them. In this framework, users can specify mappings from RDF to property graphs in G2GML.
+This mapping is processed by a tool called G2G Mapper, which was implemented by authors (available on \url{https://github.com/g2glab/g2g}).
+This tool can convert RDF data retrieved from SPARQL endpoints or from local files into PG format and then into specific formats for each of the database implementations.
+
+The G2GML is a declarative language which consists of pairs of RDF graph patterns and property graph patterns. 
+An intuitive meaning of a G2GML description is mapping RDF subgraphs that matches the specified patterns to specified components of property graphs.
+
+As an entry point to property graph, we define the Property Graph format, which is based on the Property Graph model.
+
+%%%%%%%%%%%%%%%%%%
+\subsection{G2GML}
+
+G2GML is a declative laugage, where patterns of RDF and property graphs are described. RDF pattern is described using SPARQL pattern, and property graph pattern is described using Cypher pattern.
+
+\subsubsection{Preliminaries}
+
+An RDF triple $(s, p, o)$ is an element of $(I \cup B) \times I \times (I \cup B \cup L)$ where $I$, $L$ and $B$ are a set of IRIs, a set of literals and a set of blank nodes, which are considered pairwise disjoint.
+In this paper, an RDF triple is simply called a triple.
+For a triple $(s, p, o)$, $s$ is called the subject, $p$ the predicate and $o$ the object.
+An RDF graph is defined as a finite set of triples.
+
+\subsubsection{G2GML}
+G2GML describes maps from RDF graphs to Property graphs.
+RDF graph pattern yields solution sets of SPARQL, that is, variables and bindings.
+Resultant nodes are generated by embedding bindings to its corresponding location.
+Values bound in SPARQL solutions can be used only as labels or values of properties.
+
+In this paper, we call maps written in G2GML as \textit{G2G maps}.
+A \textit{G2G map} consists of one or more \textit{node maps} and \textit{edge maps}.
+A \textit{node map} is a function that maps from an RDF graph to a set of \textit{PG nodes}. 
+An \textit{edge map} is a function that maps from an RDF graph to a set of \textit{PG edges}.
+
+A node map can be described as a pair of (i) a template of a PG node and (ii) an RDF graph pattern that can be written as \textit{GroupGraphPattern} in SPARQL syntax (see EBNF notation of SPARQL grammer~\cite{sparql}).
+
+\begin{defi}[PG node template]
+%\leavevmode \vspace{1mm} \\
+\emph{Syntax of PG node template.}
+\begin{scriptsize}
+\begin{verbatim}
+<node_template> ::= "(" node_resource  ":" label  ("{" <property_list> "}")? ")"
+<property_list> ::= <property> "," <property_list> | <property>
+<property> ::= key":" value
+\end{verbatim}
+\end{scriptsize}
+\end{defi}
+
+A PG node template is interpreted as a map from a solution of SPARQL query to a tuple of a node, its label and its properties.
+A variable bound to \texttt{node\_resource} is used as the primary key of the map.
+Other variables bound to \texttt{value} are concatenated into an array.
+
+\begin{defi}[PG edge template]
+%\leavevmode \vspace{1mm} \\
+\emph{Syntax of PG edge template.}
+\begin{scriptsize}
+\begin{verbatim}
+<edge_template> ::= "(" src_resource  ":" src_label ")" - "[" edge_resource?  ":" edge_label  ("{" 
+<property_list> "}")? ")" (-> | -) "(" dst_resource  ":" dst_label ")"
+\end{verbatim}
+\end{scriptsize}
+\end{defi}
+
+%%%%%%%%%%%
+\subsection{The Property Graph Model}
 Here we define the property graph model independent of specific graph database implementations.
@@
 
-\section{Serializing Property Graphs}
+\subsection{Serialization of Property Graphs}
 According to our definition of the property graph model, we propose serialization in flat text and JSON.
@@
 
-\section{Mapping RDF Graphs to Property Graphs}
+%%%%%%%%%%%%
+\subsection{Minimal Exmples}
+Figure~\ref{fig:example-g2g} shows the small example of G2G mapping from RDF data to PG data. This example shows the following five types of the typical mapping.
+
+\begin{itemize}
+    \item Resource to node: In the line 2-4, the RDF resources with type \texttt{:Person} are mapped into PG nodes using their URIs as node IDs.
+    \item Datatype property to node property: In the line 2-4, the RDF datatype property \texttt{:name} is mapped into PG node property key \texttt{name}.
+The literal objects 'Alice' and 'Bob' are mapped into the node property values.
+    \item Object property to edge: In the line 5-6, the RDF object property \texttt{:likes} is mapped into PG edge \texttt{follows}. 
+    \item Resource to edge: In the line 7-10, the RDF resource with type \texttt{:Follow} is mapped into PG edge \texttt{follows}. 
+    \item Datatype property to edge property: In the line 7-10, the RDF datatype property \texttt{:since} is mapped into PG edge property \texttt{since}.
+The literal objects \texttt{2017} is mapped into the edge property value.
+\end{itemize}
+
+\begin{figure}[!t]
+\begin{scriptsize}
+\begin{verbatim}
+@prefix : <http://example.org/> .
+:person1 a :Person ;
+         :name 'Alice' .
+:person2 a :Person ;
+         :name 'Bob' .
+:person1 :likes :person2 .
+[] a :Follow ;
+   :follower :person1 ;
+   :followed :person2 ;
+   :since 2017 .
+\end{verbatim}
+\end{scriptsize}
+\caption{Example of input RDF data}
+\label{fig:example-rdf}
+\end{figure}
+
+\begin{figure}[!t]
+\begin{scriptsize}
+\begin{verbatim}
+PREFIX : <http://example.org/>
+(p:Person {name:n})
+    ?p a :Person .
+    ?p :name ?n .
+(p1:Person)-[:likes]->(p2:Person)
+    ?p1 :likes ?p2 .
+(p1:person)-[:follows {since:s}]->(p2:person)
+    ?f :follower ?p1 ;
+       :followed ?p2 ;
+       :since ?s .
+\end{verbatim}
+\end{scriptsize}
+\caption{Example of G2G mapping definition}
+\label{fig:example-g2g}
+\end{figure}
+
+\begin{figure}[!t]
+\begin{scriptsize}
+\begin{verbatim}
+"http://example.org/person1" :person name:Alice
+"http://example.org/person2" :person name:Bob
+"http://example.org/person1" -> "http://example.org/person2" :likes
+"http://example.org/person1" -> "http://example.org/person2" :follows since:2017
+\end{verbatim}
+\end{scriptsize}
+\caption{Example of output PG data}
+\label{fig:example-pg}
+\end{figure}
+
+\begin{figure}
+\center
+\includegraphics[width=0.5\textwidth]{pg_example5.png}
+\caption{Example of created PG}
+\label{fig:pg_example5}
+\end{figure}
+
+%%%%%%%%%%%
+\subsection{Mapping Details}
+The G2G mapping based on G2GML is generally intuitive as it is shown above, however, there are several discussions about the details of mapping.
+
+\subsubsection{Multi Edges}
+When there are multiple information of potential edges between the same pair of resources in RDF.
+
+\begin{figure}[!t]
+\begin{scriptsize}
+\begin{verbatim}
+@prefix : <http://example.org/> .
+:person1 a :Person ;
+         :name 'Alice' .
+:person2 a :Person ;
+         :name 'Bob' .
+[] a :Follow ;
+   :follower :person1 ;
+   :followed :person2 ;
+   :since 2017 .
+[] a :Follow ;
+   :follower :person1 ;
+   :followed :person2 ;
+   :since 2018 .
+\end{verbatim}
+\end{scriptsize}
+\caption{Example of input RDF data (multi edges)}
+\label{fig:example-rdf2}
+\end{figure}
+
+\begin{figure}[!t]
+\begin{scriptsize}
+\begin{verbatim}
+"http://example.org/person1" :Person name:Alice
+"http://example.org/person2" :Person name:Bob
+"http://example.org/person1" -> "http://example.org/person2" :follows since:2017
+"http://example.org/person1" -> "http://example.org/person2" :follows since:2018
+\end{verbatim}
+\end{scriptsize}
+\caption{Example of output PG data (multi edges)}
+\label{fig:example-pg2}
+\end{figure}
+
+\subsubsection{List of Property Values}
+PG property can have multiple values. When the same data property is put multiple times on a resource, the values are assumed to be the members of a list.
+
+\begin{figure}[!t]
+\begin{scriptsize}
+\begin{verbatim}
+
+@prefix : <http://example.org/> .
+:person1 a :Person ;
+         :name 'Alice' ;
+         :name 'Allie' .
+:person2 a :Person ;
+         :name 'Bob' .
+[] a :Follow ;
+   :follower :person1 ;
+   :followed :person2 ;
+   :since 2017 ;
+   :since 2018 .
+
+\end{verbatim}
+\end{scriptsize}
+\caption{Example of input RDF data (list of property values)}
+\label{fig:example-rdf3}
+\end{figure}
+
+\begin{figure}[!t]
+\begin{scriptsize}
+\begin{verbatim}
+
+"http://example.org/person1" :Person name:Alice name:Allie
+"http://example.org/person2" :Person name:Bob
+"http://example.org/person1" -> "http://example.org/person2" :follows since:2017 since:2018
+
+\end{verbatim}
+\end{scriptsize}
+\caption{Example of output PG data (list of property values)}
+\label{fig:example-pg3}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{G2G Mapper}
+
+G2G mapper is implemented in JavaScript, and can be executed using Node.js in command line.
+
+\texttt{g2g musician.g2g http://dbpedia.org/sparql}
+
+\noindent where the first argument is G2GML mapping file and the second argument is target SPARQL endpoint from which to extract RDF data.
+
+Also, demonstration cite of G2G mapper is available (Figure~\ref{fig:sandbox}).
+
+\begin{figure}
+\center
+\includegraphics[width=1.0\textwidth]{sandbox.png}
+\caption{G2G sandbox}
+\label{fig:sandbox}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%
+\section{Use Cases}
+
+We  present several use cases to show the usefulness of G2G mapping framework, where we use publicly available open data available in RDF through SPARQL endpoint.
+
+Figure~\ref{fig:dataflow} shows the overview of the mapping.
+In this framework, users can specify mappings from RDF to property graphs in G2GML.
+This mapping is processed by a tool called G2G Mapper, which was implemented by authors (available on \url{https://github.com/g2glab/g2g}).
+This tool can convert RDF data retrieved from SPARQL endpoints or from local files into PG format and then into specific formats for each of the database implementations.
+
+The G2GML is a declarative language which consists of pairs of RDF graph patterns and property graph patterns. 
+An intuitive meaning of a G2GML description is mapping RDF subgraphs that matches the specified patterns to specified components of property graphs.
+
+\begin{figure}
+\center
+\includegraphics[width=1.0\textwidth]{dataflow.png}
+\caption{Overview of the mapping from RDF to property graph}
+\label{fig:dataflow}
+\end{figure}
+
+\subsection{Using Wikidata}
+
+Here we present use case of for Wikidata.
+Wikidata is a useful source of biological open data, and it is available in the form of RDF through the SPARQL interface.
+
+In Wikidata, each disease is associated with zero or more genes and drugs.
+The subset of Wikidata can be extracted using G2G framework by writing a mapping file in G2GML (see the following list).
+Here, we focus on human genes. So we specified the necessary conditions in G2GML.
+Each entity of ‘Q12136: disease’ can have property ‘P2176: drug used for treatment’, thereby linked to items of ‘Q12140: medication’.
+Also, each disease can have property ‘P2293: genetic association’, thereby linked to items of ‘Q7186: gene’.
+
+The numbers of obtained entities are as follows.
+
+4689 diseases
+4495 human genes
+1285 drugs
+
+The following figure shows the schematic relationships between those entities.
+
+\begin{figure}
+\center
+\includegraphics[width=0.7\textwidth]{wikidata_schema.png}
+\caption{Schematic relation of Wikidata entities}
+\label{fig:wikidata_schema.png}
+\end{figure}
+
+\begin{figure}[!t]
+\vspace{2mm}
+\begin{scriptsize}
+\begin{verbatim}
+
+PREFIX wd: <http://www.wikidata.org/entity/>
+PREFIX wdt: <http://www.wikidata.org/prop/direct/>
+
+(g:HumanGene {symbol: s})
+    ?g wdt:P31 wd:Q7187 ;      # instance of gene
+       wdt:P703 wd:Q15978631 ; # found in taxon Homo sapiens
+       wdt:P353 ?s .           # HGNC gene symbol
+
+(d:Disease {name: n})
+    ?d wdt:P31 wd:Q12136 ;     # instance of disease
+       rdfs:label ?l .
+    FILTER(lang(?l) = "en")
+    BIND(str(?l) AS ?n)
+
+(m:Drug {name: n})
+    ?m wdt:P31 wd:Q12140 ;     # instance of medication
+       rdfs:label ?l .
+    FILTER(lang(?l) = "en")
+    BIND(str(?l) AS ?n)
+
+(d:Disease)-[:hasAssociatedGene]->(g:HumanGene)
+    ?d wdt:P2293 ?g .          # genetic association
+
+(d:Disease)-[:hasDrug]->(m:Drug)
+    ?d wdt:P2176 ?m .          # drug used for treatment
+
+\end{verbatim}
+\end{scriptsize}
+\caption{G2GML for Wikidata extraction}
+\label{fig:g2gml_wikidata}
+\end{figure}
+
+\begin{figure}
+\center
+\includegraphics[width=1.0\textwidth]{neo4jexample2.png}
+\caption{Visualization on Neo4j}
+\label{fig:neo4jexample2.png}
+\end{figure}
+
+\subsection{Using DBpedia}
 
@@
 %In this section, we briefly explain the syntax of G2GML with an example.
-
-\begin{figure}
-\center
-\includegraphics[width=1.0\textwidth]{dataflow.png}
-\caption{Overview of the graph to graph mapping}
-\label{fig:dataflow}
-\end{figure}
 
@@
 
-\section{Discussion}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Evaluation}
+
+% The goal of our evaluation is to observe the impact the number of the nodes and edges on the performance and
+% analyzing its scalability when the size of the datset increases.
+% \begin{itemize}
+% \item Q1) : Is the runtime affected when more nodes are added?
+% \item Q2) : Does it scale to a larger dataset?
+% \item Q3) : How does it scale when adding a larger number of datasets?
+% \end{itemize}
+
+\subsubsection{Graph Archive}
+We created several G2GML mappings to extract public RDF from endpoint and construct knowledge graphs in PG format and resulting knowledge graphs as Graph Archive.
+
+In the listed knowledge graphs, we compared the number of nodes and edges between RDF and property graphs.
+
+\section{Related Work}
 Recently, the graph data have been attracting increasing attention, leading to plethora of database implementations. 
@@
 
+A previous work compared performance of Blazegraph and Neo4j. They concluded that RDF has advantage in terms of performance and interoperability.
+
 \section{Conclusion}
@@
 
-%\bibitem{sparql}
-%SPARQL 1.1 Query Language, W3C Recommendation 21 March 2013. \url{http://www.w3.org/TR/sparql11-query/}
+\bibitem{sparql}
+SPARQL 1.1 Query Language, W3C Recommendation 21 March 2013. \url{http://www.w3.org/TR/sparql11-query/}
 
@@
 
+\bibitem{Alocci}
+Alocci, D., Mariethoz, J., Horlacher, O., Bolleman, J.
+T., Campbell, M.
+P., & Lisacek, F.
+(2015).
+Property graph vs RDF triple store: A comparison on glycan substructure search.
+PloS one, 10(12), e0144578.
+
 % \bibitem{ref_article1}

### 2020-02-08 paper.tex
Updates from Overleaf

@@
 %
-\title{G2G: Graph to Graph Mapping Framework for Interoperable Use of RDF and Property Graphs}
+\title{G2GML: Graph to Graph Mapping Language for Bridging RDF and Property Graphs}
 %
-\titlerunning{G2G: Graph to Graph Mapping Framework}
+\titlerunning{G2GML: Graph to Graph Mapping Lanugage}
 %\titlerunning{Interoperable Use of RDF and Property Graph}
@@
 % The abstract should briefly summarize the contents of the paper in 15--250 words.
-Increasing amounts of scientific and social data are described as graphs.
-In addition to the standardized Resource Description Framework (RDF) model, the property graph model has been attracting increasing attention in the context of graph analysis.
+How can we maximize the value of accumulated RDF data?
+Although increasing amounts of scientific and social data are described as RDF, their use cases are still limited.
+Allowing access to the RDF datasets through various interface beyond the SPARQL interface will be expected.
+Importing the RDF datasets into various graph analysis engines will increase the values of the datasets.
 However, interoperable management of such graph data is challenging due to the differences in existing models and formats depending on various implementations.
@@
 
-Increasing amounts of scientific and social data are described as graphs. 
-As a standard data model, the standardized Resource Description Framework (RDF)~\cite{rdf} is widely used. 
+Increasing amounts of scientific and social data are published in the form of Resource Description Framework (RDF)~\cite{rdf}.
+It now constitutes a large open data cloud.
+DBpedia~\cite{dbpedia} and Wikidata~\cite{wikidata} are good example.
+SPARQL~\cite{sparql} is a standardized interface for RDF.
+However, the usecases through thouse interface are still limited.
+Although the standardized format and interface contributed the integrated large data could, further interface is expected to maximize the value of RDF datasets.
 % Although RDF data can be queried using the SPARQL language~\cite{sparql} in a flexible way, SPARQL is not dedicated to traversal of graphs and has a limitation in implementing graph analysis algorithms.
@@
 
-The contribution of this paper is 1) development of Graph to Graph Mapping Lauguage 2) proposal of common propergy graph model and serialization 3) development of G2G mapper 4) construction of knowledge graph resources in a common format as Graph Archive.
+The contributions of this papers are 1) development of Graph to Graph Mapping Language 2) proposal of common property graph model and serialization 3) development of G2G mapper 4) construction of knowledge graph resources in a common format as Graph Archive.
 
 %%%%%%%%%%%%%%%%%%%%%%%
-\section{G2G Framework}
+\section{G2G: Graph to Graph Mapping Framework}
 
@@
 Here we illustrate the overview of the framework.
-G2G is framework to describe mapping between RDF and property graphs for interoperable use of them. In this framework, users can specify mappings from RDF to property graphs in G2GML.
+G2G is a framework to describe mapping between RDF and property graphs for interoperable use of them. In this framework, users can specify mappings from RDF to property graphs in G2GML.
 This mapping is processed by a tool called G2G Mapper, which was implemented by authors (available on \url{https://github.com/g2glab/g2g}).
@@
 
-G2GML is a declative laugage, where patterns of RDF and property graphs are described. RDF pattern is described using SPARQL pattern, and property graph pattern is described using Cypher pattern.
+G2GML is a declarative language, where patterns of RDF and property graphs are described. RDF pattern is described using SPARQL pattern, and property graph pattern is described using Cypher pattern.
 
@@
 G2GML describes maps from RDF graphs to Property graphs.
-RDF graph pattern yields solution sets of SPARQL, that is, variables and bindings.
-Resultant nodes are generated by embedding bindings to its corresponding location.
-Values bound in SPARQL solutions can be used only as labels or values of properties.
 
@@
 
-A node map can be described as a pair of (i) a template of a PG node and (ii) an RDF graph pattern that can be written as \textit{GroupGraphPattern} in SPARQL syntax (see EBNF notation of SPARQL grammer~\cite{sparql}).
+A node map is described as a pair of (i) a template of a PG node and (ii) an RDF graph pattern that can be written as \textit{GroupGraphPattern} in SPARQL syntax (see EBNF notation of SPARQL grammer~\cite{sparql}).
 
@@
 
-A PG node template is interpreted as a map from a solution of SPARQL query to a tuple of a node, its label and its properties.
-A variable bound to \texttt{node\_resource} is used as the primary key of the map.
-Other variables bound to \texttt{value} are concatenated into an array.
+A PG node template specifies nodes, labels and properties to be generated by the map.
+A \texttt{node\_resource} specifies ID of the generated node, which is replaced by the resource retrieved by RDF graph.
+A \texttt{label} specifies the label of the resultant node.
+A \texttt{label} also works as the name of node map which is referred from other edge maps.
+A \texttt{property} is a pair of \texttt{key} and \texttt{value} that describes properties of nodes.
+Note that \texttt{node\_resource} and \texttt{value} are  placeholders of the map replaced by resources or literals retrieved from RDF graphs.
+On the other hand, \texttt{label} and \texttt{key} must be fixed value.
+
+RDF graph pattern specifies which resources should be mapped to nodes of property graphs.
+Resources match with these pattern yield solution sets of SPARQL SELECT query, that is, variables and bindings.
+The solution sets are mapped to nodes embedding bindings to its corresponding location according to the preciding node map.
+
+The URL bound to \texttt{node\_resource} used as the primary key of the map.
+Other resources or literals bound to \texttt{value} are concatenated into an array in the manner of \texttt{group\_concat} in SPARQL.
+is interpreted as a map from a solution of SPARQL query to a tuple of a node, its label and its properties.
 
@@
 \begin{verbatim}
-<edge_template> ::= "(" src_resource  ":" src_label ")" - "[" edge_resource?  ":" edge_label  ("{" 
-<property_list> "}")? ")" (-> | -) "(" dst_resource  ":" dst_label ")"
+<edge_template> ::= "(" src_resource  ":" src_label ")" - 
+                    "[" edge_resource?  ":" edge_label  ("{"<property_list> "}")? ")" 
+                    (-> | -) "(" dst_resource  ":" dst_label ")"
 \end{verbatim}
@@
 \end{defi}
+
+A PG edge template specifies edges, the label, the properties and the source nodes and the destination nodes.
+A \texttt{src\_resource} and a \texttt{dst\_resource} specify which RDF resource should be mapped to endpoint nodes of resultant edges.
+A \texttt{src\_label} and a \texttt{dst\_label} work not only as labels of resultant nodes but also work as implicit constraints of the map.
+The resultant source nodes and edge nodes must match patterns in corresponding node maps.
+For this reason, \texttt{src\_label} and \texttt{dst\_label} must be defined in other node maps.
+A \texttt{edge\_resource}, a \texttt{edge\_label} and a \texttt{property\_list} can be described in the same manner as those counterparts in a node map.
+
+The primary key of an edge map is the tuple of the variable bound to \texttt{src\_resource}, \texttt{edge\_resource} and \texttt{dst\_resource}.
+As well as node maps, other values of variables bound in \texttt{property\_list} are concatenated into an array.
+
+The resultant edge can be either directed or undirected. If we use '\texttt{->}' as delimiter between an edge part and a destination part, the edge will be directed edge.
 
@@
          :name 'Bob' .
-:person1 :likes :person2 .
-[] a :Follow ;
-   :follower :person1 ;
-   :followed :person2 ;
-   :since 2017 .
+:person1 :supervised_by :person2 .
+[] a :Email ;
+   :sender     :person1 ;
+   :receiver   :person2 ;
+   :year       2017 .
+   :attachment '01.pdf'
 \end{verbatim}
@@
     ?p :name ?n .
-(p1:Person)-[:likes]->(p2:Person)
-    ?p1 :likes ?p2 .
-(p1:person)-[:follows {since:s}]->(p2:person)
-    ?f :follower ?p1 ;
-       :followed ?p2 ;
-       :since ?s .
+(p1:Person)-[:supervised_by]->(p2:Person)
+    ?p1 :supervised_by ?p2 .
+(p1:person)-[:emailed {year:y, attachment:a}]->(p2:person)
+    ?f :sender   ?p1 ;
+       :receiver ?p2 ;
+       :year     ?y .
+    OPTIONAL { ?f :attachment ?a }
 \end{verbatim}
@@
 "http://example.org/person2" :person name:Bob
-"http://example.org/person1" -> "http://example.org/person2" :likes
-"http://example.org/person1" -> "http://example.org/person2" :follows since:2017
+"http://example.org/person1" -> "http://example.org/person2" :supervised_by
+"http://example.org/person1" -> "http://example.org/person2" :emailed year:2017 attachment:"01.pdf"
 \end{verbatim}
@@
 \subsubsection{Multi Edges}
-When there are multiple information of potential edges between the same pair of resources in RDF.
+When a pair of RDF resources has multiple relationships, those will be converted not to a single PG edge with multiple properties but to multiple PG edges.
+The G2GML in Figure~\ref{fig:example-g2g} generates two PG edges for the RDF data in Figure~\ref{fig:example-rdf2} for keeping the information that Alice emailed Bob twice.
 
@@
          :name 'Bob' .
-[] a :Follow ;
-   :follower :person1 ;
-   :followed :person2 ;
-   :since 2017 .
-[] a :Follow ;
-   :follower :person1 ;
-   :followed :person2 ;
-   :since 2018 .
+[] a :Email ;
+   :sender   :person1 ;
+   :receiver :person2 ;
+   :year     2017 .
+[] a :Email ;
+   :sender   :person1 ;
+   :receiver :person2 ;
+   :year     2018 .
 \end{verbatim}
@@
 "http://example.org/person2" :Person name:Bob
-"http://example.org/person1" -> "http://example.org/person2" :follows since:2017
-"http://example.org/person1" -> "http://example.org/person2" :follows since:2018
+"http://example.org/person1" -> "http://example.org/person2" :emailed year:2017
+"http://example.org/person1" -> "http://example.org/person2" :emailed year:2018
 \end{verbatim}
@@
 \subsubsection{List of Property Values}
-PG property can have multiple values. When the same data property is put multiple times on a resource, the values are assumed to be the members of a list.
+Each PG property can have multiple values.
+When a RDF resource has the same data property multiple times, the values are assumed to be the members of a list.
+The G2GML in Figure~\ref{fig:example-g2g} generates one PG edge with two properties for the RDF data in Figure~\ref{fig:example-rdf3} keeping the information that Alice emailed Bob once and it had two attachments.
 
@@
 :person1 a :Person ;
-         :name 'Alice' ;
-         :name 'Allie' .
+         :name 'Alice' .
 :person2 a :Person ;
          :name 'Bob' .
-[] a :Follow ;
-   :follower :person1 ;
-   :followed :person2 ;
-   :since 2017 ;
-   :since 2018 .
+[] a :Email ;
+   :sender     :person1 ;
+   :receiver   :person2 ;
+   :year       2017 ;
+   :attachment '01.pdf' ;
+   :attachment '02.pdf' .
 
@@
 
-"http://example.org/person1" :Person name:Alice name:Allie
+"http://example.org/person1" :Person name:Alice
 "http://example.org/person2" :Person name:Bob
-"http://example.org/person1" -> "http://example.org/person2" :follows since:2017 since:2018
+"http://example.org/person1" -> "http://example.org/person2" :emailed year:2017 attachment:"01.pdf" attachment:"02.pdf"
 
@@
 \label{fig:example-pg3}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{G2G Mapper}
-
-G2G mapper is implemented in JavaScript, and can be executed using Node.js in command line.
-
-\texttt{g2g musician.g2g http://dbpedia.org/sparql}
-
-\noindent where the first argument is G2GML mapping file and the second argument is target SPARQL endpoint from which to extract RDF data.
-
-Also, demonstration cite of G2G mapper is available (Figure~\ref{fig:sandbox}).
-
-\begin{figure}
-\center
-\includegraphics[width=1.0\textwidth]{sandbox.png}
-\caption{G2G sandbox}
-\label{fig:sandbox}
 \end{figure}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Availability}
+
+\subsection{G2G Mapper}
+
+G2G mapper is implemented in JavaScript, and can be executed using Node.js in command line.
+It has endpoint mode and local file mode.
+Local file mode uses Apache Jena package to load and extract subset of the the loaded dataset by specifying SPARQL pattern.
+An example of endpoint mode is as follows:
+
+\texttt{g2g musician.g2g http://dbpedia.org/sparql}
+
+\noindent where the first argument is G2GML mapping file and the second argument is target SPARQL endpoint from which to extract RDF data.
+
+Docker image is also available.
+
+Furthermore, demonstration cite of G2G mapper is available (Figure~\ref{fig:sandbox}).
+
+\begin{figure}
+\center
+\includegraphics[width=1.0\textwidth]{sandbox.png}
+\caption{G2G sandbox}
+\label{fig:sandbox}
+\end{figure}
+
+\subsection{Graph Archive}
+We created several G2GML mappings to extract public RDF from endpoint and construct knowledge graphs in PG format and resulting knowledge graphs as Graph Archive.
+
+In the listed knowledge graphs, we compared the number of nodes and edges between RDF and property graphs.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\subsubsection{Graph Archive}
-We created several G2GML mappings to extract public RDF from endpoint and construct knowledge graphs in PG format and resulting knowledge graphs as Graph Archive.
-
-In the listed knowledge graphs, we compared the number of nodes and edges between RDF and property graphs.
+Comparison of direct mapping vs controlled mapping on the basis of G2GML should be conducted. For several datasets, statistics such as numbers of nodes and edges, and performaces should be presented.
 
@@
 RDF 1.1 Concepts and Abstract Syntax, W3C Recommendation 25 February 2014. \url{http://www.w3.org/TR/rdf11-concepts/}
+
+\bibitem{dbpedia}
+Lehmann, J., Isele, R., Jakob, M., Jentzsch, A., Kontokostas, D., Mendes, P.
+N., ...
+& Bizer, C.
+(2015).
+DBpedia–a large-scale, multilingual knowledge base extracted from Wikipedia.
+Semantic Web, 6(2), 167-195.
+
+\bibitem{wikidata}
+Vrandečić, D., & Krötzsch, M. (2014). Wikidata: a free collaborative knowledgebase. Communications of the ACM, 57(10), 78-85.
 

### 2020-03-21 paper.tex
Updates from Overleaf

@@
 \usepackage{hyperref}
+\usepackage{amsthm}
 % Used for displaying a sample figure. If possible, figure files should
@@
 \newtheorem{defi}[theorem]{Definition}
+\newtheorem*{prel}{Preliminaries}
 %
@@
 The G2GML is a declarative language which consists of pairs of RDF graph patterns and property graph patterns. 
-An intuitive meaning of a G2GML description is mapping RDF subgraphs that matches the specified patterns to specified components of property graphs.
+An intuitive meaning of a G2GML description is a map from  RDF subgraphs that matches the specified patterns to specified components of property graphs.
 
@@
 
-G2GML is a declarative language, where patterns of RDF and property graphs are described. RDF pattern is described using SPARQL pattern, and property graph pattern is described using Cypher pattern.
+G2GML is a language to describes maps from RDF graphs to Property graphs (PG).
+G2GML is a domain specific declarative language where programmers only have to describe target patterns of RDF and PG.
+RDF pattern is described using SPARQL pattern, and PG pattern is described using Cypher pattern.
 
-\subsubsection{Preliminaries}
-
+\begin{prel}
 An RDF triple $(s, p, o)$ is an element of $(I \cup B) \times I \times (I \cup B \cup L)$ where $I$, $L$ and $B$ are a set of IRIs, a set of literals and a set of blank nodes, which are considered pairwise disjoint.
@@
 An RDF graph is defined as a finite set of triples.
+\end{prel}
 
-\subsubsection{G2GML}
-G2GML describes maps from RDF graphs to Property graphs.
-
+\par
 In this paper, we call maps written in G2GML as \textit{G2G maps}.
@@
 A \textit{node map} is a function that maps from an RDF graph to a set of \textit{PG nodes}. 
-An \textit{edge map} is a function that maps from an RDF graph to a set of \textit{PG edges}.
-
-A node map is described as a pair of (i) a template of a PG node and (ii) an RDF graph pattern that can be written as \textit{GroupGraphPattern} in SPARQL syntax (see EBNF notation of SPARQL grammer~\cite{sparql}).
-
-\begin{defi}[PG node template]
-%\leavevmode \vspace{1mm} \\
-\emph{Syntax of PG node template.}
-\begin{scriptsize}
+Similarly, an \textit{edge map} is a function that maps from an RDF graph to a set of \textit{PG edges}.
+The meaning of a G2G map is a function that maps from an RDF graph to a set of PG nodes and edges that is mapped by  all its node and edge maps.
+We show a complete example of G2GML in Figure \ref{fig:example-g2g}.
+%TODO: consider the position of the example
+A node map is described as a pair of a PG node pattern  and an RDF graph pattern. Here we define the syntax of PG node pattern as follows. Note that symbols in uppercase are implicitly identifiers.
+\begin{defi}[EBNF notation of PG node pattern]
+\leavevmode
 \begin{verbatim}
-<node_template> ::= "(" node_resource  ":" label  ("{" <property_list> "}")? ")"
-<property_list> ::= <property> "," <property_list> | <property>
-<property> ::= key":" value
+ node_pat  ::= "(" NODE  ":" LABEL  ("{" prop_list "}")? ")"
+ prop_list ::= property "," prop_list | property
+ property  ::= PROP_NAME ":" PROP_VAL
 \end{verbatim}
-\end{scriptsize}
 \end{defi}
 
-A PG node template specifies nodes, labels and properties to be generated by the map.
-A \texttt{node\_resource} specifies ID of the generated node, which is replaced by the resource retrieved by RDF graph.
-A \texttt{label} specifies the label of the resultant node.
-A \texttt{label} also works as the name of node map which is referred from other edge maps.
-A \texttt{property} is a pair of \texttt{key} and \texttt{value} that describes properties of nodes.
-Note that \texttt{node\_resource} and \texttt{value} are  placeholders of the map replaced by resources or literals retrieved from RDF graphs.
-On the other hand, \texttt{label} and \texttt{key} must be fixed value.
+A PG node pattern specifies a node, a label and properties to be generated by the map.
+The \texttt{NODE} symbol specifies ID of the generated node, which is replaced by the resource retrieved by RDF graph.
+The \texttt{LABEL} symbol specifies the label of the resultant node.
+A label also works as the name of the node map which is referred from edge maps.
+Therefore an identifier of a label must be unique in a  G2GML map.
+Each node pattern contains zero or more properties as \texttt{prop\_list}.
+A \texttt{property} is a pair of \texttt{PROP\_NAME} and \texttt{PROP\_VAL} that describes properties of nodes.
+Identifiers \texttt{NODE} and \texttt{PROP\_VAL} must be names of variables in the succeeding RDF graph pattern, while \texttt{LABEL} and \texttt{PROP\_NAME} are regarded as text literals.
 
-RDF graph pattern specifies which resources should be mapped to nodes of property graphs.
-Resources match with these pattern yield solution sets of SPARQL SELECT query, that is, variables and bindings.
-The solution sets are mapped to nodes embedding bindings to its corresponding location according to the preciding node map.
+An RDF graph pattern in G2GML can be written in \textit{GroupGraphPattern} in SPARQL syntax (see EBNF notation of SPARQL grammer~\cite{sparql}).
+An RDF graph pattern specifies which resources should be mapped to PG nodes. Resources matching with these pattern yield solution sets of SELECT query in SPARQL, which 
+ are mapped to PG nodes by embedding variable bindings to corresponding location according to the preceding PG node pattern.
+Here, a variable bound to \texttt{PROP\_VAL} may have multiple candidates for single node.
+If such multiple candidate exists, they are concatenated into an array in the manner of \texttt{GROUP\_CONCAT} in SPARQL if multiple resources are bound to single \texttt{PROP\_NAME}.
 
-The URL bound to \texttt{node\_resource} used as the primary key of the map.
-Other resources or literals bound to \texttt{value} are concatenated into an array in the manner of \texttt{group\_concat} in SPARQL.
-is interpreted as a map from a solution of SPARQL query to a tuple of a node, its label and its properties.
-
-\begin{defi}[PG edge template]
-%\leavevmode \vspace{1mm} \\
-\emph{Syntax of PG edge template.}
-\begin{scriptsize}
+A PG edge pattern specifies a pattern of edge, the label, the properties and the source node and the destination node.
+Here we define the syntax of PG edge pattern as follows.
+\begin{defi}[EBNF notation of PG edge pattern]
+\leavevmode
 \begin{verbatim}
-<edge_template> ::= "(" src_resource  ":" src_label ")" - 
-                    "[" edge_resource?  ":" edge_label  ("{"<property_list> "}")? ")" 
-                    (-> | -) "(" dst_resource  ":" dst_label ")"
+edge_pat ::= "(" SRC  ":" SRC_LAB ") -" 
+                "[" EDGE?  ":" EDGE_LAB  ("{" prop_list "}")? ")" 
+                ("->" | "-") "(" DST ":" DST_LAB ")"
 \end{verbatim}
-\end{scriptsize}
 \end{defi}
 
-A PG edge template specifies edges, the label, the properties and the source nodes and the destination nodes.
-A \texttt{src\_resource} and a \texttt{dst\_resource} specify which RDF resource should be mapped to endpoint nodes of resultant edges.
-A \texttt{src\_label} and a \texttt{dst\_label} work not only as labels of resultant nodes but also work as implicit constraints of the map.
-The resultant source nodes and edge nodes must match patterns in corresponding node maps.
-For this reason, \texttt{src\_label} and \texttt{dst\_label} must be defined in other node maps.
-A \texttt{edge\_resource}, a \texttt{edge\_label} and a \texttt{property\_list} can be described in the same manner as those counterparts in a node map.
+ Identifiers of \texttt{SRC} and \texttt{DST} specify which variables in the succeeding RDF graph pattern should be mapped to endpoint nodes of resultant edges.
+A \texttt{SRC\_LAB} and a \texttt{DST\_LAB} work not only as labels of resultant nodes but also work as implicit constraints of the edge map.
+%TODO add ref
+The resultant source nodes and destination nodes must match patterns in corresponding node maps.
+For this reason, \texttt{SRC\_LAB} and \texttt{DST\_LAB} must be defined in other node maps.
+\texttt{EDGE}, \texttt{EDGE\_LAB} and \texttt{prop\_list} can be described in the same manner as those counterparts in node maps.
 
-The primary key of an edge map is the tuple of the variable bound to \texttt{src\_resource}, \texttt{edge\_resource} and \texttt{dst\_resource}.
-As well as node maps, other values of variables bound in \texttt{property\_list} are concatenated into an array.
+The primary key of an edge map is the tuple of the resources bound to \texttt{SRC}, \texttt{EDGE} and \texttt{DST}.
+As well as node maps, other values of properties bound in \texttt{prop\_list} are concatenated into an array.
 
-The resultant edge can be either directed or undirected. If we use '\texttt{->}' as delimiter between an edge part and a destination part, the edge will be directed edge.
+The resultant edges can be either directed or undirected. If we use '\texttt{->}' as delimiter between an edge part and a destination part, the edge will be a directed edge.
+ %TODO: add whole syntax of G2G using PG node pattern and edge pattern and SPARQL
 
@@
 
-\begin{defi}[PG Format]
-\leavevmode \vspace{1mm} \\
-\emph{EBNF notation of the PG format.}
-\begin{scriptsize}
+\begin{defi}[EBNF notation of the PG format]
+\leavevmode
 \begin{verbatim}
-    PG         ::= (Node | Edge)+
-    Node       ::= NODE_ID Labels Properties NEWLINE
-    Edge       ::= NODE_ID Direction NODE_ID Labels Properties NEWLINE
-    Labels     ::= Label*
-    Properties ::= Property*
-    Label      ::= ':' STRING
-    Property   ::= STRING ':' Value
-    Value      ::= STRING | NUMBER
-    Direction  ::= '--' | '->'
+ pg         ::= (node | edge)+
+ node       ::= NODE_ID labels properties NEWLINE
+ edge       ::= NODE_ID direction NODE_ID labels properties NEWLINE
+ labels     ::= label*
+ properties ::= property*
+ label      ::= ":" STRING
+ property   ::= STRING ":" value
+ value      ::= STRING | NUMBER
+ direction  ::= "--" | "->"
 \end{verbatim}
-\end{scriptsize}
 \end{defi}
@@
 
-%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Use Cases}
 
-We  present several use cases to show the usefulness of G2G mapping framework, where we use publicly available open data available in RDF through SPARQL endpoint.
+We present several use cases to show how to applythe usefulness of G2G mapping framework, where we utilizeuse publicly available open data available in RDF datasets through SPARQL endpoints.
 
@@
 
-Here we present use case of for Wikidata.
-Wikidata is a useful source of biological open data, and it is available in the form of RDF through the SPARQL interface.
+Here we present use case of for Wikidata. Wikidata is a useful source of biological open data, and it is available in the form of RDF through the SPARQL interface.
 
@@
 
+%--code--code--code--code--code--
 \begin{figure}[!t]
@@
 \end{figure}
+%--code--code--code--code--code--
 
@@
 An intuitive meaning of a G2GML description is mapping RDF subgraphs that matches the specified patterns to specified components of property graphs.
-
-%In this section, we briefly explain the syntax of G2GML with an example.
-
-%\subsection{Usecase}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}[h]
+    \centering
+    \begin{tabular}{l|r|r|r|r}
+        \hline
+        & RDF nodes & RDF edges & PG nodes & PG edges \\
+        \hline
+        Wikidata disease & 20,692 & 36,826 & 10,488 & 11,770 \\
+        DBpedia musician & 24,660 &  & 12,329 & 57,351 \\
+        \hline
+    \end{tabular}
+    \caption{Number of nodes and edges}
+    \label{tab:my_label}
+\end{table}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Evaluation}
-
-% The goal of our evaluation is to observe the impact the number of the nodes and edges on the performance and
-% analyzing its scalability when the size of the datset increases.
-% \begin{itemize}
-% \item Q1) : Is the runtime affected when more nodes are added?
-% \item Q2) : Does it scale to a larger dataset?
-% \item Q3) : How does it scale when adding a larger number of datasets?
-% \end{itemize}
-
-Comparison of direct mapping vs controlled mapping on the basis of G2GML should be conducted. For several datasets, statistics such as numbers of nodes and edges, and performaces should be presented.
 

### 2020-03-23 paper.tex
Updates from Overleaf

@@
 % Although RDF data can be queried using the SPARQL language~\cite{sparql} in a flexible way, SPARQL is not dedicated to traversal of graphs and has a limitation in implementing graph analysis algorithms.
-Recently, the property graph model~\cite{angles1,angles2} have been attracting increasing attention in the context of graph analysis; various graph database engines, including Neo4j~\cite{neo4j}, Oracle Labs PGX~\cite{pgx}, and Amazon Neptune~\cite{neptune}, adopt this model.
+Recently, the property graph model~\cite{angles1,angles2} have been attracting increasing attention in the context of graph analysis; various graph database engines, including Neo4j~\cite{neo4j}, Oracle Database~\cite{oracle}, and Amazon Neptune~\cite{neptune}, adopt this model.
 These graph database engines support algorithms for traversing or analyzing graphs.
@@
 
-G2GML is a language to describes maps from RDF graphs to Property graphs (PG).
-G2GML is a domain specific declarative language where programmers only have to describe target patterns of RDF and PG.
+G2GML is a language to describes maps from RDF graphs to property graphs.
+G2GML is a domain specific declarative language where programmers only have to describe patterns of RDF and property graphs (PG).
 RDF pattern is described using SPARQL pattern, and PG pattern is described using Cypher pattern.
@@
 The meaning of a G2G map is a function that maps from an RDF graph to a set of PG nodes and edges that is mapped by  all its node and edge maps.
-We show a complete example of G2GML in Figure \ref{fig:example-g2g}.
+Here we define the syntax of PG node pattern as follows. 
+Note that \texttt{NEWLINE} is an abstract symbol corresponding to appropriate character to start a new line.
+
+\begin{defi}[EBNF notation of G2GML]
+\label{defi:G2GML}
+\leavevmode
+\begin{verbatim}
+ g2gml   ::= SPARQL_PREFIX* mapping+
+ mapping ::= ( node_pat | edge_pat ) NEWLINE
+               INDENTED_RDF_PATTERN NEWLINE
+\end{verbatim}
+\end{defi}
+In Definition \ref{defi:G2GML}, \texttt{SPARQL\_PREFIX}
+ and \texttt{INDENTED\_RDF\_PATTERN} are almost same as \textit{PrefixDecl} and \textit{GroupGraphPattern} in SPARQL syntax (see EBNF notation of SPARQL grammer~\cite{sparql}).
+The only difference is that \texttt{INDENTED\_RDF\_PATTERN} must have one or more white spaces at the top of each line.
+Symbols \texttt{node\_pat} \texttt{edge\_pat} will be described in the following definition.
+
+An RDF graph pattern in G2GML specifies which resources should be mapped to PG nodes. Resources matching with these pattern yield solution sets of SELECT query in SPARQL, which 
+ are mapped to PG nodes by embedding variable bindings to corresponding location according to the preceding PG node pattern.
+A complete example of G2GML is shown in Figure \ref{fig:example-g2g}.
 %TODO: consider the position of the example
-A node map is described as a pair of a PG node pattern  and an RDF graph pattern. Here we define the syntax of PG node pattern as follows. Note that symbols in uppercase are implicitly identifiers.
+A node map is described as a pair of a PG node pattern  and an RDF graph pattern.
+Here we define the syntax of PG node pattern as follows.
+Note that \texttt{NODE}, \texttt{LABEL}, \texttt{PROP\_NAME} and \texttt{PROP\_VAL} are all identifiers.
 \begin{defi}[EBNF notation of PG node pattern]
@@
 
-An RDF graph pattern in G2GML can be written in \textit{GroupGraphPattern} in SPARQL syntax (see EBNF notation of SPARQL grammer~\cite{sparql}).
-An RDF graph pattern specifies which resources should be mapped to PG nodes. Resources matching with these pattern yield solution sets of SELECT query in SPARQL, which 
- are mapped to PG nodes by embedding variable bindings to corresponding location according to the preceding PG node pattern.
-Here, a variable bound to \texttt{PROP\_VAL} may have multiple candidates for single node.
-If such multiple candidate exists, they are concatenated into an array in the manner of \texttt{GROUP\_CONCAT} in SPARQL if multiple resources are bound to single \texttt{PROP\_NAME}.
-
 A PG edge pattern specifies a pattern of edge, the label, the properties and the source node and the destination node.
 Here we define the syntax of PG edge pattern as follows.
+Note that \texttt{SRC}, \texttt{SRC\_LAB}, \texttt{EDGE}, \texttt{EDGE\_LAB}, \textt{DST} and \texttt{DST\_LAB} are all identifiers.
 \begin{defi}[EBNF notation of PG edge pattern]
@@
 A \texttt{SRC\_LAB} and a \texttt{DST\_LAB} work not only as labels of resultant nodes but also work as implicit constraints of the edge map.
-%TODO add ref
+%TODO add ref to example section.
 The resultant source nodes and destination nodes must match patterns in corresponding node maps.
@@
 
-The primary key of an edge map is the tuple of the resources bound to \texttt{SRC}, \texttt{EDGE} and \texttt{DST}.
-As well as node maps, other values of properties bound in \texttt{prop\_list} are concatenated into an array.
+The resultant edges can be either directed or undirected. If we use '\texttt{->}' as delimiter between an edge part and a destination part, the edge will be a directed edge.
 
-The resultant edges can be either directed or undirected. If we use '\texttt{->}' as delimiter between an edge part and a destination part, the edge will be a directed edge.
- %TODO: add whole syntax of G2G using PG node pattern and edge pattern and SPARQL
+In node maps and edge maps, a variable bound to \texttt{PROP\_VAL} may have multiple candidates against single node or edge.
+If multiple candidate exists, they are concatenated into an array in the manner of \texttt{GROUP\_CONCAT} in SPARQL.
+If \texttt{EDGE} is omitted in an edge map, such candidates are concatenated  within groups of tuples of \texttt{SRC} and \texttt{DST}.
 
@@
 According to our definition of the property graph model, we propose serialization in flat text and JSON.
-The flat text format (PG) is better for human readability and line-oriented processing, while the JSON format (JSON-PG) is best used for server-client communication.
+The flat text format (PG format) is better for human readability and line-oriented processing, while the JSON format (JSON-PG format) is best used for server-client communication.
 
-The flat text PG format has the following characteristics, and an example is given in Figure~\ref{fig:example-pg}.
+The PG format has the following characteristics, and an example is given in Figure~\ref{fig:example-pg}.
 
@@
 
-Furthermore, we have implemented command-line tools to convert between PG and JSON-PG, as well as to transform them into formats for well-known graph databases such as Neo4j, Oracle Labs PGX, and Amazon Neptune.
+Furthermore, we have implemented command-line tools to convert between PG format and JSON-PG format, as well as to transform them into formats for well-known graph databases such as Neo4j, Oracle Database, and Amazon Neptune.
 The practical use cases of our tools demonstrate that the proposed data model and formats have the capability to describe property graph data begin used in existing graph databases (see \url{https://github.com/g2glab/pg}).
@@
 \end{scriptsize}
-\caption{Example of PG}
+\caption{Example of PG format}
 \label{fig:example-pg}
@@
 \end{scriptsize}
-\caption{Example of JSON-PG}
+\caption{Example of JSON-PG format}
 \label{fig:example-json}
@@
 %%%%%%%%%%%%
-\subsection{Minimal Exmples}
+\subsection{Minimal Examples}
 Figure~\ref{fig:example-g2g} shows the small example of G2G mapping from RDF data to PG data. This example shows the following five types of the typical mapping.
@@
 \begin{itemize}
-    \item Resource to node: In the line 2-4, the RDF resources with type \texttt{:Person} are mapped into PG nodes using their URIs as node IDs.
-    \item Datatype property to node property: In the line 2-4, the RDF datatype property \texttt{:name} is mapped into PG node property key \texttt{name}.
+    \item Resource to node: In the line 2-4, the RDF resources with type \texttt{:Person} are mapped into the PG nodes using their IRIs as node IDs.
+    \item Datatype property to node property: In the line 2-4, the RDF datatype property \texttt{:name} is mapped into the PG node property key \texttt{name}.
 The literal objects 'Alice' and 'Bob' are mapped into the node property values.
-    \item Object property to edge: In the line 5-6, the RDF object property \texttt{:likes} is mapped into PG edge \texttt{follows}. 
-    \item Resource to edge: In the line 7-10, the RDF resource with type \texttt{:Follow} is mapped into PG edge \texttt{follows}. 
-    \item Datatype property to edge property: In the line 7-10, the RDF datatype property \texttt{:since} is mapped into PG edge property \texttt{since}.
-The literal objects \texttt{2017} is mapped into the edge property value.
+    \item Object property to edge: In the line 5-6, the RDF object property \texttt{:supervised\_by} is mapped into the PG edge \texttt{supervised\_by}.
+    \item Resource to edge: In the line 7-10, the RDF resource with type \texttt{:Email} is mapped into the PG edge \texttt{emailed}. 
+    \item Datatype property to edge property: In the line 7-10, the RDF datatype property \texttt{:year} and \texttt{:attachment} are mapped into the PG edge property \texttt{year} and \texttt{attachment}.
+The literal objects \texttt{2017} and \texttt{01.pdf} are mapped into the edge property values.
 \end{itemize}
@@
 (p1:person)-[:emailed {year:y, attachment:a}]->(p2:person)
-    ?f :sender   ?p1 ;
+    ?f a :Email
+       :sender   ?p1 ;
        :receiver ?p2 ;
@@
 \includegraphics[width=0.5\textwidth]{pg_example5.png}
-\caption{Example of created PG}
+\caption{Example of output PG data}
 \label{fig:pg_example5}
@@
 The G2G mapping based on G2GML is generally intuitive as it is shown above, however, there are several discussions about the details of mapping.
+
+\subsubsection{Referencing Node Labels}
+The node labels in edge maps must be defined in node maps  (described in section 2.2) for referencing the conditions.
+This means that the conditions for defining `Person` are inherited to the definition of `supervised\_by` and `emailed` relationships.
+Therefore, when any `supervised\_by` relationship exists between the nodes which are not `Person`, this relationship will not be generated.
+In this way, users can retrieve the property graph datasets which are intuitively consistent (it is also possible not to specify node labels).
+On the other hand, edge conditions are not inherited to nodes, so the nodes which do not have any `supervised\_by` nor `emailed` relationships are also generated.
 
@@
 
-We present several use cases to show how to applythe usefulness of G2G mapping framework, where we utilizeuse publicly available open data available in RDF datasets through SPARQL endpoints.
+We present several use cases to show how to apply G2G mapping framework, where we utilize publicly available RDF datasets through SPARQL endpoints.
 
@@
 This mapping is processed by a tool called G2G Mapper, which was implemented by authors (available on \url{https://github.com/g2glab/g2g}).
-This tool can convert RDF data retrieved from SPARQL endpoints or from local files into PG format and then into specific formats for each of the database implementations.
+This tool retrieves RDF dataset from SPARQL endpoints or from local files, then coverts it into PG format.
+Optionally, the new dataset can be also saved in specific formats for loading it into the major graph database implementations.
 
@@
 
-Here we present use case of for Wikidata. Wikidata is a useful source of biological open data, and it is available in the form of RDF through the SPARQL interface.
+Here we present an example of mapping using a disease dataset from Wikidata.
+Wikidata is a useful source of open data from various domains, and it is available in the form of RDF through the SPARQL interface.
 
@@
     ?m rdfs:label ?n . FILTER(lang(?n) = "en") .
-    OPTIONAL { ?m dbo:hometown / rdfs:label ?h . FILTER(lang(?h) = "en") }
+    OPTIONAL { ?m dbo:hometown/rdfs:label ?h . FILTER(lang(?h) = "en") }
 
 # Edge mapping
-(m1:Musician)-[:same_group {name:n, since:s}]-(m2:Musician)  # PG Pattern
+(m1:Musician)-[:sameGroup {name:n, since:s}]-(m2:Musician)  # PG Pattern
     ?g rdf:type schema:MusicGroup ;                          # RDF Pattern
@@
 
-\texttt{g2g musician.g2g http://dbpedia.org/sparql}
+\texttt{\$ g2g musician.g2g http://dbpedia.org/sparql}
 
@@
 \section{Related Work}
+
+\subsection{PG Model}
 Recently, the graph data have been attracting increasing attention, leading to plethora of database implementations. 
@@
 
+\subsection{Graph to Graph Mapping}
 As a preceding work for converting existing data into graph data, there was an effort to convert relational to graph databases~\cite{virgilio1}. 
@@
 A previous work compared performance of Blazegraph and Neo4j. They concluded that RDF has advantage in terms of performance and interoperability.
+
+\subsubsection{Direct Mapping}
+
+Other mapping frameworks such as Neosemantics (a Neo4j plugins) propose the method to convert RDF datasets without mapping definitions (for convenience, we call such methods as direct mapping).
+However, the following capabilities are essential in practical usage.
+
+1.
+Filtering data - RDF is designed for the web of data.
+When the source RDF dataset is retrieved from the public web space, it is inefficient (or even unrealistic) to convert the whole connected dataset.
+In G2GML, users specify the resources they need, so the SPARQL endpoints can return the filtered dataset.
+(This design is described in the section 2.2.)
+
+2.
+Mapping details - There is no common ruleset to uniquely map RDF terms to PG elements (labels, key-value pairs of properties) and to name the new PG elements.
+Also, the conversion rules of multi-edges and list of property values (discussed in the section 2.6) are not always obvious for users.
+Therefore, the definition method of the mapping details is necessary for creating precise data in actual usage.
+
+3.
+Schema definition - We expect that the mapping is often used for developing specific applications on the property graph datasets.
+In such development, the schema of the dataset should be known, while the original RDF data source could contains more information which are not covered by the schema.
+G2GML helps developers understand the data schema in its intuitive definition (separately for nodes and edges, and their referencing - discussed in the section 2.6), while direct mapping has potential to generate property graphs without defining schema.
+
+We can find a similar discussion in the conversion from relational model to RDF, and in this case, there are two W3C standards, Direct Mapping~\cite{dm} and R2RML~\cite{r2rml}.
 
@@
 
-\bibitem{pgx}
-Oracle Labs Parallel Graph AnalytiX (PGX). \url{https://www.oracle.com/technetwork/oracle-labs/parallel-graph-analytix/overview/index.html}
+\bibitem{oracle}
+Oracle Database Property Graph. \url{https://www.oracle.com/goto/propertygraph}
 
@@
 
+\bibitem{dm}
+A Direct Mapping of Relational Data to RDF, W3C Recommendation 27 September 2012 \url{https://www.w3.org/TR/r2rml/}
+
+\bibitem{r2rml}
+R2RML: RDB to RDF Mapping Language, W3C Recommendation 27 September 2012 \url{https://www.w3.org/TR/r2rml/}
+
 % \bibitem{ref_article1}

### 2020-03-23 paper.tex
update before the first English editing

@@
 
-Next, we describe the JSON-PG format which follows the JSON syntax in addition to the above definition of the property graph model.
+% Next, we describe the JSON-PG format which follows the JSON syntax in addition to the above definition of the property graph model.
 The JSON-PG format has the following characteristics, and an example of the format is shown in Figure~\ref{fig:example-json}.
@@
 
-\begin{itemize}
-    \item Nodes and edges are listed under \texttt{nodes} and \texttt{edges} elements, respectively.
-    \item Edge direction is defined with the boolean element \texttt{undirected}. By default it is false (directed).
-    \item Labels are listed under the \texttt{labels} element.
-    \item Properties (key-value pairs) are listed under the \texttt{properties} element.
-\end{itemize}
+% \begin{itemize}
+%     \item Nodes and edges are listed under \texttt{nodes} and \texttt{edges} elements, respectively.
+%     \item Edge direction is defined with the boolean element \texttt{undirected}. By default it is false (directed).
+%     \item Labels are listed under the \texttt{labels} element.
+%     \item Properties (key-value pairs) are listed under the \texttt{properties} element.
+% \end{itemize}
 
-Furthermore, we have implemented command-line tools to convert between PG format and JSON-PG format, as well as to transform them into formats for well-known graph databases such as Neo4j, Oracle Database, and Amazon Neptune.
+Furthermore, we have implemented command-line tools to convert between PG format and JSON-PG format which follows the JSON syntax in adition to the above definition, as well as to transform them into formats for well-known graph databases such as Neo4j, Oracle Database, and Amazon Neptune.
 The practical use cases of our tools demonstrate that the proposed data model and formats have the capability to describe property graph data begin used in existing graph databases (see \url{https://github.com/g2glab/pg}).
@@
 
-\begin{figure}[!t]
-\begin{scriptsize}
-\begin{verbatim}
-{
-  "nodes":[
-    {
-     "id":101,
-     "labels":["Person"],
-     "properties":{"name":["Alice"], "age":[15], "country":["United States"]}
-    },
-    {
-     "id":102,
-     "labels":["Person", "Student"],
-     "properties":{"name":["Bob"], "country":["Japan", "Germany"]}
-    }
-  ],https://ja.overleaf.com/project/5d6e87b11a254100014e487d
-  "edges":[
-    {
-     "from":101,
-     "to":102,
-     "undirected":true,
-     "labels":["sameSchool", "sameClass"],
-     "properties":{"since":[2012]}
-    },
-    {
-     "from":102,
-     "to":101,
-     "labels":["likes"],
-     "properties":{"since":[2015]}
-    }
-  ]
-}
-\end{verbatim}
-\end{scriptsize}
-\caption{Example of JSON-PG format}
-\label{fig:example-json}
-\end{figure}
+% \begin{figure}[!t]
+% \begin{scriptsize}
+% \begin{verbatim}
+% {
+%   "nodes":[
+%     {
+%      "id":101,
+%      "labels":["Person"],
+%      "properties":{"name":["Alice"], "age":[15], "country":["United States"]}
+%     },
+%     {
+%      "id":102,
+%      "labels":["Person", "Student"],
+%      "properties":{"name":["Bob"], "country":["Japan", "Germany"]}
+%     }
+%   ],https://ja.overleaf.com/project/5d6e87b11a254100014e487d
+%   "edges":[
+%     {
+%      "from":101,
+%      "to":102,
+%      "undirected":true,
+%      "labels":["sameSchool", "sameClass"],
+%      "properties":{"since":[2012]}
+%     },
+%     {
+%      "from":102,
+%      "to":101,
+%      "labels":["likes"],
+%      "properties":{"since":[2015]}
+%     }
+%   ]
+% }
+% \end{verbatim}
+% \end{scriptsize}
+% \caption{Example of JSON-PG format}
+% \label{fig:example-json}
+% \end{figure}
 
@@
 
-\begin{figure}
-\center
-\includegraphics[width=1.0\textwidth]{neo4jexample2.png}
-\caption{Visualization on Neo4j}
-\label{fig:neo4jexample2.png}
-\end{figure}
+% \begin{figure}
+% \center
+% \includegraphics[width=1.0\textwidth]{neo4jexample2.png}
+% \caption{Visualization on Neo4j}
+% \label{fig:neo4jexample2.png}
+% \end{figure}
 
@@
 
-\subsection{Graph Archive}
-We created several G2GML mappings to extract public RDF from endpoint and construct knowledge graphs in PG format and resulting knowledge graphs as Graph Archive.
+% \subsection{Graph Archive}
+% We created several G2GML mappings to extract public RDF from endpoint and construct knowledge graphs in PG format and resulting knowledge graphs as Graph Archive.
 
-In the listed knowledge graphs, we compared the number of nodes and edges between RDF and property graphs.
+% In the listed knowledge graphs, we compared the number of nodes and edges between RDF and property graphs.
 

### 2020-03-23 paper.tex
update after call

@@
 SPARQL~\cite{sparql} is a standardized interface for RDF.
-However, the usecases through thouse interface are still limited.
+However, the use cases through thouse interface are still limited.
 Although the standardized format and interface contributed the integrated large data could, further interface is expected to maximize the value of RDF datasets.
@@
 
-The contributions of this papers are 1) development of Graph to Graph Mapping Language 2) proposal of common property graph model and serialization 3) development of G2G mapper 4) construction of knowledge graph resources in a common format as Graph Archive.
+%The contributions of this papers are 1) development of G2GML, 2) proposal of common property graph model and its serialization, 3) development of a prototype implementation, 4) construction of knowledge graph resources in a common format as Graph Archive.
+
+The main contributions of this papers are 1) language design of G2GML, 2) its prototype implementation.
+Additionally, we proposes 3) the common property graph model and its serialization, which are essential to make this mapping framework independent from the implementations of database systems.
 
 %%%%%%%%%%%%%%%%%%%%%%%
-\section{G2G: Graph to Graph Mapping Framework}
+\section{Graph to Graph Mapping}
 
@@
 
-Here we illustrate the overview of the framework.
-G2G is a framework to describe mapping between RDF and property graphs for interoperable use of them. In this framework, users can specify mappings from RDF to property graphs in G2GML.
-This mapping is processed by a tool called G2G Mapper, which was implemented by authors (available on \url{https://github.com/g2glab/g2g}).
-This tool can convert RDF data retrieved from SPARQL endpoints or from local files into PG format and then into specific formats for each of the database implementations.
+Here we illustrate the overview of the graph to graph mapping (G2G mapping) framework (Figure~\ref{fig:dataflow}).
+
+In this framework, users describe mappings from RDF to property graphs in G2GML.
+According to this G2GML description, a G2GML implementation converts input RDF dataset into property graph dataset.
+Optionally, the new dataset can be also saved in specific formats for loading it into the major graph database implementations.
+
+%G2G is a framework to perform mapping between RDF and property graphs for interoperable use of them. In this framework, users can describe mappings from RDF to property graphs in G2GML.
+%G2GML implementation converts RDF dataset into property graph dataset. Optionally, the new dataset can be also saved in specific formats for loading it into the major graph database implementations.
 
@@
 As an entry point to property graph, we define the Property Graph format, which is based on the Property Graph model.
+
+\begin{figure}
+\center
+\includegraphics[width=1.0\textwidth]{dataflow.png}
+\caption{Overview of the mapping from RDF to property graph}
+\label{fig:dataflow}
+\end{figure}
 
@@
 \par
-In this paper, we call maps written in G2GML as \textit{G2G maps}.
-A \textit{G2G map} consists of one or more \textit{node maps} and \textit{edge maps}.
+A map described by G2GML consists of one or more \textit{node maps} and \textit{edge maps}.
 A \textit{node map} is a function that maps from an RDF graph to a set of \textit{PG nodes}. 
 Similarly, an \textit{edge map} is a function that maps from an RDF graph to a set of \textit{PG edges}.
-The meaning of a G2G map is a function that maps from an RDF graph to a set of PG nodes and edges that is mapped by  all its node and edge maps.
+The meaning of a G2GML description is a function that maps from an RDF graph to a set of PG nodes and edges that is mapped by all its node and edge maps.
 Here we define the syntax of PG node pattern as follows. 
@@
 A label also works as the name of the node map which is referred from edge maps.
-Therefore an identifier of a label must be unique in a  G2GML map.
+Therefore an identifier of a label must be unique in a G2GML description.
 Each node pattern contains zero or more properties as \texttt{prop\_list}.
@@
 Here we define the syntax of PG edge pattern as follows.
-Note that \texttt{SRC}, \texttt{SRC\_LAB}, \texttt{EDGE}, \texttt{EDGE\_LAB}, \textt{DST} and \texttt{DST\_LAB} are all identifiers.
+Note that \texttt{SRC}, \texttt{SRC\_LAB}, \texttt{EDGE}, \texttt{EDGE\_LAB}, \texttt{DST} and \texttt{DST\_LAB} are all identifiers.
 \begin{defi}[EBNF notation of PG edge pattern]
@@
 In node maps and edge maps, a variable bound to \texttt{PROP\_VAL} may have multiple candidates against single node or edge.
-If multiple candidate exists, they are concatenated into an array in the manner of \texttt{GROUP\_CONCAT} in SPARQL.
+If multiple candidate exists, they are concatenated into an array in the manner of GROUP\_CONCAT in SPARQL.
 If \texttt{EDGE} is omitted in an edge map, such candidates are concatenated  within groups of tuples of \texttt{SRC} and \texttt{DST}.
@@
 Furthermore, we have implemented command-line tools to convert between PG format and JSON-PG format which follows the JSON syntax in adition to the above definition, as well as to transform them into formats for well-known graph databases such as Neo4j, Oracle Database, and Amazon Neptune.
-The practical use cases of our tools demonstrate that the proposed data model and formats have the capability to describe property graph data begin used in existing graph databases (see \url{https://github.com/g2glab/pg}).
+The practical use cases of our tools demonstrate that the proposed data model and formats have the capability to describe property graph data being used in existing graph databases (see \url{https://github.com/g2glab/pg}).
 
@@
 
-Figure~\ref{fig:dataflow} shows the overview of the mapping.
-In this framework, users can specify mappings from RDF to property graphs in G2GML.
-This mapping is processed by a tool called G2G Mapper, which was implemented by authors (available on \url{https://github.com/g2glab/g2g}).
-This tool retrieves RDF dataset from SPARQL endpoints or from local files, then coverts it into PG format.
-Optionally, the new dataset can be also saved in specific formats for loading it into the major graph database implementations.
-
-The G2GML is a declarative language which consists of pairs of RDF graph patterns and property graph patterns. 
-An intuitive meaning of a G2GML description is mapping RDF subgraphs that matches the specified patterns to specified components of property graphs.
-
-\begin{figure}
-\center
-\includegraphics[width=1.0\textwidth]{dataflow.png}
-\caption{Overview of the mapping from RDF to property graph}
-\label{fig:dataflow}
-\end{figure}
-
 \subsection{Using Wikidata}
@@
 In Wikidata, each disease is associated with zero or more genes and drugs.
-The subset of Wikidata can be extracted using G2G framework by writing a mapping file in G2GML (see the following list).
+The subset of Wikidata can be extracted using G2G mapping framework by writing a mapping file in G2GML (see the following list).
 Here, we focus on human genes. So we specified the necessary conditions in G2GML.
@@
 \subsection{Using DBpedia}
-
-Here we describe a framework for mapping RDF graphs to property graphs.
-Figure~\ref{fig:dataflow} shows the overview of the framework.
-In this framework, users can specify mappings from RDF to property graphs in G2GML.
-This mapping is processed by a tool called G2G Mapper, which was implemented by authors (available on \url{https://github.com/g2glab/g2g}).
-This tool can convert RDF data retrieved from SPARQL endpoints or from local files into PG format and then into specific formats for each of the database implementations.
-
-The G2GML is a declarative language which consists of pairs of RDF graph patterns and property graph patterns. 
-An intuitive meaning of a G2GML description is mapping RDF subgraphs that matches the specified patterns to specified components of property graphs.
 
@@
 Figure~\ref{fig:sparql} shows the SPARQL query to retrieve the pairs of musicians who are in the same group.
-After the G2G mapping, we can load the generated property graph data into graph databases, such as Oracle Labs PGX, and the query can be written in PGQL~\cite{pgql} (the query language of PGX).
+After the G2G mapping, we can load the generated property graph data into graph databases, such as Oracle Database, and the query can be written in PGQL~\cite{pgql} (the graph query language of Oracle Database).
 
@@
 \section{Availability}
-
-\subsection{G2G Mapper}
-
-G2G mapper is implemented in JavaScript, and can be executed using Node.js in command line.
+The prototype implementation is written in JavaScript, and can be executed using Node.js in command line.
 It has endpoint mode and local file mode.
-Local file mode uses Apache Jena package to load and extract subset of the the loaded dataset by specifying SPARQL pattern.
-An example of endpoint mode is as follows:
+Local file mode uses Apache Jena ARQ to execute SPARQL queries internally, while endpoint mode accesses SPARQL endpoints via the Internet.
+An example of the usage in endpoint mode is as follows:
 
@@
 
-\noindent where the first argument is G2GML mapping file and the second argument is target SPARQL endpoint from which to extract RDF data.
+\noindent where the first argument is a G2GML mapping file and the second argument is the target SPARQL endpoint which provides the source RDF dataset. %from which the RDF dataset is extracted.
 
-Docker image is also available.
-
-Furthermore, demonstration cite of G2G mapper is available (Figure~\ref{fig:sandbox}).
+Furthermore, its Docker image (\url{https://hub.docker.com/r/g2glab/g2g}) and a demonstration site of G2G mapping framework (\url{http://g2g.fun}) are also available (Figure~\ref{fig:sandbox}).
 
@@
 \includegraphics[width=1.0\textwidth]{sandbox.png}
-\caption{G2G sandbox}
+\caption{G2G mapping demonstration site}
 \label{fig:sandbox}

### 2020-04-18 paper.tex
Update after English editing

@@
 %
-\titlerunning{G2GML: Graph to Graph Mapping Lanugage}
+\titlerunning{G2GML: Graph to Graph Mapping Language}
 %\titlerunning{Interoperable Use of RDF and Property Graph}
@@
 \begin{abstract}
-% The abstract should briefly summarize the contents of the paper in 15--250 words.
-How can we maximize the value of accumulated RDF data?
-Although increasing amounts of scientific and social data are described as RDF, their use cases are still limited.
-Allowing access to the RDF datasets through various interface beyond the SPARQL interface will be expected.
-Importing the RDF datasets into various graph analysis engines will increase the values of the datasets.
-However, interoperable management of such graph data is challenging due to the differences in existing models and formats depending on various implementations.
-Here, we redefine the property graph model incorporating the differences in existing models and propose exchangeable serialization formats for property graphs, which can be converted into specific formats for each of the databases.
-The serialization formats independent of certain database implementations will increase the interoperability of graph databases and will make it easier for users to import accumulated graph data.
-We further propose a framework for mapping RDF graphs to property graphs on the basis of the Graph to Graph Mapping Language (G2GML).
-Using this framework, accumulated graph data described in RDF can be converted to property graphs, which can then be loaded into several graph database engines for further analysis.
-%This work provides interoperability not only between property graph formats but also between RDF and proper graphs.
-%Future works include implementing and utilizing graph algorithms to make the most of the accumulated data in various analytical engines.
+Increasing amounts of scientific and social data are presented in the resource description framework (RDF); however, their use cases remain limited.
+Maximizing the value of accumulated RDF data is therefore considered a challenge, and efforts have been made to this end, including allowing access to RDF datasets through various interfaces beyond SPARQL and importing RDF datasets into various graph analysis engines.
+However, the interoperable management of graph data is challenging due to differences in existing models and formats, which depend on various implementations.
+In this study, we redefine the property graph (PG) model incorporating the differences in existing models and propose exchangeable serialization formats for PGs, which can be converted into specific formats for each database.
+The serialization formats that are independent of certain database implementations increase the interoperability of graph databases and make it easier for users to import accumulated graph data.
+We further propose a framework for mapping RDF graphs to PGs based on the graph to graph mapping language (G2GML).
+Using this framework, accumulated graph data described in RDF can be converted into PGs, which can then be loaded into several graph database engines for further analysis.
 
@@
 \section{Introduction}
-% Please note that the first paragraph of a section or subsection is not indented. The first paragraph that follows a table, figure, equation etc. does not need an indent, either.
 
-Increasing amounts of scientific and social data are published in the form of Resource Description Framework (RDF)~\cite{rdf}.
-It now constitutes a large open data cloud.
-DBpedia~\cite{dbpedia} and Wikidata~\cite{wikidata} are good example.
-SPARQL~\cite{sparql} is a standardized interface for RDF.
-However, the use cases through thouse interface are still limited.
-Although the standardized format and interface contributed the integrated large data could, further interface is expected to maximize the value of RDF datasets.
-% Although RDF data can be queried using the SPARQL language~\cite{sparql} in a flexible way, SPARQL is not dedicated to traversal of graphs and has a limitation in implementing graph analysis algorithms.
-Recently, the property graph model~\cite{angles1,angles2} have been attracting increasing attention in the context of graph analysis; various graph database engines, including Neo4j~\cite{neo4j}, Oracle Database~\cite{oracle}, and Amazon Neptune~\cite{neptune}, adopt this model.
+Increasing amounts of scientific and social data are being published in the form of the Resource Description Framework (RDF)~\cite{rdf}, which presently constitutes a large open data cloud.
+DBpedia~\cite{dbpedia} and Wikidata~\cite{wikidata} are good examples of such RDF datasets.
+SPARQL~\cite{sparql} is a protocol and query language that serves as a standardized interface for RDF data.
+This standardized format and interface enables the construction of integrated graph datasets.
+However, the lack of an interface for graph-based analysis and performant traversal limits use cases of the graph data.
+
+Recently, the property graph (PG) model~\cite{angles1,angles2} has been attracting increasing attention in the context of graph analysis.
+Various graph database engines, including Neo4j~\cite{neo4j}, Oracle Database~\cite{oracle}, and Amazon Neptune~\cite{neptune} adopt this model.
 These graph database engines support algorithms for traversing or analyzing graphs.
-However, currently not many datasets are consistently described in the property graph model, so the application of these powerful engines are limited.
+However, few datasets are consistently described in the PG model, such that the application of these powerful engines is limited.
 
-Considering this situation, it is valuable to develop a method to transform RDF into property graphs. One of the practical issues is the lack of a standardized model for property graphs. 
-Another issue is that transformation between them is not straightforward due to the differences between RDF and property graph models. 
-In RDF graphs, all information is expressed as the triple (node-edge-node), whereas in property graphs, arbitrary information can be contained in each of the nodes and edges as the key-value form. 
-Although this issue has been previously addressed on the basis of predefined transformations~\cite{hartig},
+In light of this situation, developing a method to transform RDF into PG would be highly valuable. One of the practical issues faced by this challenge is the lack of a standardized PG model.
+Another issue is that the transformation between RDF and PG is not straightforward due to the differences in their models. 
+In RDF graphs, all information is expressed by a triple (node-edge-node), whereas in PGs, arbitrary information can be contained in each node and edge as the key-value form. 
+Although this issue was previously addressed on the basis of predefined transformations~\cite{hartig},
 users still cannot control the mapping for their specific use cases.
 
-Here, we redefine the property graph model incorporating the differences in existing models and also propose serialization formats based on the data model.
-We further propose a graph to graph mapping framework on the basis of the Graph to Graph Mapping Language (G2GML).
-Using this mapping framework, accumulated graph data described in RDF can be converted into property graphs, which can then be loaded into several graph database engines for further analysis.
-We will show several use cases where publicly available RDF data is extracted and convert to property graphs and also evaluate the performance.
-This work provides the foundation of interoperability of knowledge graphs.
+In this study, we redefine the PG model incorporating the differences in existing models and propose serialization formats based on the data model.
+We further propose a graph to graph mapping framework based on the graph to graph mapping language (G2GML).
+Employing this mapping framework, accumulated graph data described in the RDF can be converted into PGs, which can be loaded into several graph database engines for further analysis.
+We demonstrate several use cases, where publicly available RDF data is extracted and converted to PGs, and evaluate the performance.
+Thus, this study provides the foundation for the interoperability of knowledge graphs.
 
@@
 
-The main contributions of this papers are 1) language design of G2GML, 2) its prototype implementation.
-Additionally, we proposes 3) the common property graph model and its serialization, which are essential to make this mapping framework independent from the implementations of database systems.
+The main contributions of this study are as follows: 1) language design of G2GML; 2) its prototype implementation.
+Furthermore, we propose 3) the common PG model and its serialization, which are essential to ensure this mapping framework is independent from the implementations of database systems.
 
@@
 
-Here we illustrate the overview of the graph to graph mapping (G2G mapping) framework (Figure~\ref{fig:dataflow}).
+We provide an overview of the graph to graph mapping (G2G mapping) framework (Figure~\ref{fig:dataflow}).
 
-In this framework, users describe mappings from RDF to property graphs in G2GML.
-According to this G2GML description, a G2GML implementation converts input RDF dataset into property graph dataset.
-Optionally, the new dataset can be also saved in specific formats for loading it into the major graph database implementations.
+In this framework, users describe mappings from the RDF to PG in G2GML.
+According to this G2GML description, G2GML implementation converts the input RDF dataset into the PG dataset.
+The new dataset can also be optionally saved in specific formats for loading into major graph database implementations.
 
-%G2G is a framework to perform mapping between RDF and property graphs for interoperable use of them. In this framework, users can describe mappings from RDF to property graphs in G2GML.
-%G2GML implementation converts RDF dataset into property graph dataset. Optionally, the new dataset can be also saved in specific formats for loading it into the major graph database implementations.
+The G2GML is a declarative language that consists of pairs of RDF patterns and PG patterns. 
+The intuitive meaning of a G2GML can be represented by a map of RDF subgraphs, which matches the specified patterns to specified components of PGs.
 
-The G2GML is a declarative language which consists of pairs of RDF graph patterns and property graph patterns. 
-An intuitive meaning of a G2GML description is a map from RDF subgraphs that matches the specified patterns to specified components of property graphs.
-
-As an entry point to property graph, we define the Property Graph format, which is based on the Property Graph model.
+%As an entry point to the PG, we define serialization based on the PG model.
+%G2GML implementation converts the RDF dataset into a property graph dataset. The new dataset can also be saved in specific formats for loading into major graph database implementations.
 
@@
 \includegraphics[width=1.0\textwidth]{dataflow.png}
-\caption{Overview of the mapping from RDF to property graph}
+\caption{Overview of mapping from RDF to PG}
 \label{fig:dataflow}
@@
 
-G2GML is a language to describes maps from RDF graphs to property graphs.
-G2GML is a domain specific declarative language where programmers only have to describe patterns of RDF and property graphs (PG).
-RDF pattern is described using SPARQL pattern, and PG pattern is described using Cypher pattern.
+G2GML is a language applied to describe maps from RDF graphs to PGs.
+It represents a domain-specific declarative language, where programmers only have to describe patterns of RDF and PG.
+The RDF pattern is described in terms of the SPARQL pattern, and the PG pattern is described using the Cypher pattern.
 
 \begin{prel}
-An RDF triple $(s, p, o)$ is an element of $(I \cup B) \times I \times (I \cup B \cup L)$ where $I$, $L$ and $B$ are a set of IRIs, a set of literals and a set of blank nodes, which are considered pairwise disjoint.
-In this paper, an RDF triple is simply called a triple.
-For a triple $(s, p, o)$, $s$ is called the subject, $p$ the predicate and $o$ the object.
+An RDF triple $(s, p, o)$ is an element of $(I \cup B) \times I \times (I \cup B \cup L)$, where $I$, $L$, and $B$ are a set of IRIs, a set of literals, and a set of blank nodes, which are considered pairwise disjoint.
+In this study, an RDF triple is simply referred to as a triple.
+For a triple $(s, p, o)$, $s$ is the subject, $p$ the predicate, and $o$ the object.
 An RDF graph is defined as a finite set of triples.
@@
 \par
-A map described by G2GML consists of one or more \textit{node maps} and \textit{edge maps}.
-A \textit{node map} is a function that maps from an RDF graph to a set of \textit{PG nodes}. 
-Similarly, an \textit{edge map} is a function that maps from an RDF graph to a set of \textit{PG edges}.
-The meaning of a G2GML description is a function that maps from an RDF graph to a set of PG nodes and edges that is mapped by all its node and edge maps.
-Here we define the syntax of PG node pattern as follows. 
-Note that \texttt{NEWLINE} is an abstract symbol corresponding to appropriate character to start a new line.
+A G2GML description consists of one or more \textit{node maps} and \textit{edge maps}.
+A \textit{node map} is a function that maps resources from an RDF graph to a set of \textit{PG nodes}. 
+Similarly, an \textit{edge map} is a function that maps resources from an RDF graph to a set of \textit{PG edges}.
+%A G2GML description is a function that maps resources from an RDF graph to a set of PG nodes and edges that are mapped by all node and edge maps.
+Here, we define the syntax of the PG node pattern as follows. 
+\texttt{NEWLINE} is used an abstract symbol corresponding to the appropriate character to start a new line.
 
@@
 In Definition \ref{defi:G2GML}, \texttt{SPARQL\_PREFIX}
- and \texttt{INDENTED\_RDF\_PATTERN} are almost same as \textit{PrefixDecl} and \textit{GroupGraphPattern} in SPARQL syntax (see EBNF notation of SPARQL grammer~\cite{sparql}).
-The only difference is that \texttt{INDENTED\_RDF\_PATTERN} must have one or more white spaces at the top of each line.
-Symbols \texttt{node\_pat} \texttt{edge\_pat} will be described in the following definition.
+ and \texttt{INDENTED\_RDF\_PATTERN} are almost the same as \textit{PrefixDecl} and \textit{GroupGraphPattern} in SPARQL syntax (see EBNF notation of SPARQL grammar~\cite{sparql}).
+The only difference is that \texttt{INDENTED\_RDF\_PATTERN} must have one or more white spaces on top of each line.
+Symbols \texttt{node\_pat} \texttt{edge\_pat} are described according to the following definition.
 
-An RDF graph pattern in G2GML specifies which resources should be mapped to PG nodes. Resources matching with these pattern yield solution sets of SELECT query in SPARQL, which 
- are mapped to PG nodes by embedding variable bindings to corresponding location according to the preceding PG node pattern.
+An RDF graph pattern in G2GML specifies the resources that should be mapped to PG nodes.
+Resources matching with these patterns yield solution sets of SELECT query in SPARQL, which are mapped to PG nodes by embedding variable bindings to corresponding locations according to the preceding PG node pattern.
 A complete example of G2GML is shown in Figure \ref{fig:example-g2g}.
@@
 A node map is described as a pair of a PG node pattern and an RDF graph pattern.
-Here we define the syntax of PG node pattern as follows.
-Note that \texttt{NODE}, \texttt{LABEL}, \texttt{PROP\_NAME} and \texttt{PROP\_VAL} are all identifiers.
+Here, we define the syntax of the PG node pattern as follows.
+Notably, \texttt{NODE}, \texttt{LABEL}, \texttt{PROP\_NAME}, and \texttt{PROP\_VAL} are all identifiers.
 \begin{defi}[EBNF notation of PG node pattern]
@@
 
-A PG node pattern specifies a node, a label and properties to be generated by the map.
-The \texttt{NODE} symbol specifies ID of the generated node, which is replaced by the resource retrieved by RDF graph.
+A PG node pattern specifies a node, a label, and properties to be generated by the map.
+The \texttt{NODE} symbol specifies the ID of the generated node, which is replaced by the resource retrieved by the RDF graph.
 The \texttt{LABEL} symbol specifies the label of the resultant node.
-A label also works as the name of the node map which is referred from edge maps.
-Therefore an identifier of a label must be unique in a G2GML description.
+A label also serves as the name of the node map, which is referred from edge maps.
+Therefore, the identifier of each label must be unique in a G2GML description.
 Each node pattern contains zero or more properties as \texttt{prop\_list}.
-A \texttt{property} is a pair of \texttt{PROP\_NAME} and \texttt{PROP\_VAL} that describes properties of nodes.
+A \texttt{property} is a pair of \texttt{PROP\_NAME} and \texttt{PROP\_VAL} that describes the properties of nodes.
 Identifiers \texttt{NODE} and \texttt{PROP\_VAL} must be names of variables in the succeeding RDF graph pattern, while \texttt{LABEL} and \texttt{PROP\_NAME} are regarded as text literals.
 
-A PG edge pattern specifies a pattern of edge, the label, the properties and the source node and the destination node.
-Here we define the syntax of PG edge pattern as follows.
-Note that \texttt{SRC}, \texttt{SRC\_LAB}, \texttt{EDGE}, \texttt{EDGE\_LAB}, \texttt{DST} and \texttt{DST\_LAB} are all identifiers.
+A PG edge pattern specifies the pattern of the edge, label, properties, as well as the source and destination nodes.
+Here, we define the syntax of the PG edge pattern as follows.
+Notably, \texttt{SRC}, \texttt{SRC\_LAB}, \texttt{EDGE}, \texttt{EDGE\_LAB}, \texttt{DST}, and \texttt{DST\_LAB} are all identifiers.
 \begin{defi}[EBNF notation of PG edge pattern]
@@
 
- Identifiers of \texttt{SRC} and \texttt{DST} specify which variables in the succeeding RDF graph pattern should be mapped to endpoint nodes of resultant edges.
-A \texttt{SRC\_LAB} and a \texttt{DST\_LAB} work not only as labels of resultant nodes but also work as implicit constraints of the edge map.
+ Identifiers of \texttt{SRC} and \texttt{DST} specify the variables in the succeeding RDF graph pattern that should be mapped to endpoint nodes of resultant edges.
+A \texttt{SRC\_LAB} and a \texttt{DST\_LAB} serve not only as labels of resultant nodes, but also as implicit constraints of the edge map.
 %TODO add ref to example section.
-The resultant source nodes and destination nodes must match patterns in corresponding node maps.
+The resultant source and destination nodes must match patterns in the corresponding node maps.
 For this reason, \texttt{SRC\_LAB} and \texttt{DST\_LAB} must be defined in other node maps.
-\texttt{EDGE}, \texttt{EDGE\_LAB} and \texttt{prop\_list} can be described in the same manner as those counterparts in node maps.
+\texttt{EDGE}, \texttt{EDGE\_LAB}, and \texttt{prop\_list} can be described in the same manner as their counterparts in node maps.
 
-The resultant edges can be either directed or undirected. If we use '\texttt{->}' as delimiter between an edge part and a destination part, the edge will be a directed edge.
+The resultant edges can be either directed or undirected. If we use '\texttt{->}' as delimiter between an edge and a destination part, the edge will be a directed edge.
 
-In node maps and edge maps, a variable bound to \texttt{PROP\_VAL} may have multiple candidates against single node or edge.
-If multiple candidate exists, they are concatenated into an array in the manner of GROUP\_CONCAT in SPARQL.
+In node and edge maps, a variable bound to \texttt{PROP\_VAL} may have multiple candidates against a single node or edge.
+If multiple candidates exist, they are concatenated into an array in the same manner as GROUP\_CONCAT in SPARQL.
 If \texttt{EDGE} is omitted in an edge map, such candidates are concatenated within groups of tuples of \texttt{SRC} and \texttt{DST}.
@@
 %%%%%%%%%%%
-\subsection{The Property Graph Model}
-Here we define the property graph model independent of specific graph database implementations.
-For the purpose of interoperability, we incorporate differences in property graph models, taking into consideration multiple labels or property values for nodes and edges, as well as mixed graphs with both of directed and undirected edges.
-The property graph model we redefine here requires the following characteristics:
+\subsection{Property Graph Model}
+We define the PG model independent of specific graph database implementations.
+For the purpose of interoperability, we incorporate differences in PG models, taking into consideration multiple labels or property values for nodes and edges, as well as mixed graphs with both directed and undirected edges.
+The PG model we redefine here requires the following characteristics:
 
 \begin{itemize}
-    \item A property graph contains nodes and edges.
-    \item Each of the nodes and edges can have zero or more labels.
-    \item Each of the nodes and edges can have properties (key-value pairs).
+    \item A PG contains nodes and edges.
+    \item Each node and edge can have zero or more labels.
+    \item Each node and edge can have properties (key-value pairs).
     \item Each property can have multiple values.
@@
 \end{itemize}
-More formally, we define the property graph model as follows.
+Formally, we define the PG model as follows.
 
@@
 \leavevmode \vspace{1mm} \\
-A \emph{Property Graph} is a tuple
+A \emph{property graph} is a tuple
 $PG = \langle N, E_d, E_u, S, V, P, e, l_n, l_e, p_n, p_e\rangle$, where:
@@
     \item $E_u$ is a set of undirected edges.
-    \item $E$ is a set of edges where $E = E_d \cup E_u$.
+    \item $E$ is a set of edges, where $E = E_d \cup E_u$.
     \item $S$ is a set of strings.
     \item $V$ is a set of values of arbitrary data types.
-    \item $P$ is a set of properties. Each property has the form $p = \langle k,v \rangle$, where $k \in S$ and $v \in 2^V$.
-    \item $e: E \to \langle N \times N \rangle$ is a function which yields the endpoints of each directed or undirected edge (if the edge is directed, the first node is the source and the second node is the destination).
+    \item $P$ is a set of properties. Each property assumes the form $p = \langle k,v \rangle$, where $k \in S$ and $v \in 2^V$.
+    \item $e: E \to \langle N \times N \rangle$ is a function that yields the endpoints of each directed or undirected edge (if the edge is directed, the first node is the source, and the second node is the destination).
     \item $l_n : N \to 2^S$ is a function mapping each node to its multiple labels.
@@
 \subsection{Serialization of Property Graphs}
-According to our definition of the property graph model, we propose serialization in flat text and JSON.
-The flat text format (PG format) is better for human readability and line-oriented processing, while the JSON format (JSON-PG format) is best used for server-client communication.
+According to our definition of the PG model, we propose serialization in flat text and JSON.
+The flat text format (PG format) performs better in terms of human readability and line-oriented processing, while the JSON format (JSON-PG format) is best used for server-client communication.
 
@@
     \item Each line describes a node or an edge.
-    \item All elements in each line are separated by space or tab.
+    \item All the elements in each line are separated by spaces or tabs.
     \item In each of the node lines, the first column contains the node ID.
-    \item In each of the edge lines, the first three columns contain the source node ID, the direction, and the destination node ID.
+    \item In each of the edge lines, the first three columns contain the source node ID, direction, and destination node ID.
     \item Each line can contain an arbitrary number of labels.
@@
 
-% Next, we describe the JSON-PG format which follows the JSON syntax in addition to the above definition of the property graph model.
-The JSON-PG format has the following characteristics, and an example of the format is shown in Figure~\ref{fig:example-json}.
-It is to be noted that, whereas the set of labels or property values are represented as arrays in JSON, those elements are supposed to have no specific order according to the property graph model.
-
-% \begin{itemize}
-%     \item Nodes and edges are listed under \texttt{nodes} and \texttt{edges} elements, respectively.
-%     \item Edge direction is defined with the boolean element \texttt{undirected}. By default it is false (directed).
-%     \item Labels are listed under the \texttt{labels} element.
-%     \item Properties (key-value pairs) are listed under the \texttt{properties} element.
-% \end{itemize}
-
-Furthermore, we have implemented command-line tools to convert between PG format and JSON-PG format which follows the JSON syntax in adition to the above definition, as well as to transform them into formats for well-known graph databases such as Neo4j, Oracle Database, and Amazon Neptune.
-The practical use cases of our tools demonstrate that the proposed data model and formats have the capability to describe property graph data being used in existing graph databases (see \url{https://github.com/g2glab/pg}).
+Furthermore, we implemented command-line tools to convert formats between the flat PG and JSON-PG, where the latter follows the JSON syntax in addition to the above definition.
+We further transform them into formats for well-known graph databases such as Neo4j, Oracle Database, and Amazon Neptune.
+The practical use cases of our tools demonstrate that the proposed data model and formats have the capability to describe PG data used in existing graph databases (see \url{https://github.com/g2glab/pg}).
 
@@
 
-% \begin{figure}[!t]
-% \begin{scriptsize}
-% \begin{verbatim}
-% {
-%   "nodes":[
-%     {
-%      "id":101,
-%      "labels":["Person"],
-%      "properties":{"name":["Alice"], "age":[15], "country":["United States"]}
-%     },
-%     {
-%      "id":102,
-%      "labels":["Person", "Student"],
-%      "properties":{"name":["Bob"], "country":["Japan", "Germany"]}
-%     }
-%   ],https://ja.overleaf.com/project/5d6e87b11a254100014e487d
-%   "edges":[
-%     {
-%      "from":101,
-%      "to":102,
-%      "undirected":true,
-%      "labels":["sameSchool", "sameClass"],
-%      "properties":{"since":[2012]}
-%     },
-%     {
-%      "from":102,
-%      "to":101,
-%      "labels":["likes"],
-%      "properties":{"since":[2015]}
-%     }
-%   ]
-% }
-% \end{verbatim}
-% \end{scriptsize}
-% \caption{Example of JSON-PG format}
-% \label{fig:example-json}
-% \end{figure}
-
 %%%%%%%%%%%%
 \subsection{Minimal Examples}
-Figure~\ref{fig:example-g2g} shows the small example of G2G mapping from RDF data to PG data. This example shows the following five types of the typical mapping.
+Figure~\ref{fig:example-g2g} shows the minimal example of G2G mapping from RDF to PG data, representing the following five types of typical mapping.
 
 \begin{itemize}
-    \item Resource to node: In the line 2-4, the RDF resources with type \texttt{:Person} are mapped into the PG nodes using their IRIs as node IDs.
-    \item Datatype property to node property: In the line 2-4, the RDF datatype property \texttt{:name} is mapped into the PG node property key \texttt{name}.
-The literal objects 'Alice' and 'Bob' are mapped into the node property values.
-    \item Object property to edge: In the line 5-6, the RDF object property \texttt{:supervised\_by} is mapped into the PG edge \texttt{supervised\_by}.
-    \item Resource to edge: In the line 7-10, the RDF resource with type \texttt{:Email} is mapped into the PG edge \texttt{emailed}. 
-    \item Datatype property to edge property: In the line 7-10, the RDF datatype property \texttt{:year} and \texttt{:attachment} are mapped into the PG edge property \texttt{year} and \texttt{attachment}.
-The literal objects \texttt{2017} and \texttt{01.pdf} are mapped into the edge property values.
+    \item Resource to node: In line 2-4, the RDF resources with type \texttt{:Person} are mapped into the PG nodes using their IRIs as node IDs.
+    \item Datatype property to node property: In line 2-4, the RDF datatype property \texttt{:name} is mapped onto the PG node property key \texttt{name}.
+The literal objects 'Alice' and 'Bob' are mapped onto the node property values.
+    \item Object property to edge: In line 5-6, the RDF object property \texttt{:supervised\_by} is mapped onto the PG edge \texttt{supervised\_by}.
+    \item Resource to edge: In line 7-10, the RDF resource with type \texttt{:Email} is mapped onto the PG edge \texttt{emailed}. 
+    \item Datatype property to edge property: In line 7-10, the RDF datatype property \texttt{:year} and \texttt{:attachment} are mapped onto the PG edge property \texttt{year} and \texttt{attachment}.
+The literal objects \texttt{2017} and \texttt{01.pdf} are mapped onto the edge property values.
 \end{itemize}
@@
 \subsection{Mapping Details}
-The G2G mapping based on G2GML is generally intuitive as it is shown above, however, there are several discussions about the details of mapping.
+The G2G mapping based on G2GML is generally intuitive, as shown above; however, there are several discussions regarding the details of mapping.
 
 \subsubsection{Referencing Node Labels}
-The node labels in edge maps must be defined in node maps  (described in section 2.2) for referencing the conditions.
-This means that the conditions for defining `Person` are inherited to the definition of `supervised\_by` and `emailed` relationships.
-Therefore, when any `supervised\_by` relationship exists between the nodes which are not `Person`, this relationship will not be generated.
-In this way, users can retrieve the property graph datasets which are intuitively consistent (it is also possible not to specify node labels).
-On the other hand, edge conditions are not inherited to nodes, so the nodes which do not have any `supervised\_by` nor `emailed` relationships are also generated.
+The node labels in edge maps must be defined in node maps (described in Section 2.2) to reference the conditions.
+This means that the conditions for defining `Person` are imported into the definition of `supervised\_by` and `emailed` relationships.
+Therefore, the `supervised\_by` relationship will be generated only between the nodes satisfying the `Person` condition.
+In this manner, users can retrieve the PG datasets that are intuitively consistent (it is also possible to avoid specifying node labels).
+In contrast, edge conditions are not inherited to nodes, such that the nodes that do not have any `supervised\_by` nor `emailed` relationships are also generated.
 
-\subsubsection{Multi Edges}
-When a pair of RDF resources has multiple relationships, those will be converted not to a single PG edge with multiple properties but to multiple PG edges.
-The G2GML in Figure~\ref{fig:example-g2g} generates two PG edges for the RDF data in Figure~\ref{fig:example-rdf2} for keeping the information that Alice emailed Bob twice.
+\subsubsection{Multi-Edges}
+When a pair of RDF resources has multiple relationships, those will be converted to multiple PG edges instead of a single PG edge with multiple properties.
+The G2GML in Figure~\ref{fig:example-g2g} generates two PG edges for the RDF data in Figure~\ref{fig:example-rdf2} to maintain the information that Alice emailed Bob twice.
 
@@
 \end{scriptsize}
-\caption{Example of input RDF data (multi edges)}
+\caption{Example of input RDF data (multi-edges)}
 \label{fig:example-rdf2}
@@
 \end{scriptsize}
-\caption{Example of output PG data (multi edges)}
+\caption{Example of output PG data (multi-edges)}
 \label{fig:example-pg2}
@@
 \subsubsection{List of Property Values}
-Each PG property can have multiple values.
-When a RDF resource has the same data property multiple times, the values are assumed to be the members of a list.
-The G2GML in Figure~\ref{fig:example-g2g} generates one PG edge with two properties for the RDF data in Figure~\ref{fig:example-rdf3} keeping the information that Alice emailed Bob once and it had two attachments.
+Each PG property can assume multiple values.
+In an RDF that includes the same data property multiple times, the values are assumed to be the members of a list.
+The G2GML in Figure~\ref{fig:example-g2g} generates one PG edge with two properties for the RDF data in Figure~\ref{fig:example-rdf3}, keeping the information that Alice emailed Bob once, and the email contained two attachments.
 
@@
 
-We present several use cases to show how to apply G2G mapping framework, where we utilize publicly available RDF datasets through SPARQL endpoints.
+We present several use cases to show how to apply the G2G mapping framework, where we utilize publicly available RDF datasets through SPARQL endpoints.
 
@@
 
-Here we present an example of mapping using a disease dataset from Wikidata.
 Wikidata is a useful source of open data from various domains, and it is available in the form of RDF through the SPARQL interface.
-
-In Wikidata, each disease is associated with zero or more genes and drugs.
-The subset of Wikidata can be extracted using G2G mapping framework by writing a mapping file in G2GML (see the following list).
-Here, we focus on human genes. So we specified the necessary conditions in G2GML.
-Each entity of ‘Q12136: disease’ can have property ‘P2176: drug used for treatment’, thereby linked to items of ‘Q12140: medication’.
-Also, each disease can have property ‘P2293: genetic association’, thereby linked to items of ‘Q7186: gene’.
-
-The numbers of obtained entities are as follows.
-
-4689 diseases
-4495 human genes
-1285 drugs
-
-The following figure shows the schematic relationships between those entities.
+We present an example of mapping using a disease dataset from Wikidata, 
+where each disease is associated with zero or more genes and drugs.
+Figure~\ref{fig:wikidata_schema.png} illustrates the schematic relationships between those entities. 
+The subset of Wikidata can be extracted using the G2G mapping framework by writing a mapping file in G2GML (see Figure~\ref{fig:g2gml_wikidata}).
+Here, we focus on human genes and specify the necessary conditions in G2GML.
+Each instance of \texttt{Q12136} (disease) can have a property \texttt{P2176} (drug used for treatment), which is thereby linked to items of \texttt{Q12140} (medication).
+Further, each disease can have property \texttt{P2293} (genetic association), which is thereby linked to items of \texttt{Q7186} (gene).
+The numbers of obtained instances includes 4696 diseases, 4496 human genes, and 1287 drugs.
+The total numbers of nodes and edges are summarized in Table~\ref{table:numbers}.
+As a result of G2G mapping, the numbers of nodes and edges are reduced to almost half and one third, respectively.
 
@@
 \includegraphics[width=0.7\textwidth]{wikidata_schema.png}
-\caption{Schematic relation of Wikidata entities}
+\caption{Schematic relations of Wikidata entities}
 \label{fig:wikidata_schema.png}
@@
 (g:HumanGene {symbol: s})
-    ?g wdt:P31 wd:Q7187 ;      # instance of gene
-       wdt:P703 wd:Q15978631 ; # found in taxon Homo sapiens
-       wdt:P353 ?s .           # HGNC gene symbol
+    ?g wdt:P31 wd:Q7187 ;      # "instance of" "gene"
+       wdt:P703 wd:Q15978631 ; # "found in taxon" "Homo sapiens"
+       wdt:P353 ?s .           # "HGNC gene symbol"
 
 (d:Disease {name: n})
-    ?d wdt:P31 wd:Q12136 ;     # instance of disease
+    ?d wdt:P31 wd:Q12136 ;     # "instance of" "disease"
        rdfs:label ?l .
@@
 (m:Drug {name: n})
-    ?m wdt:P31 wd:Q12140 ;     # instance of medication
+    ?m wdt:P31 wd:Q12140 ;     # "instance of" "medication"
        rdfs:label ?l .
@@
 (d:Disease)-[:hasAssociatedGene]->(g:HumanGene)
-    ?d wdt:P2293 ?g .          # genetic association
+    ?d wdt:P2293 ?g .          # "genetic association"
 
 (d:Disease)-[:hasDrug]->(m:Drug)
-    ?d wdt:P2176 ?m .          # drug used for treatment
+    ?d wdt:P2176 ?m .          # "drug used for treatment"
 
@@
 
-Figure~\ref{fig:conversion} schematically shows an example of the G2G mapping to convert RDF data retrieved from DBpedia into property graph data. 
-When we focus on a relationships where two musicians (\texttt{?m1} and \texttt{?m2}) belong to the same group, such information can be represented in the property graph shown in the right side of the figure.
+Figure~\ref{fig:conversion} schematically illustrates an example of the G2G mapping to convert RDF data retrieved from DBpedia into PG data. 
+Focusing on a relationship where two musicians (\texttt{?m1} and \texttt{?m2}) belong to the same group, this information can be represented in the PG shown in the right side of the figure.
 
@@
 \includegraphics[width=1.0\textwidth]{example.jpg}
-\caption{Schematic example of the graph to graph mapping}
+\caption{Schematic example of graph to graph mapping}
 \label{fig:conversion}
@@
 
-The mapping rule for the above example is specified in G2GML shown in Figure~\ref{fig:g2gml}.
-Following the prefix declaration for URIs used to write mappings, each mapping pattern is defined by a combination of a property graph pattern in an unindented line and an RDF graph pattern in indented lines.
-The property graph pattern is specified in a syntax like Cypher (the query language of Neo4j), whereas the RDF graph pattern is specified using a SPARQL code pattern.
-Variables in each mapping pattern are associated by their names across the different data models. 
-In G2G mapping, execution of the edge mappings is dependent on the node mappings, which means that edges are generated iff both nodes' patterns and edges' patterns are matched with RDF graphs. 
+The mapping rule for the above example is specified in the G2GML description shown in Figure~\ref{fig:g2gml}.
+Following the prefix declaration for URIs used to write mappings, each mapping pattern is defined by a combination of a PG pattern in an unindented line and an RDF graph pattern in indented lines.
+The PG pattern is specified in a syntax derived from Cypher (the query language of Neo4j), whereas the RDF graph pattern is specified using a SPARQL code pattern.
+Variables in each mapping pattern are associated by their names across different data models. 
+In G2G mapping, the execution of the edge mappings is dependent on the node mappings, which means that edges are generated if and only if both nodes' and edges' patterns are matched with RDF graphs. 
 The example contains node mapping for \texttt{Musician} entities and edge mapping for \texttt{same\_group} relationships.
-In each of the specified property graph patterns, \texttt{\{m, n, h\}} and \texttt{\{m1, m2, n, s\}} are used as variables to reconstruct resources and literals extracted from RDF graphs. 
+In each specified PG pattern, \texttt{\{m, n, h\}} and \texttt{\{m1, m2, n, s\}} are used as variables to reconstruct resources and literals extracted from RDF graphs. 
 %In this example, RDF literals are mapped to property values.
@@
 (m:Musician {name:n, hometown:h})                            # PG Pattern
-    ?m rdf:type foaf:Person , dbo:MusicalArtist .            # RDF Pattern
-    ?m rdfs:label ?n . FILTER(lang(?n) = "en") .
+    ?m rdf:type foaf:Person , dbo:MusicalArtist ;            # RDF Pattern
+       rdfs:label ?n . FILTER(lang(?n) = "en") .
     OPTIONAL { ?m dbo:hometown/rdfs:label ?h . FILTER(lang(?h) = "en") }
@@
 
-Figure~\ref{fig:sparql} shows the SPARQL query to retrieve the pairs of musicians who are in the same group.
+Figure~\ref{fig:sparql} shows the SPARQL query to retrieve the pairs of musicians that are in the same group.
 After the G2G mapping, we can load the generated property graph data into graph databases, such as Oracle Database, and the query can be written in PGQL~\cite{pgql} (the graph query language of Oracle Database).
@@
         \hline
-        Wikidata disease & 20,692 & 36,826 & 10,488 & 11,770 \\
-        DBpedia musician & 24,660 &  & 12,329 & 57,351 \\
+        Wikidata disease & 20,692 & 36,826 & 10,477 & 11,770 \\
+        DBpedia musician & 23,846 & 32,808 & 7,069 & 10,755 \\
         \hline
     \end{tabular}
-    \caption{Number of nodes and edges}
-    \label{tab:my_label}
+    \caption{Number of nodes and edges in use cases}
+    \label{table:numbers}
 \end{table}
@@
 \section{Availability}
-The prototype implementation is written in JavaScript, and can be executed using Node.js in command line.
-It has endpoint mode and local file mode.
-Local file mode uses Apache Jena ARQ to execute SPARQL queries internally, while endpoint mode accesses SPARQL endpoints via the Internet.
-An example of the usage in endpoint mode is as follows:
+The prototype implementation is written in JavaScript and can be executed using Node.js in the command line.
+It has an endpoint mode and a local file mode.
+The local file mode uses Apache Jena ARQ to execute SPARQL queries internally, while the endpoint mode accesses SPARQL endpoints via the Internet.
+An example of the usage in the endpoint mode is as follows:
 
@@
 
-\noindent where the first argument is a G2GML mapping file and the second argument is the target SPARQL endpoint which provides the source RDF dataset. %from which the RDF dataset is extracted.
+\noindent where the first argument is a G2GML mapping file, and the second argument is the target SPARQL endpoint, which provides the source RDF dataset. %from which the RDF dataset is extracted.
 
@@
 
-\subsection{PG Model}
-Recently, the graph data have been attracting increasing attention, leading to plethora of database implementations. 
-%So far, there have been implementations of graph databases on the basis of various data models and query languages. 
-%So far, there are differences in data models and query languages based on the implementations of graph databases.
-So far, there have been different data models and query languages for these graph database implementations.
-Thus, there have been community-based activities for standardizing graph query language for interoperable use of property graph databases~\cite{angles3}.
-Similarly, standardization of the property graph model of various database implementations will enhance the interoperable use of graph data.
-In fact, there is a need for graph standardization in the community and graph data standardization was recently discussed in a W3C workshop~\cite{w3c}; there were similar proposals for property graph model and serialization~\cite{tomaszuk} including ours and it is noteworthy that the two independent approaches have converged to the similar solution.
-In particular, our serialization has implementation for some of the major database engines and also has a potential to cover further various implementations.
-%However, it requires developing a converter for each format.
-%This work provides a basis of an interoperable platform for creating, exchanging, and utilizing property graph data.
-%Specifically, our model and serialization are independent of specific implementations and provides a basis 
-%Specifically, it provides the basis for mapping of our G2GML mapping. 
-The serialization formats independent of certain database implementations will increase the interoperability of graph databases and will make it easier for users to import accumulated graph data.
+\subsection{Property Graph Model and Serialization}
+Recently, graph data have attracted increasing attention, leading to a plethora of database implementations. 
+Thus far, different data models and query languages have been available for these graph database implementations.
+Consequently, there have been community-based activities for standardizing the graph query language for interoperable use of PG databases~\cite{angles3}.
+Similarly, the standardization of the PG model for various database implementations enhances the interoperable use of graph data.
+There is indeed a demand for graph standardization in the community, which was recently discussed in a W3C workshop~\cite{w3c}.
+Another proposal for the PG model and serialization~\cite{tomaszuk} that was similar to ours was presented in the workshop, and it is noteworthy that the two independent studies converged to a similar solution.
+They seem to be interchangeable; however, this remains to be tested.
+Future studies should address collaboration and standardization of the data model.
+In particular, our serialization has implementation for some of the major database engines and also has a potential to further cover various database engines. 
+The serialization formats that are independent of certain database implementations will increase the interoperability of graph databases and make it easier for users to import accumulated graph data.
 %In G2G mapping, PG format works as a gateway from RDF to property graphs.
@@
 \subsection{Graph to Graph Mapping}
-As a preceding work for converting existing data into graph data, there was an effort to convert relational to graph databases~\cite{virgilio1}. 
-However, given that RDF has now prevailed as a standardized data model in scientific communities, considering the mapping on the basis of the RDF model is crucial.
-There have been discussions about the interoperability of RDF and property graphs~\cite{hartig,angles4,das,thakkar} and efforts were made to develop methods to convert RDF into property graphs~\cite{tomaszuk1,virgilio}.
-However, considering the flexibility of what kind of information can be expressed by each edge in property graphs, a novel method for controlling the mapping is necessary.
-To the best of our knowledge, this is the first attempt to develop a framework for controlled mapping between RDF and property graphs. 
-Notably, the G2GML we have designed is a declarative mapping language. 
+A preceding study on converting existing data into graph data included an effort to convert relational databases into graph databases~\cite{virgilio1}. 
+However, given that RDF has prevailed as a standardized data model in scientific communities, considering mapping based on the RDF model is crucial.
+The interoperability of RDF and PG~\cite{hartig,angles4,das,thakkar} has been discussed, and efforts were made to develop methods to convert RDF into PG~\cite{tomaszuk1,virgilio}.
+However, considering the flexibility regarding the type of information that can be expressed by each edge in property graphs, a novel method for controlling the mapping is necessary.
+To the best of our knowledge, this study presents the first attempt to develop a framework for controlled mapping between RDF and PG. 
+Notably, the designed G2GML is a declarative mapping language. 
 As a merit of the declarative description, we can concentrate on the core logic of mappings.
-In the sense that the mapping process generates new graph data on the basis of existing graph data, it has close relation to the semantic inference.
-Similar concept can be found in SPARQL CONSTRUCT queries.
+In the sense that the mapping process generates new graph data on the basis of existing graph data, it has a close relation to the semantic inference.
+A similar concept is found in the SPARQL CONSTRUCT queries.
 While the SPARQL CONSTRUCT clause defines mapping on the same data model, G2GML defines mapping between different data models.
@@
 However, if mapping includes the SPARQL pattern that are not declarative, it is not applicable for generating RDF triples.
-Thus, G2GML can be considered as a specific extension of the SPARQL CONSTRUCT clause for generation or inference of property graph data.
+Thus, G2GML is considered as a specific extension of the SPARQL CONSTRUCT clause for generation or inference of PG data.
 %Future works include further analysis of the converted graph data on the database engines adopting the property graph model.
 
-A previous work compared performance of Blazegraph and Neo4j. They concluded that RDF has advantage in terms of performance and interoperability.
+A previous study compared the performance of Blazegraph and Neo4j. They concluded that RDF has an advantage in terms of performance and interoperability.
 
@@
 
-Other mapping frameworks such as Neosemantics (a Neo4j plugins) propose the method to convert RDF datasets without mapping definitions (for convenience, we call such methods as direct mapping).
+Other mapping frameworks, such as Neosemantics (a Neo4j plugins), propose a method to convert RDF datasets without mapping definitions (for convenience, we call such methods direct mapping).
 However, the following capabilities are essential in practical usage.
@@
 When the source RDF dataset is retrieved from the public web space, it is inefficient (or even unrealistic) to convert the whole connected dataset.
-In G2GML, users specify the resources they need, so the SPARQL endpoints can return the filtered dataset.
-(This design is described in the section 2.2.)
+In G2GML, users specify the resources they need, such that the SPARQL endpoints can return the filtered dataset.
+(This design is described in Section 2.2.)
 
 2.
-Mapping details - There is no common ruleset to uniquely map RDF terms to PG elements (labels, key-value pairs of properties) and to name the new PG elements.
-Also, the conversion rules of multi-edges and list of property values (discussed in the section 2.6) are not always obvious for users.
-Therefore, the definition method of the mapping details is necessary for creating precise data in actual usage.
+Mapping details - There is no common ruleset to uniquely map RDF terms to PG elements (labels, key-value pairs of properties) and to name new PG elements.
+Further, the conversion rules of multi-edges and list of property values (discussed in Section 2.6) are not always obvious to users.
+Therefore, the defining method of the mapping details is necessary to create precise data in actual usage.
 
 3.
-Schema definition - We expect that the mapping is often used for developing specific applications on the property graph datasets.
-In such development, the schema of the dataset should be known, while the original RDF data source could contains more information which are not covered by the schema.
-G2GML helps developers understand the data schema in its intuitive definition (separately for nodes and edges, and their referencing - discussed in the section 2.6), while direct mapping has potential to generate property graphs without defining schema.
+Schema definition - We assume that mapping is often used for developing specific applications on top of PG datasets.
+In this development, the schema of the dataset should be known, while the original RDF data source could contain more information that is not covered by the schema.
+G2GML helps developers understand the data schema in its intuitive definition (separately for nodes and edges, and their referencing - discussed in Section 2.6), while direct mapping has the potential to generate PGs without defining a schema.
 
-We can find a similar discussion in the conversion from relational model to RDF, and in this case, there are two W3C standards, Direct Mapping~\cite{dm} and R2RML~\cite{r2rml}.
+We find a similar discussion in the conversion from the relational model to RDF, where are two W3C standards, i.e., Direct Mapping~\cite{dm} and R2RML~\cite{r2rml}.
 
 \section{Conclusion}
-Here we redefined the property graph model independent of specific graph database implementations and also proposed serialization formats based on the data model.
-We further designed G2GML for mapping RDF graphs to property graphs and implemented a converter on the basis of G2GML.
-Our data model and mapping framework will increase the interoperability of existing graph databases and make it easier for users to create, exchange, and utilize graph data.
+We redefined the PG model independent of specific graph database implementations and proposed serialization formats based on the data model.
+We further designed the G2GML for mapping RDF graphs to PGs and developed a prototype implementation of G2GML, which is publicly available.
+Our data model and mapping framework increase the interoperability of existing graph databases and make it easier for users to create, exchange, and utilize graph data.
 
 \section*{Acknowledgements}
-Part of the work was conducted through the BioHackathon meetings (\url{http://www.biohackathon.org}).
-We thank Yuka Tsujii for helping creating figures.
+Part of the work was conducted in BioHackathon meetings (\url{http://www.biohackathon.org}).
+We thank Yuka Tsujii for helping create the figures.
 We thank Ramona Roess for careful review of the manuscript and useful comments.

### 2020-05-11 paper.tex
Before collaborators' reviews

@@
 %
-\maketitle              % typeset the header of the contribution
+\maketitle
 %
 \begin{abstract}
-Increasing amounts of scientific and social data are presented in the resource description framework (RDF); however, their use cases remain limited.
-Maximizing the value of accumulated RDF data is therefore considered a challenge, and efforts have been made to this end, including allowing access to RDF datasets through various interfaces beyond SPARQL and importing RDF datasets into various graph analysis engines.
-However, the interoperable management of graph data is challenging due to differences in existing models and formats, which depend on various implementations.
+How can we maximize the value of accumulated RDF data?
+Increasing amounts of scientific and social data are presented in the Resource Description Framework (RDF); however, their use cases remain limited.
+Importing RDF datasets into various graph analysis engines will enable access to the accumulated datasets through various application interfaces.
+However, the interoperable management of graph data is challenging due to differences in existing models and formats, which depend on implementations.
 In this study, we redefine the property graph (PG) model incorporating the differences in existing models and propose exchangeable serialization formats for PGs, which can be converted into specific formats for each database.
@@
 
-\section{Introduction}
+\section{Introduction }
 
@@
 SPARQL~\cite{sparql} is a protocol and query language that serves as a standardized interface for RDF data.
-This standardized format and interface enables the construction of integrated graph datasets.
+This standardized data model and interface enables the construction of integrated graph datasets.
 However, the lack of an interface for graph-based analysis and performant traversal limits use cases of the graph data.
@@
 These graph database engines support algorithms for traversing or analyzing graphs.
-However, few datasets are consistently described in the PG model, such that the application of these powerful engines is limited.
+However, few datasets are consistently described in the PG model  and the lack of ecosystem for exchanging data in the PG model limits the application of these powerful engines.
 
@@
 Another issue is that the transformation between RDF and PG is not straightforward due to the differences in their models. 
-In RDF graphs, all information is expressed by a triple (node-edge-node), whereas in PGs, arbitrary information can be contained in each node and edge as the key-value form. 
+In RDF graphs, all information is expressed by triples  (node-edge-node), whereas in PGs, arbitrary information can be contained in each node and edge as the key-value form. 
 Although this issue was previously addressed on the basis of predefined transformations~\cite{hartig},
@@
 
-%The contributions of this papers are 1) development of G2GML, 2) proposal of common property graph model and its serialization, 3) development of a prototype implementation, 4) construction of knowledge graph resources in a common format as Graph Archive.
+The main contributions of this study are as follows: 1) language design of G2GML; 2) its prototype implementation.
+Furthermore, we propose 3) the common PG model and its serialization, which are essential to ensure this mapping framework is independent from the implementations of databases.
 
-The main contributions of this study are as follows: 1) language design of G2GML; 2) its prototype implementation.
-Furthermore, we propose 3) the common PG model and its serialization, which are essential to ensure this mapping framework is independent from the implementations of database systems.
-
-%%%%%%%%%%%%%%%%%%%%%%%
 \section{Graph to Graph Mapping}
@@
 
-In this framework, users describe mappings from the RDF to PG in G2GML.
+In this framework, users describe mappings from RDF to PG in G2GML.
 According to this G2GML description, G2GML implementation converts the input RDF dataset into the PG dataset.
@@
 The G2GML is a declarative language that consists of pairs of RDF patterns and PG patterns. 
-The intuitive meaning of a G2GML can be represented by a map of RDF subgraphs, which matches the specified patterns to specified components of PGs.
-
-%As an entry point to the PG, we define serialization based on the PG model.
-%G2GML implementation converts the RDF dataset into a property graph dataset. The new dataset can also be saved in specific formats for loading into major graph database implementations.
+The intuitive meaning of a G2GML description can be represented by a map from RDF subgraphs, which matches the specified patterns, to components of PGs.
 
@@
 \center
-\includegraphics[width=1.0\textwidth]{dataflow.png}
+\includegraphics[width=1.0\textwidth]{dataflow.jpg}
 \caption{Overview of mapping from RDF to PG}
@@
 
-%%%%%%%%%%%%%%%%%%
 \subsection{G2GML}
@@
 It represents a domain-specific declarative language, where programmers only have to describe patterns of RDF and PG.
-The RDF pattern is described in terms of the SPARQL pattern, and the PG pattern is described using the Cypher pattern.
+The RDF pattern is described in terms of the SPARQL pattern, and the PG pattern is described in a syntax derived from openCypher \cite{openCypher}.
 
@@
 Similarly, an \textit{edge map} is a function that maps resources from an RDF graph to a set of \textit{PG edges}.
-%A G2GML description is a function that maps resources from an RDF graph to a set of PG nodes and edges that are mapped by all node and edge maps.
-Here, we define the syntax of the PG node pattern as follows. 
-\texttt{NEWLINE} is used an abstract symbol corresponding to the appropriate character to start a new line.
+Here, we define the syntax of G2GML as follows.
 
@@
 The only difference is that \texttt{INDENTED\_RDF\_PATTERN} must have one or more white spaces on top of each line.
-Symbols \texttt{node\_pat} \texttt{edge\_pat} are described according to the following definition.
+Symbols \texttt{node\_pat} \texttt{edge\_pat} are described according  to Definition \ref{defi:pgnode} and \ref{defi:pgedge}.\texttt{NEWLINE} is used an abstract symbol corresponding to the appropriate character to start a new line.
+A complete example of G2GML is shown in Section \ref{subsec:minimal-examples}.
 
-An RDF graph pattern in G2GML specifies the resources that should be mapped to PG nodes.
-Resources matching with these patterns yield solution sets of SELECT query in SPARQL, which are mapped to PG nodes by embedding variable bindings to corresponding locations according to the preceding PG node pattern.
-A complete example of G2GML is shown in Figure \ref{fig:example-g2g}.
-%TODO: consider the position of the example
-A node map is described as a pair of a PG node pattern and an RDF graph pattern.
-Here, we define the syntax of the PG node pattern as follows.
-Notably, \texttt{NODE}, \texttt{LABEL}, \texttt{PROP\_NAME}, and \texttt{PROP\_VAL} are all identifiers.
+An RDF graph pattern in G2GML specifies the resources that should be mapped to PG components.
+Variables in RDF graph patterns are embedded into the corresponding location in the preceding PG patterns, which yield resultant PGs.
+
+A node map is described as a pair of a PG node pattern and an RDF graph pattern. Here, we define the syntax of the PG node pattern as follows. 
 \begin{defi}[EBNF notation of PG node pattern]
+\label{defi:pgnode}
 \leavevmode
@@
 
+In Figure~\ref{defi:pgnode}, \texttt{NODE}, \texttt{LABEL}, \texttt{PROP\_NAME}, and \texttt{PROP\_VAL} are all identifiers.
 A PG node pattern specifies a node, a label, and properties to be generated by the map.
-The \texttt{NODE} symbol specifies the ID of the generated node, which is replaced by the resource retrieved by the RDF graph.
+The \texttt{NODE} symbol specifies the ID of the generated node, which is replaced by the resource retrieved from the RDF graph.
 The \texttt{LABEL} symbol specifies the label of the resultant node.
@@
 
-A PG edge pattern specifies the pattern of the edge, label, properties, as well as the source and destination nodes.
+On the other hand, a PG edge pattern specifies the pattern of the edge, label, properties, as well as the source and destination nodes.
 Here, we define the syntax of the PG edge pattern as follows.
-Notably, \texttt{SRC}, \texttt{SRC\_LAB}, \texttt{EDGE}, \texttt{EDGE\_LAB}, \texttt{DST}, and \texttt{DST\_LAB} are all identifiers.
 \begin{defi}[EBNF notation of PG edge pattern]
+\label{defi:pgedge}
 \leavevmode
@@
 edge_pat ::= "(" SRC  ":" SRC_LAB ") -" 
-                "[" EDGE?  ":" EDGE_LAB  ("{" prop_list "}")? ")" 
+             "[" EDGE?  ":" EDGE_LAB  ("{" prop_list "}")? "]" 
              ("->" | "-") "(" DST ":" DST_LAB ")"
@@
 
+In Figure~\ref{defi:pgedge}, \texttt{SRC}, \texttt{SRC\_LAB}, \texttt{EDGE}, \texttt{EDGE\_LAB}, \texttt{DST}, and \texttt{DST\_LAB} are all identifiers.
 Identifiers of \texttt{SRC} and \texttt{DST} specify the variables in the succeeding RDF graph pattern that should be mapped to endpoint nodes of resultant edges.
 A \texttt{SRC\_LAB} and a \texttt{DST\_LAB} serve not only as labels of resultant nodes, but also as implicit constraints of the edge map.
-%TODO add ref to example section.
-The resultant source and destination nodes must match patterns in the corresponding node maps.
+The resultant source and destination nodes must match patterns in the corresponding node maps (described in Section \ref{subsec:mapping-details} with a concrete example).
 For this reason, \texttt{SRC\_LAB} and \texttt{DST\_LAB} must be defined in other node maps.
@@
 
-The resultant edges can be either directed or undirected. If we use '\texttt{->}' as delimiter between an edge and a destination part, the edge will be a directed edge.
+The resultant edges can be either directed or undirected. If we use '\texttt{->}' as a delimiter between an edge and a destination part, the edge will be a directed edge.
 
@@
 
-%%%%%%%%%%%
 \subsection{Property Graph Model}
@@
 A \emph{property graph} is a tuple
-$PG = \langle N, E_d, E_u, S, V, P, e, l_n, l_e, p_n, p_e\rangle$, where:
+$PG = \langle N, E_d, E_u, e, l_n, l_e, p_n, p_e\rangle$, where:
 \begin{enumerate}
@@
     \item $E_u$ is a set of undirected edges.
-    \item $E$ is a set of edges, where $E = E_d \cup E_u$.
-    \item $S$ is a set of strings.
-    \item $V$ is a set of values of arbitrary data types.
-    \item $P$ is a set of properties. Each property assumes the form $p = \langle k,v \rangle$, where $k \in S$ and $v \in 2^V$.
-    \item $e: E \to \langle N \times N \rangle$ is a function that yields the endpoints of each directed or undirected edge (if the edge is directed, the first node is the source, and the second node is the destination).
-    \item $l_n : N \to 2^S$ is a function mapping each node to its multiple labels.
+    \item $e: E \to \langle N \times N \rangle$ is a function that yields the endpoints of each directed or undirected edge where $E := E_d \cup E_u$.
+If the edge is directed, the first node is the source, and the second node is the destination.
+    \item $l_n : N \to 2^S$ is a function mapping each node to its multiple labels where $S$ is a set of all strings.
     \item $l_e : E \to 2^S$ is a function mapping each edge to its multiple labels.
     \item $p_n : N \to 2^P$ is a function used to assign nodes to their multiple properties.
+$P$ is a set of properties.
+Each property assumes the form $p = \langle k,v \rangle$, where $k \in S$ and $v \in 2^V$.
+Here $V$ is a set of values of arbitrary data types.
     \item $p_e : E \to 2^P$ is a function used to assign edges to their multiple properties.
@@
 
-%%%%%%%%%%%%
 \subsection{Minimal Examples}
+\label{subsec:minimal-examples}
 Figure~\ref{fig:example-g2g} shows the minimal example of G2G mapping from RDF to PG data, representing the following five types of typical mapping.
@@
 
-%%%%%%%%%%%
 \subsection{Mapping Details}
+\label{subsec:mapping-details}
 The G2G mapping based on G2GML is generally intuitive, as shown above; however, there are several discussions regarding the details of mapping.
@@
 The node labels in edge maps must be defined in node maps (described in Section 2.2) to reference the conditions.
-This means that the conditions for defining `Person` are imported into the definition of `supervised\_by` and `emailed` relationships.
-Therefore, the `supervised\_by` relationship will be generated only between the nodes satisfying the `Person` condition.
+This means that the conditions for defining \texttt{Person} are imported into the definition of \texttt{supervised\_by} and \texttt{emailed} relationships.
+Therefore, the \texttt{supervised\_by} relationship will be generated only between the nodes satisfying the \texttt{Person} condition.
 In this manner, users can retrieve the PG datasets that are intuitively consistent (it is also possible to avoid specifying node labels).
-In contrast, edge conditions are not inherited to nodes, such that the nodes that do not have any `supervised\_by` nor `emailed` relationships are also generated.
+In contrast, edge conditions are not inherited to nodes, such that the nodes are retrieved without all relationships, \texttt{supervised\_by} and \texttt{emailed}.
+Although the nodes with no relationship also satisfy the conditions, the prototype implementation does not retrieve such orphan nodes by default from a practical perspective.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Use Cases}
@@
 
-Wikidata is a useful source of open data from various domains, and it is available in the form of RDF through the SPARQL interface.
+Wikidata is a useful source of open data from various domains.
 We present an example of mapping using a disease dataset from Wikidata, 
@@
 Figure~\ref{fig:wikidata_schema.png} illustrates the schematic relationships between those entities. 
-The subset of Wikidata can be extracted using the G2G mapping framework by writing a mapping file in G2GML (see Figure~\ref{fig:g2gml_wikidata}).
+The subset of Wikidata can be converted as a PG using the G2G mapping framework by writing a mapping file in G2GML (see Figure~\ref{fig:g2gml_wikidata}).
 Here, we focus on human genes and specify the necessary conditions in G2GML.
@@
 Further, each disease can have property \texttt{P2293} (genetic association), which is thereby linked to items of \texttt{Q7186} (gene).
-The numbers of obtained instances includes 4696 diseases, 4496 human genes, and 1287 drugs.
+The resultant PG includes 4696 diseases, 4496 human genes, and 1287 drugs.
 The total numbers of nodes and edges are summarized in Table~\ref{table:numbers}.
@@
 
-%--code--code--code--code--code--
 \begin{figure}[!t]
@@
 \end{scriptsize}
-\caption{G2GML for Wikidata extraction}
+\caption{G2GML for Wikidata mapping}
 \label{fig:g2gml_wikidata}
 \end{figure}
-%--code--code--code--code--code--
-
-% \begin{figure}
-% \center
-% \includegraphics[width=1.0\textwidth]{neo4jexample2.png}
-% \caption{Visualization on Neo4j}
-% \label{fig:neo4jexample2.png}
-% \end{figure}
 
@@
 Focusing on a relationship where two musicians (\texttt{?m1} and \texttt{?m2}) belong to the same group, this information can be represented in the PG shown in the right side of the figure.
+The relationships are originally presented as independent resources \texttt{?g}.
+In the mapping, we map \texttt{?g}, \texttt{?n}, and \texttt{?s} into a PG edge labeled 'sameGroup' with attributes.
+Such compaction  by mapping is useful in many use cases , for example, when users are just interested in relationships between musicians.
 
@@
 \includegraphics[width=1.0\textwidth]{example.jpg}
-\caption{Schematic example of graph to graph mapping}
+\caption{Schematic example of DBpedia mapping}
 \label{fig:conversion}
@@
 
-The mapping rule for the above example is specified in the G2GML description shown in Figure~\ref{fig:g2gml}.
-Following the prefix declaration for URIs used to write mappings, each mapping pattern is defined by a combination of a PG pattern in an unindented line and an RDF graph pattern in indented lines.
-The PG pattern is specified in a syntax derived from Cypher (the query language of Neo4j), whereas the RDF graph pattern is specified using a SPARQL code pattern.
-Variables in each mapping pattern are associated by their names across different data models. 
-In G2G mapping, the execution of the edge mappings is dependent on the node mappings, which means that edges are generated if and only if both nodes' and edges' patterns are matched with RDF graphs. 
-The example contains node mapping for \texttt{Musician} entities and edge mapping for \texttt{same\_group} relationships.
+The mapping rules for the example are specified in the G2GML description shown in Figure~\ref{fig:g2gml}.
+The G2GML description contains node mapping for \texttt{Musician} entities and edge mapping for \texttt{same\_group} relationships.
 In each specified PG pattern, \texttt{\{m, n, h\}} and \texttt{\{m1, m2, n, s\}} are used as variables to reconstruct resources and literals extracted from RDF graphs.
-%In this example, RDF literals are mapped to property values.
-%As a result, the specified RDF resources are reconstructed as nodes and edges in property graphs, while literals are mapped to property values.
 
-%# Prefixes
 \begin{figure}[!t]
@@
 \end{scriptsize}
-\caption{Example of G2GML}
+\caption{G2GML for DBpedia mapping}
 \label{fig:g2gml}
@@
 
+# Cypher
+MATCH (m1)-[:same_group]-(m2) RETURN DISTINCT m1.name, m2.name
+
 # PGQL
-SELECT DISTINCT m1.name, m2.name WHERE (m1)-[:same_group]-(m2)
+SELECT DISTINCT m1.name, m2.name MATCH (m1)-[:same_group]-(m2)
 \end{verbatim}
 \end{scriptsize}
-\caption{Example of SPARQL and PGQL queries}
+\caption{SPARQL, Cypher, and PGQL }
 \label{fig:sparql}
@@
 
-Figure~\ref{fig:sparql} shows the SPARQL query to retrieve the pairs of musicians that are in the same group.
-After the G2G mapping, we can load the generated property graph data into graph databases, such as Oracle Database, and the query can be written in PGQL~\cite{pgql} (the graph query language of Oracle Database).
+Figure~\ref{fig:sparql} shows queries to retrieve the pairs of musicians that are in the same group in SPARQL and graph query languages  ~\cite{openCypher}~\cite{pgql}.
+The queries in Cypher and PGQL are more succinct because of the simple structure of the PG obtained by G2G mapping.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Availability}
@@
 
-\noindent where the first argument is a G2GML mapping file, and the second argument is the target SPARQL endpoint, which provides the source RDF dataset. %from which the RDF dataset is extracted.
+\noindent where the first argument is a G2GML description file, and the second argument is the target SPARQL endpoint, which provides the source RDF dataset.
 
@@
 
-% \subsection{Graph Archive}
-% We created several G2GML mappings to extract public RDF from endpoint and construct knowledge graphs in PG format and resulting knowledge graphs as Graph Archive.
-
-% In the listed knowledge graphs, we compared the number of nodes and edges between RDF and property graphs.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Related Work}
+\section{Related Work }
 
@@
 However, considering the flexibility regarding the type of information that can be expressed by each edge in property graphs, a novel method for controlling the mapping is necessary.
+We discuss the comparison of controlled mapping and direct mapping in this section later.
+
 To the best of our knowledge, this study presents the first attempt to develop a framework for controlled mapping between RDF and PG. 
@@
 While the SPARQL CONSTRUCT clause defines mapping on the same data model, G2GML defines mapping between different data models.
-%Currently, it is limited to the mapping from RDF to property graphs, it can be extended to the mapping from property graph to RDF.
-However, if mapping includes the SPARQL pattern that are not declarative, it is not applicable for generating RDF triples.
 Thus, G2GML is considered as a specific extension of the SPARQL CONSTRUCT clause for generation or inference of PG data.
-%Future works include further analysis of the converted graph data on the database engines adopting the property graph model.
 
-A previous study compared the performance of Blazegraph and Neo4j. They concluded that RDF has an advantage in terms of performance and interoperability.
+A previous study compared the performance of RDF triple stores, such as Blazegraph and Virtuoso, and Neo4j~\cite{alocci}.
+They concluded that RDF has an advantage in terms of performance and interoperability.
+However, they tested only Neo4j for PG model.
+It will be necessary to update of such benchmarks using more implementations, which requires improved interoperability and standardization of the PG model.
+Our work will contribute the improved interoperability of PG model, although the continuous discussion is necessary for the standardization of query language for the PG model to achieve an interoperable ecosystem of RDF and PG and a more fair benchmarking.
 
@@
 
-\section{Conclusion}
-We redefined the PG model independent of specific graph database implementations and proposed serialization formats based on the data model.
-We further designed the G2GML for mapping RDF graphs to PGs and developed a prototype implementation of G2GML, which is publicly available.
-Our data model and mapping framework increase the interoperability of existing graph databases and make it easier for users to create, exchange, and utilize graph data.
+\section{Conclusion   }
+
+We designed G2GML, a framework for mapping RDF graphs to PGs, and developed prototype implementation of G2GML, which is publicly available.
+For the clear definition of this mapping, we defined the PG model independent of specific graph database implementations and proposed its serialization formats.
+
+The advantage of using RDF is that different applications can retrieve necessary information from the same integrated datasets because of the interoperable nature of semantic modeling.
+
+For such increasing RDF resources, graph databases are potentially the ideal data storage as property graph model can naturally preserve the relationship information which semantically defined in RDF.
+G2GML plays a key role in this data transformation process.
+
+Various graph database implementations are actively developed and its query language standardization is currently on going.
+We expect that G2GML or its enhanced mapping framework will be supported by database management systems and other software.
+We believe our initial effort of generalization and the prototype implementation promote further discussion.
 
@@
 
-\bibitem{Alocci}
+\bibitem{alocci}
 Alocci, D., Mariethoz, J., Horlacher, O., Bolleman, J.
@@
 R2RML: RDB to RDF Mapping Language, W3C Recommendation 27 September 2012 \url{https://www.w3.org/TR/r2rml/}
+
+\bibitem{openCypher}
+openCypher, \url{https://www.opencypher.org/}
 

### 2020-05-25 paper.tex
submitted

@@
 How can we maximize the value of accumulated RDF data?
-Increasing amounts of scientific and social data are presented in the Resource Description Framework (RDF); however, their use cases remain limited.
-Importing RDF datasets into various graph analysis engines will enable access to the accumulated datasets through various application interfaces.
-However, the interoperable management of graph data is challenging due to differences in existing models and formats, which depend on implementations.
-In this study, we redefine the property graph (PG) model incorporating the differences in existing models and propose exchangeable serialization formats for PGs, which can be converted into specific formats for each database.
-The serialization formats that are independent of certain database implementations increase the interoperability of graph databases and make it easier for users to import accumulated graph data.
-We further propose a framework for mapping RDF graphs to PGs based on the graph to graph mapping language (G2GML).
-Using this framework, accumulated graph data described in RDF can be converted into PGs, which can then be loaded into several graph database engines for further analysis.
+Whereas the RDF data can be queried using the SPARQL language, even the SPARQL-based operation has a limitation in implementing traversal or analytical algorithms.
+Recently, a variety of database implementations dedicated to analyses on the property graph (PG) model have emerged.
+Importing RDF datasets into these graph analysis engines will enable access to the accumulated datasets through various application interfaces.
+However, the RDF model and the PG model are not interoperable.
+Here, we developed a framework based on the Graph to Graph Mapping Language (G2GML) for mapping RDF graphs to PGs to make the most of accumulated RDF data.
+Using this framework, accumulated graph data described in the RDF model can be converted to the PG model, which can then be loaded to graph database engines for further analysis.
+For supporting different graph database implementations, we redefined the PG model and proposed its exchangeable serialization formats.
+We demonstrate several use cases, where publicly available RDF data are extracted and converted to PGs.
+This study bridges RDF and PGs and contributes to interoperable management of knowledge graphs, thereby expanding the use cases of accumulated RDF data.
 
@@
 
-\section{Introduction }
+\section{Introduction}
 
 Increasing amounts of scientific and social data are being published in the form of the Resource Description Framework (RDF)~\cite{rdf}, which presently constitutes a large open data cloud.
-DBpedia~\cite{dbpedia} and Wikidata~\cite{wikidata} are good examples of such RDF datasets.
+DBpedia~\cite{dbpedia} and Wikidata~\cite{wikidata} are well-known examples of such RDF datasets.
 SPARQL~\cite{sparql} is a protocol and query language that serves as a standardized interface for RDF data.
-This standardized data model and interface enables the construction of integrated graph datasets.
+This standardized data model and interface enables the construction of integrated graph data.
 However, the lack of an interface for graph-based analysis and performant traversal limits use cases of the graph data.
 
-Recently, the property graph (PG) model~\cite{angles1,angles2} has been attracting increasing attention in the context of graph analysis.
+Recently, the property graph (PG) model~\cite{angles1,angles2} has been increasingly attracting attention in the context of graph analysis.
 Various graph database engines, including Neo4j~\cite{neo4j}, Oracle Database~\cite{oracle}, and Amazon Neptune~\cite{neptune} adopt this model.
 These graph database engines support algorithms for traversing or analyzing graphs.
-However, few datasets are consistently described in the PG model  and the lack of ecosystem for exchanging data in the PG model limits the application of these powerful engines.
+However, few datasets are published in the PG model and the lack of an ecosystem for exchanging data in the PG model limits the application of these powerful engines.
 
-In light of this situation, developing a method to transform RDF into PG would be highly valuable. One of the practical issues faced by this challenge is the lack of a standardized PG model.
+In the light of this situation, developing a method to transform RDF into PG would be highly valuable. One of the practical issues faced by this challenge is the lack of a standardized PG model.
 Another issue is that the transformation between RDF and PG is not straightforward due to the differences in their models. 
@@
 In this study, we redefine the PG model incorporating the differences in existing models and propose serialization formats based on the data model.
-We further propose a graph to graph mapping framework based on the graph to graph mapping language (G2GML).
-Employing this mapping framework, accumulated graph data described in the RDF can be converted into PGs, which can be loaded into several graph database engines for further analysis.
-We demonstrate several use cases, where publicly available RDF data is extracted and converted to PGs, and evaluate the performance.
-Thus, this study provides the foundation for the interoperability of knowledge graphs.
+We further propose a graph to graph mapping framework based on the Graph to Graph Mapping Language (G2GML).
+Employing this mapping framework, accumulated graph data described in RDF can be converted into PGs, which can then be loaded into several graph database engines for further analysis.
+We demonstrate several use cases, where publicly available RDF data is extracted and converted to PGs.
+Thus, this study provides the foundation for the interoperability between knowledge graphs.
 
-The main contributions of this study are as follows: 1) language design of G2GML; 2) its prototype implementation.
-Furthermore, we propose 3) the common PG model and its serialization, which are essential to ensure this mapping framework is independent from the implementations of databases.
+The main contributions of this study are as follows: 1) language design of G2GML and 2) its prototype implementation.
+Furthermore, we propose 3) the common PG model and its serialization, which are essential to ensure that this mapping framework is independent from the implementations of databases.
 
@@
 In this framework, users describe mappings from RDF to PG in G2GML.
-According to this G2GML description, G2GML implementation converts the input RDF dataset into the PG dataset.
+According to this G2GML description, the input RDF dataset is converted into a PG dataset.
 The new dataset can also be optionally saved in specific formats for loading into major graph database implementations.
 
-The G2GML is a declarative language that consists of pairs of RDF patterns and PG patterns. 
-The intuitive meaning of a G2GML description can be represented by a map from RDF subgraphs, which matches the specified patterns, to components of PGs.
+G2GML is a declarative language comprising pairs of RDF patterns and PG patterns. 
+The core concept of a G2GML description can be represented by a map from RDF subgraphs, which matches specified SPARQL patterns, to PG components.
 
@@
 
-G2GML is a language applied to describe maps from RDF graphs to PGs.
+G2GML is a language to describe maps from RDF graphs to PGs.
 It represents a domain-specific declarative language, where programmers only have to describe patterns of RDF and PG.
-The RDF pattern is described in terms of the SPARQL pattern, and the PG pattern is described in a syntax derived from openCypher \cite{openCypher}.
+The RDF pattern is described in terms of the SPARQL syntax, and the PG pattern is described in a syntax derived from openCypher \cite{openCypher}.
 
 \begin{prel}
-An RDF triple $(s, p, o)$ is an element of $(I \cup B) \times I \times (I \cup B \cup L)$, where $I$, $L$, and $B$ are a set of IRIs, a set of literals, and a set of blank nodes, which are considered pairwise disjoint.
-In this study, an RDF triple is simply referred to as a triple.
-For a triple $(s, p, o)$, $s$ is the subject, $p$ the predicate, and $o$ the object.
-An RDF graph is defined as a finite set of triples.
+An RDF triple $(s, p, o)$ is an element of $(I \cup B) \times I \times (I \cup B \cup L)$, where $I$, $L$, and $B$ are a set of IRIs, a set of literals, and a set of blank nodes, respectively, which are considered pairwise disjoint.
+For an RDF triple $(s, p, o)$, $s$ is the subject, $p$ the predicate, and $o$ the object.
+An RDF graph is defined as a finite set of RDF triples.
 \end{prel}
@@
 \par
-A G2GML description consists of one or more \textit{node maps} and \textit{edge maps}.
+A G2GML description comprises one or more \textit{node maps} and \textit{edge maps}.
 A \textit{node map} is a function that maps resources from an RDF graph to a set of \textit{PG nodes}. 
@@
  and \texttt{INDENTED\_RDF\_PATTERN} are almost the same as \textit{PrefixDecl} and \textit{GroupGraphPattern} in SPARQL syntax (see EBNF notation of SPARQL grammar~\cite{sparql}).
-The only difference is that \texttt{INDENTED\_RDF\_PATTERN} must have one or more white spaces on top of each line.
-Symbols \texttt{node\_pat} \texttt{edge\_pat} are described according  to Definition \ref{defi:pgnode} and \ref{defi:pgedge}.\texttt{NEWLINE} is used an abstract symbol corresponding to the appropriate character to start a new line.
-A complete example of G2GML is shown in Section \ref{subsec:minimal-examples}.
+The only difference is that \texttt{INDENTED\_RDF\_PATTERN} must have one or more white spaces at the beginning of each line.
+The symbols \texttt{node\_pat} and \texttt{edge\_pat} are described according to Definition \ref{defi:pgnode} and \ref{defi:pgedge}.
+\texttt{NEWLINE} is used as an abstract symbol corresponding to the appropriate character to start a new line.
+Minimal examples of G2GML are shown in Section \ref{subsec:minimal-examples}.
 
@@
 
-In Figure~\ref{defi:pgnode}, \texttt{NODE}, \texttt{LABEL}, \texttt{PROP\_NAME}, and \texttt{PROP\_VAL} are all identifiers.
+In Definition~\ref{defi:pgnode}, \texttt{NODE}, \texttt{LABEL}, \texttt{PROP\_NAME}, and \texttt{PROP\_VAL} are all identifiers.
 A PG node pattern specifies a node, a label, and properties to be generated by the map.
@@
 Therefore, the identifier of each label must be unique in a G2GML description.
-Each node pattern contains zero or more properties as \texttt{prop\_list}.
+Each node pattern contains zero or more properties in a \texttt{prop\_list}.
 A \texttt{property} is a pair of \texttt{PROP\_NAME} and \texttt{PROP\_VAL} that describes the properties of nodes.
-Identifiers \texttt{NODE} and \texttt{PROP\_VAL} must be names of variables in the succeeding RDF graph pattern, while \texttt{LABEL} and \texttt{PROP\_NAME} are regarded as text literals.
+The identifiers \texttt{NODE} and \texttt{PROP\_VAL} must be names of variables in the succeeding RDF graph pattern, while \texttt{LABEL} and \texttt{PROP\_NAME} are regarded as text literals.
 
-On the other hand, a PG edge pattern specifies the pattern of the edge, label, properties, as well as the source and destination nodes.
+In contrast, a PG edge pattern specifies the pattern of the edge itself, its label, and properties, as well as the source and destination nodes.
 Here, we define the syntax of the PG edge pattern as follows.
@@
 
-In Figure~\ref{defi:pgedge}, \texttt{SRC}, \texttt{SRC\_LAB}, \texttt{EDGE}, \texttt{EDGE\_LAB}, \texttt{DST}, and \texttt{DST\_LAB} are all identifiers.
-Identifiers of \texttt{SRC} and \texttt{DST} specify the variables in the succeeding RDF graph pattern that should be mapped to endpoint nodes of resultant edges.
+In Definition~\ref{defi:pgedge}, \texttt{SRC}, \texttt{SRC\_LAB}, \texttt{EDGE}, \texttt{EDGE\_LAB}, \texttt{DST}, and \texttt{DST\_LAB} are all identifiers.
+Identifiers of \texttt{SRC} and \texttt{DST} specify the variables in the succeeding RDF graph pattern that should be mapped to the endpoint nodes of resultant edges.
 A \texttt{SRC\_LAB} and a \texttt{DST\_LAB} serve not only as labels of resultant nodes, but also as implicit constraints of the edge map.
@@
 
-The resultant edges can be either directed or undirected. If we use '\texttt{->}' as a delimiter between an edge and a destination part, the edge will be a directed edge.
+The resultant edges can be either directed or undirected. If '\texttt{->}' is used as a delimiter between an edge and a destination part, the edge will be  directed.
 
-In node and edge maps, a variable bound to \texttt{PROP\_VAL} may have multiple candidates against a single node or edge.
+In node and edge maps, a variable bound to \texttt{PROP\_VAL} may have multiple candidates for a single node or edge.
 If multiple candidates exist, they are concatenated into an array in the same manner as GROUP\_CONCAT in SPARQL.
@@
 According to our definition of the PG model, we propose serialization in flat text and JSON.
-The flat text format (PG format) performs better in terms of human readability and line-oriented processing, while the JSON format (JSON-PG format) is best used for server-client communication.
+The flat text format (PG format) performs better in terms of human readability and line-oriented processing, while the JSON format (JSON-PG format) is best used for server--client communication.
 
-The PG format has the following characteristics, and an example is given in Figure~\ref{fig:example-pg}.
+The PG format has the following characteristics. An example is given in Figure~\ref{fig:example-pg}.
 
@@
     \item Each line describes a node or an edge.
-    \item All the elements in each line are separated by spaces or tabs.
-    \item In each of the node lines, the first column contains the node ID.
-    \item In each of the edge lines, the first three columns contain the source node ID, direction, and destination node ID.
+    \item All elements in a line are separated by spaces or tabs.
+    \item The first column of a node line contains the node ID.
+    \item The first three columns of an edge line contain the source node ID, direction, and destination node ID.
     \item Each line can contain an arbitrary number of labels.
@@
 \begin{itemize}
-    \item Resource to node: In line 2-4, the RDF resources with type \texttt{:Person} are mapped into the PG nodes using their IRIs as node IDs.
-    \item Datatype property to node property: In line 2-4, the RDF datatype property \texttt{:name} is mapped onto the PG node property key \texttt{name}.
+    \item Resource to node: In lines 2--4, the RDF resources with type \texttt{:Person} are mapped into the PG nodes using their IRIs as node IDs.
+    \item Datatype property to node property: In lines 2--4, the RDF datatype property \texttt{:name} is mapped onto the PG node property key \texttt{name}.
 The literal objects 'Alice' and 'Bob' are mapped onto the node property values.
-    \item Object property to edge: In line 5-6, the RDF object property \texttt{:supervised\_by} is mapped onto the PG edge \texttt{supervised\_by}.
-    \item Resource to edge: In line 7-10, the RDF resource with type \texttt{:Email} is mapped onto the PG edge \texttt{emailed}. 
-    \item Datatype property to edge property: In line 7-10, the RDF datatype property \texttt{:year} and \texttt{:attachment} are mapped onto the PG edge property \texttt{year} and \texttt{attachment}.
+    \item Object property to edge: In lines 5--6, the RDF object property \texttt{:supervised\_by} is mapped onto the PG edge \texttt{supervised\_by}.
+    \item Resource to edge: In lines 7--10, the RDF resource with type \texttt{:Email} is mapped onto the PG edge \texttt{emailed}. 
+    \item Datatype property to edge property: In lines 7--10, the RDF datatype property \texttt{:year} and \texttt{:attachment} are mapped onto the PG edge property \texttt{year} and \texttt{attachment}.
 The literal objects \texttt{2017} and \texttt{01.pdf} are mapped onto the edge property values.
@@
 \label{subsec:mapping-details}
-The G2G mapping based on G2GML is generally intuitive, as shown above; however, there are several discussions regarding the details of mapping.
+The G2G mapping based on G2GML is designed to be intuitive in general as shown above; however, there are several discussions regarding the details of mapping.
 
@@
 Figure~\ref{fig:wikidata_schema.png} illustrates the schematic relationships between those entities. 
-The subset of Wikidata can be converted as a PG using the G2G mapping framework by writing a mapping file in G2GML (see Figure~\ref{fig:g2gml_wikidata}).
+This subset of Wikidata can be converted as a PG using the G2G mapping framework by writing a mapping file in G2GML (see Figure~\ref{fig:g2gml_wikidata}).
 Here, we focus on human genes and specify the necessary conditions in G2GML.
 Each instance of \texttt{Q12136} (disease) can have a property \texttt{P2176} (drug used for treatment), which is thereby linked to items of \texttt{Q12140} (medication).
-Further, each disease can have property \texttt{P2293} (genetic association), which is thereby linked to items of \texttt{Q7186} (gene).
+Further, each disease can have a property \texttt{P2293} (genetic association), which is thereby linked to items of \texttt{Q7186} (gene).
 The resultant PG includes 4696 diseases, 4496 human genes, and 1287 drugs.
@@
 Figure~\ref{fig:conversion} schematically illustrates an example of the G2G mapping to convert RDF data retrieved from DBpedia into PG data. 
-Focusing on a relationship where two musicians (\texttt{?m1} and \texttt{?m2}) belong to the same group, this information can be represented in the PG shown in the right side of the figure.
+Focusing on a relationship where two musicians (\texttt{?m1} and \texttt{?m2}) belong to the same group, this information can be represented in the PG shown on the right side of the figure.
 The relationships are originally presented as independent resources \texttt{?g}.
-In the mapping, we map \texttt{?g}, \texttt{?n}, and \texttt{?s} into a PG edge labeled 'sameGroup' with attributes.
-Such compaction  by mapping is useful in many use cases , for example, when users are just interested in relationships between musicians.
+In the mapping, we map \texttt{?g}, \texttt{?n}, and \texttt{?s} onto a PG edge labeled 'sameGroup' with attributes.
+Such compaction by mapping is useful in many use cases, for example, when users are just interested in relationships between musicians.
 
@@
 
-The mapping rules for the example are specified in the G2GML description shown in Figure~\ref{fig:g2gml}.
+The mapping rules for this example are specified in the G2GML description shown in Figure~\ref{fig:g2gml}.
 The G2GML description contains node mapping for \texttt{Musician} entities and edge mapping for \texttt{same\_group} relationships.
@@
 \end{scriptsize}
-\caption{SPARQL, Cypher, and PGQL }
+\caption{SPARQL, Cypher, and PGQL}
 \label{fig:sparql}
@@
 Figure~\ref{fig:sparql} shows queries to retrieve the pairs of musicians that are in the same group in SPARQL and graph query languages ~\cite{openCypher}~\cite{pgql}.
-The queries in Cypher and PGQL are more succinct because of the simple structure of the PG obtained by G2G mapping.
+The queries in Cypher and PGQL are more succinct owing to the simple structure of the PG obtained by G2G mapping.
 
@@
 
-Furthermore, its Docker image (\url{https://hub.docker.com/r/g2glab/g2g}) and a demonstration site of G2G mapping framework (\url{http://g2g.fun}) are also available (Figure~\ref{fig:sandbox}).
+Furthermore, a Docker image (\url{https://hub.docker.com/r/g2glab/g2g}) and a demonstration site of the G2G mapping framework (\url{http://g2g.fun}) are also available (Figure~\ref{fig:sandbox}).
 
@@
 
-\section{Related Work }
+\section{Related Work}
 
 \subsection{Property Graph Model and Serialization}
-Recently, graph data have attracted increasing attention, leading to a plethora of database implementations. 
+Recently, graph data has increasingly attracted attention, leading to a plethora of database implementations. 
 Thus far, different data models and query languages have been available for these graph database implementations.
@@
 Future studies should address collaboration and standardization of the data model.
-In particular, our serialization has implementation for some of the major database engines and also has a potential to further cover various database engines.  
-The serialization formats that are independent of certain database implementations will increase the interoperability of graph databases and make it easier for users to import accumulated graph data.
+In particular, our serialization has implementations for some of the major database engines and has the potential to further cover various database engines. 
+The serialization formats that are independent of specific database implementations will increase the interoperability of graph databases and make it easier for users to import accumulated graph data.
 %In G2G mapping, PG format works as a gateway from RDF to property graphs.
@@
 The interoperability of RDF and PG~\cite{hartig,angles4,das,thakkar} has been discussed, and efforts were made to develop methods to convert RDF into PG~\cite{tomaszuk1,virgilio}.
-However, considering the flexibility regarding the type of information that can be expressed by each edge in property graphs, a novel method for controlling the mapping is necessary.
-We discuss the comparison of controlled mapping and direct mapping in this section later.
+However, considering the flexibility regarding the type of information that can be expressed by edges in property graphs, a novel method for controlling the mapping is necessary.
+We discuss the comparison of controlled mapping and direct mapping later in this section.
 
@@
 They concluded that RDF has an advantage in terms of performance and interoperability.
-However, they tested only Neo4j for PG model.
-It will be necessary to update of such benchmarks using more implementations, which requires improved interoperability and standardization of the PG model.
-Our work will contribute the improved interoperability of PG model, although the continuous discussion is necessary for the standardization of query language for the PG model to achieve an interoperable ecosystem of RDF and PG and a more fair benchmarking.
+However, as PG model, they tested only Neo4j.
+It will be necessary to update such benchmarks using additional implementations, which requires improved interoperability and standardization of the PG model.
+Our study is expected to contribute to the improved interoperability of PG models, although a continuous discussion is necessary for the standardization of query language for the PG model, in order to achieve an interoperable ecosystem of both RDF and PG, and a fair benchmarking.
 
@@
 When the source RDF dataset is retrieved from the public web space, it is inefficient (or even unrealistic) to convert the whole connected dataset.
-In G2GML, users specify the resources they need, such that the SPARQL endpoints can return the filtered dataset.
+In G2GML, users can specify the resources they need, such that the SPARQL endpoints can return the filtered dataset.
 (This design is described in Section 2.2.)
@@
 Mapping details - There is no common ruleset to uniquely map RDF terms to PG elements (labels, key-value pairs of properties) and to name new PG elements.
-Further, the conversion rules of multi-edges and list of property values (discussed in Section 2.6) are not always obvious to users.
-Therefore, the defining method of the mapping details is necessary to create precise data in actual usage.
+Further, the conversion rules of multi-edges and lists of property values (discussed in Section 2.6) are not always obvious to users.
+Therefore, defining a method for mapping details is necessary to create precise data in actual use cases.
 
@@
 
-We find a similar discussion in the conversion from the relational model to RDF, where are two W3C standards, i.e., Direct Mapping~\cite{dm} and R2RML~\cite{r2rml}.
+We observe a similar discussion in the conversion from the relational model to RDF, where are two W3C standards, i.e., Direct Mapping~\cite{dm} and R2RML~\cite{r2rml}.
 
-\section{Conclusion   }
+\section{Conclusion}
 
-We designed G2GML, a framework for mapping RDF graphs to PGs, and developed prototype implementation of G2GML, which is publicly available.
-For the clear definition of this mapping, we defined the PG model independent of specific graph database implementations and proposed its serialization formats.
+We designed the G2GML for mapping RDF graphs to PGs and developed its prototype implementation.
+To ensure a clear definition of this mapping, we defined the PG model independent of specific graph database implementations and proposed its exchangeable serialization formats.
 
-The advantage of using RDF is that different applications can retrieve necessary information from the same integrated datasets because of the interoperable nature of semantic modeling.
+The advantage of using RDF is that different applications can retrieve necessary information from the same integrated datasets owing to the interoperable nature of semantic modeling.
 
-For such increasing RDF resources, graph databases are potentially the ideal data storage as property graph model can naturally preserve the relationship information which semantically defined in RDF.
-G2GML plays a key role in this data transformation process.
+For such increasing RDF resources, graph databases are potentially the ideal data storage as the property graph model can naturally preserve the relationship information semantically defined in RDF.
+G2GML therefore plays an important role in this data transformation process.
 
-Various graph database implementations are actively developed and its query language standardization is currently on going.
-We expect that G2GML or its enhanced mapping framework will be supported by database management systems and other software.
-We believe our initial effort of generalization and the prototype implementation promote further discussion.
+Various graph database implementations are actively developed and standardization of query languages is currently ongoing.
+We expect that the G2GML or its enhanced mapping framework will be supported by database management systems and other software.
+We believe that our efforts of generalization and prototype implementation will promote further discussion.
 
@@
 We thank Yuka Tsujii for helping create the figures.
-We thank Ramona Roess for careful review of the manuscript and useful comments.
+We thank Ramona Röß for careful review of the manuscript and useful comments.
 

### 2020-08-15 paper.tex

@@
 
-Recently, the property graph (PG) model~\cite{angles1,angles2} has been increasingly attracting attention in the context of graph analysis.
+Recently, the property graph (PG) model~\cite{angles1,angles2} has been increasingly attracting attention in the context of graph analysis~\cite{agri}.
 Various graph database engines, including Neo4j~\cite{neo4j}, Oracle Database~\cite{oracle}, and Amazon Neptune~\cite{neptune} adopt this model.
@@
 
-The PG format has the following characteristics. An example is given in Figure~\ref{fig:example-pg}.
+The PG format has the following characteristics. An example is given in Figure~\ref{fig:example-pg}, which is visualized in Figure~\ref{fig:pg_example5}.
 
@@
  label      ::= ":" STRING
- property   ::= STRING ":" value
- value      ::= STRING | NUMBER
+ property   ::= STRING ":" VALUE
  direction  ::= "--" | "->"
@@
 \end{defi}
+
+According to this definition, each property value of PGs is a set of items of any datatype.
+Meanwhile, our G2G mapping prototype implementation currently supports the main three datatypes (integer, double, and string) as property value, and those types are inferred from the serialized values.
 
@@
 \includegraphics[width=0.5\textwidth]{pg_example5.png}
-\caption{Example of output PG data}
+\caption{Visualization of Figure 5}
 \label{fig:pg_example5}
@@
 
+For the future adoption of this framework, we expect two scenarios: The use of the standalone G2G mapping tools, such as our implementation, for generating PG datasets from RDF resources.
+Also, the adoption of the framework within the database management systems which support both RDF and PG datasets.
+
 \section{Related Work}
@@
 
+\bibitem{agri}
+Abad-Navarro, F., Bernabé-Diaz, J.
+A., García-Castro, A., & Fernandez-Breis, J.
+T.
+(2020).
+Semantic Publication of Agricultural Scientific Literature Using Property Graphs.
+Applied Sciences, 10(3), 861.
+
 % \bibitem{ref_article1}

### 2020-08-15 paper.tex
Unify the casing of pg labels and properties

@@
 According to this definition, each property value of PGs is a set of items of any datatype.
-Meanwhile, our G2G mapping prototype implementation currently supports the main three datatypes (integer, double, and string) as property value, and those types are inferred from the serialized values.
+Meanwhile, our G2G mapping prototype implementation currently supports the main three datatypes (integer, double, and string) as property value, and those types are inferred from the format of serialized values.
 
@@
 # NODES
-101  :Person  name:Alice  age:15  country:"United States"
-102  :Person  :Student  name:Bob  country:Japan  country:Germany
+101  :person  name:Alice  age:15  country:"United States"
+102  :person  :student  name:Bob  country:Japan  country:Germany
 
 # EDGES
-101 -- 102  :sameSchool  :sameClass  since:2012
+101 -- 102  :same_school  :same_class  since:2012
 102 -> 101  :likes  since:2015
@@
 PREFIX : <http://example.org/>
-(p:Person {name:n})
+(p:person {name:n})
     ?p a :Person .
     ?p :name ?n .
-(p1:Person)-[:supervised_by]->(p2:Person)
+(p1:person)-[:supervised_by]->(p2:person)
     ?p1 :supervised_by ?p2 .
@@
 The node labels in edge maps must be defined in node maps (described in Section 2.2) to reference the conditions.
-This means that the conditions for defining \texttt{Person} are imported into the definition of \texttt{supervised\_by} and \texttt{emailed} relationships.
-Therefore, the \texttt{supervised\_by} relationship will be generated only between the nodes satisfying the \texttt{Person} condition.
+This means that the conditions for defining \texttt{person} are imported into the definition of \texttt{supervised\_by} and \texttt{emailed} relationships.
+Therefore, the \texttt{supervised\_by} relationship will be generated only between the nodes satisfying the \texttt{person} condition.
 In this manner, users can retrieve the PG datasets that are intuitively consistent (it is also possible to avoid specifying node labels).
@@
 \begin{verbatim}
-"http://example.org/person1" :Person name:Alice
-"http://example.org/person2" :Person name:Bob
+"http://example.org/person1" :person name:Alice
+"http://example.org/person2" :person name:Bob
 "http://example.org/person1" -> "http://example.org/person2" :emailed year:2017
@@
 
-"http://example.org/person1" :Person name:Alice
-"http://example.org/person2" :Person name:Bob
+"http://example.org/person1" :person name:Alice
+"http://example.org/person2" :person name:Bob
 "http://example.org/person1" -> "http://example.org/person2" :emailed year:2017 attachment:"01.pdf" attachment:"02.pdf"
@@
 
-(g:HumanGene {symbol: s})
+(g:human_gene {symbol: s})
     ?g wdt:P31 wd:Q7187 ;      # "instance of" "gene"
@@
 
-(d:Disease {name: n})
+(d:disease {name: n})
     ?d wdt:P31 wd:Q12136 ;     # "instance of" "disease"
@@
 
-(m:Drug {name: n})
+(m:drug {name: n})
     ?m wdt:P31 wd:Q12140 ;     # "instance of" "medication"
@@
 
-(d:Disease)-[:hasAssociatedGene]->(g:HumanGene)
+(d:disease)-[:has_associated_gene]->(g:human_gene)
     ?d wdt:P2293 ?g .          # "genetic association"
 
-(d:Disease)-[:hasDrug]->(m:Drug)
+(d:disease)-[:has_drug]->(m:drug)
     ?d wdt:P2176 ?m .          # "drug used for treatment"
@@
 The relationships are originally presented as independent resources \texttt{?g}.
-In the mapping, we map \texttt{?g}, \texttt{?n}, and \texttt{?s} onto a PG edge labeled 'sameGroup' with attributes.
+In the mapping, we map \texttt{?g}, \texttt{?n}, and \texttt{?s} onto a PG edge labeled 'same_group' with attributes.
 Such compaction by mapping is useful in many use cases, for example, when users are just interested in relationships between musicians.
@@
 The mapping rules for this example are specified in the G2GML description shown in Figure~\ref{fig:g2gml}.
-The G2GML description contains node mapping for \texttt{Musician} entities and edge mapping for \texttt{same\_group} relationships.
+The G2GML description contains node mapping for \texttt{musician} entities and edge mapping for \texttt{same\_group} relationships.
 In each specified PG pattern, \texttt{\{m, n, h\}} and \texttt{\{m1, m2, n, s\}} are used as variables to reconstruct resources and literals extracted from RDF graphs.
@@
 # Node mapping
-(m:Musician {name:n, hometown:h})                            # PG Pattern
+(m:musician {name:n, hometown:h})                            # PG Pattern
     ?m rdf:type foaf:Person , dbo:MusicalArtist ;            # RDF Pattern
@@
 # Edge mapping
-(m1:Musician)-[:sameGroup {name:n, since:s}]-(m2:Musician)   # PG Pattern
+(m1:musician)-[:same_group {name:n, since:s}]-(m2:musician)   # PG Pattern
     ?g rdf:type schema:MusicGroup ;                          # RDF Pattern

### 2020-08-19 paper.tex
Reflect changes of the demo paper

@@
 %
-\author{Hirokazu Chiba\inst{1} \and Ryota Yamanaka\inst{2} \and Shota Matsumoto\inst{3}}
+\author{Hirokazu Chiba\inst{1}\orcidID{0000-0003-4062-8903} \and Ryota Yamanaka\inst{2} \and Shota Matsumoto\inst{3}}
 %
 \authorrunning{H. Chiba {\itshape et al.}}
+
+\setlength\abovecaptionskip{-0.5ex}
 % First names are abbreviated in the running head.
@@
 Recently, a variety of database implementations dedicated to analyses on the property graph (PG) model have emerged.
-Importing RDF datasets into these graph analysis engines will enable access to the accumulated datasets through various application interfaces.
+Importing RDF datasets into these graph analysis engines provides access to the accumulated datasets through various application interfaces.
 However, the RDF model and the PG model are not interoperable.
@@
 G2GML is a declarative language comprising pairs of RDF patterns and PG patterns. 
-The core concept of a G2GML description can be represented by a map from RDF subgraphs, which matches specified SPARQL patterns, to PG components.
+The core concept of a G2GML description can be represented by a map from RDF subgraphs, which match specified SPARQL patterns, to PG components.
 
@@
     \item Datatype property to node property: In lines 2--4, the RDF datatype property \texttt{:name} is mapped onto the PG node property key \texttt{name}.
-The literal objects 'Alice' and 'Bob' are mapped onto the node property values.
+The literal objects \texttt{'Alice'} and \texttt{'Bob'} are mapped onto the node property values.
     \item Object property to edge: In lines 5--6, the RDF object property \texttt{:supervised\_by} is mapped onto the PG edge \texttt{supervised\_by}.
-    \item Resource to edge: In lines 7--10, the RDF resource with type \texttt{:Email} is mapped onto the PG edge \texttt{emailed}. 
-    \item Datatype property to edge property: In lines 7--10, the RDF datatype property \texttt{:year} and \texttt{:attachment} are mapped onto the PG edge property \texttt{year} and \texttt{attachment}.
-The literal objects \texttt{2017} and \texttt{01.pdf} are mapped onto the edge property values.
+    \item Resource to edge: In lines 7--12, the RDF resource with type \texttt{:Email} is mapped onto the PG edge \texttt{emailed}. 
+    \item Datatype property to edge property: In lines 7--12, the RDF datatype property \texttt{:year} and \texttt{:attachment} are mapped onto the PG edge property \texttt{year} and \texttt{attachment}.
+The literal objects \texttt{2017} and \texttt{'01.pdf'} are mapped onto the edge property values.
 \end{itemize}
@@
    :receiver   :person2 ;
-   :year       2017 .
-   :attachment '01.pdf'
+   :year       2017 ;
+   :attachment '01.pdf' .
 \end{verbatim}
@@
 (p1:person)-[:emailed {year:y, attachment:a}]->(p2:person)
-    ?f a :Email
+    ?f a :Email ;
        :sender   ?p1 ;
@@
 \includegraphics[width=0.5\textwidth]{pg_example5.png}
-\caption{Visualization of Figure 5}
+\caption{Example of output PG data (Visualization)}
 \label{fig:pg_example5}
@@
 The relationships are originally presented as independent resources \texttt{?g}.
-In the mapping, we map \texttt{?g}, \texttt{?n}, and \texttt{?s} onto a PG edge labeled 'same_group' with attributes.
+In the mapping, we map \texttt{?g}, \texttt{?n}, and \texttt{?s} onto a PG edge labeled \texttt{same\_group} with attributes.
 Such compaction by mapping is useful in many use cases, for example, when users are just interested in relationships between musicians.
@@
 \section{Availability}
-The prototype implementation is written in JavaScript and can be executed using Node.js in the command line.
+The prototype implementation of G2G mapping is written in JavaScript and can be executed using Node.js in the command line.
 It has an endpoint mode and a local file mode.
@@
 
-Furthermore, a Docker image (\url{https://hub.docker.com/r/g2glab/g2g}) and a demonstration site of the G2G mapping framework (\url{http://g2g.fun}) are also available (Figure~\ref{fig:sandbox}).
+Furthermore, a Docker image (\url{https://hub.docker.com/r/g2glab/g2g}) and a demonstration site of the G2G mapping framework (\url{https://purl.org/g2gml}) are available (Figure~\ref{fig:sandbox}).
 

### 2020-08-19 paper.tex
Before submission

@@
 \newtheorem*{prel}{Preliminaries}
+
 %
@@
 
-\setlength\abovecaptionskip{-0.5ex}
+\setlength\abovecaptionskip{0ex}
 % First names are abbreviated in the running head.
@@
 
-In the light of this situation, developing a method to transform RDF into PG would be highly valuable. One of the practical issues faced by this challenge is the lack of a standardized PG model.
+In light of this situation, developing a method to transform RDF into PG would be highly valuable. One of the practical issues faced by this challenge is the lack of a standardized PG model.
 Another issue is that the transformation between RDF and PG is not straightforward due to the differences in their models. 
@@
 For the purpose of interoperability, we incorporate differences in PG models, taking into consideration multiple labels or property values for nodes and edges, as well as mixed graphs with both directed and undirected edges.
-The PG model we redefine here requires the following characteristics:
+The PG model that is redefined here requires the following characteristics:
 
@@
 
-The PG format has the following characteristics. An example is given in Figure~\ref{fig:example-pg}, which is visualized in Figure~\ref{fig:pg_example5}.
+The PG format has the following characteristics. An example is given in Figure~\ref{fig:example-pg}, which is visualized in Figure~\ref{fig:pg_example_vis}.
 
@@
 More formally, we describe the PG format in the EBNF notation as follows.
-
+\vspace{1ex}
 \begin{defi}[EBNF notation of the PG format]
@@
 According to this definition, each property value of PGs is a set of items of any datatype.
-Meanwhile, our G2G mapping prototype implementation currently supports the main three datatypes (integer, double, and string) as property value, and those types are inferred from the format of serialized values.
+Meanwhile, our G2G mapping prototype implementation currently supports the three main datatypes (integer, double, and string) as property values, and those types are inferred from the format of serialized values.
 
@@
 # EDGES
-101 -- 102  :same_school  :same_class  since:2012
-102 -> 101  :likes  since:2015
+101 -- 102  :same_school  :same_class  since:2002
+102 -> 101  :likes  since:2005
 \end{verbatim}
@@
 
-\subsection{Minimal Examples}
+\begin{figure}
+\center
+\includegraphics[width=0.9\textwidth]{fig3.png}
+\caption{Example of PG format (Visualization)}
+\label{fig:pg_example_vis}
+\end{figure}
+
+\subsection{Minimal Example}
 \label{subsec:minimal-examples}
-Figure~\ref{fig:example-g2g} shows the minimal example of G2G mapping from RDF to PG data, representing the following five types of typical mapping.
+Figure~\ref{fig:example-g2g} shows the minimal example of G2G mapping from RDF data (Figure~\ref{fig:example-rdf}) to PG data (Figure~\ref{fig:output-pg}), representing the following five types of typical mapping.
 
@@
 \caption{Example of output PG data}
-\label{fig:example-pg}
-\end{figure}
-
-\begin{figure}
-\center
-\includegraphics[width=0.5\textwidth]{pg_example5.png}
-\caption{Example of output PG data (Visualization)}
-\label{fig:pg_example5}
+\label{fig:output-pg}
 \end{figure}
@@
 When a pair of RDF resources has multiple relationships, those will be converted to multiple PG edges instead of a single PG edge with multiple properties.
-The G2GML in Figure~\ref{fig:example-g2g} generates two PG edges for the RDF data in Figure~\ref{fig:example-rdf2} to maintain the information that Alice emailed Bob twice.
+The G2GML in Figure~\ref{fig:example-g2g} generates two PG edges for the RDF data in Figure~\ref{fig:example-rdf2} to maintain the information that Alice emailed Bob twice (Figure~\ref{fig:example-pg2}).
 
@@
 In an RDF that includes the same data property multiple times, the values are assumed to be the members of a list.
-The G2GML in Figure~\ref{fig:example-g2g} generates one PG edge with two properties for the RDF data in Figure~\ref{fig:example-rdf3}, keeping the information that Alice emailed Bob once, and the email contained two attachments.
+The G2GML in Figure~\ref{fig:example-g2g} generates one PG edge with two properties for the RDF data in Figure~\ref{fig:example-rdf3}, keeping the information that Alice emailed Bob once, and the email contained two attachments (Figure~\ref{fig:example-pg3}).
 
@@
 In the mapping, we map \texttt{?g}, \texttt{?n}, and \texttt{?s} onto a PG edge labeled \texttt{same\_group} with attributes.
-Such compaction by mapping is useful in many use cases, for example, when users are just interested in relationships between musicians.
+Such compaction by mapping is useful in numerous use cases, for example, when users are interested only in relationships between musicians.
 
@@
 It has an endpoint mode and a local file mode.
-The local file mode uses Apache Jena ARQ to execute SPARQL queries internally, while the endpoint mode accesses SPARQL endpoints via the Internet.
+The local file mode uses Apache Jena ARQ to execute SPARQL queries internally, whereas the endpoint mode accesses SPARQL endpoints via the Internet.
 An example of the usage in the endpoint mode is as follows:
@@
 
-For the future adoption of this framework, we expect two scenarios: The use of the standalone G2G mapping tools, such as our implementation, for generating PG datasets from RDF resources.
-Also, the adoption of the framework within the database management systems which support both RDF and PG datasets.
+In future adoptions of this framework, we expect two scenarios: The use of the standalone G2G mapping tools, such as our implementation, for generating PG datasets from RDF resources.
+Further, the adoption of the framework within the database management systems, which support both RDF and PG datasets.
 
@@
 There is indeed a demand for graph standardization in the community, which was recently discussed in a W3C workshop~\cite{w3c}.
-Another proposal for the PG model and serialization~\cite{tomaszuk} that was similar to ours was presented in the workshop, and it is noteworthy that the two independent studies converged to a similar solution.
+Another proposal for the PG model and serialization~\cite{tomaszuk} that was similar to ours was presented in the workshop.
+Notably, that the two independent studies converged to a similar solution.
 They seem to be interchangeable; however, this remains to be tested.
@@
 They concluded that RDF has an advantage in terms of performance and interoperability.
-However, as PG model, they tested only Neo4j.
-It will be necessary to update such benchmarks using additional implementations, which requires improved interoperability and standardization of the PG model.
-Our study is expected to contribute to the improved interoperability of PG models, although a continuous discussion is necessary for the standardization of query language for the PG model, in order to achieve an interoperable ecosystem of both RDF and PG, and a fair benchmarking.
+However, they tested only Neo4j as an implementation of the PG model.
+It is necessary to update such benchmarks using additional implementations, which requires improved interoperability and standardization of the PG model.
+Our study is expected to contribute to the improved interoperability of PG models, although a continuous discussion is necessary for the standardization of query languages for the PG model to achieve an interoperable ecosystem of both RDF and PG, along with a fair benchmarking.
 
@@
 
-Various graph database implementations are actively developed and standardization of query languages is currently ongoing.
-We expect that the G2GML or its enhanced mapping framework will be supported by database management systems and other software.
+Various graph database implementations are actively developed and the standardization of query languages is currently ongoing.
+We expect the G2GML or its enhanced mapping framework to be supported by database management systems and other software.
 We believe that our efforts of generalization and prototype implementation will promote further discussion.
@@
 N., ...
-& Bizer, C.
-(2015).
-DBpedia–a large-scale, multilingual knowledge base extracted from Wikipedia.
-Semantic Web, 6(2), 167-195.
+& Bizer, C.: DBpedia–a large-scale, multilingual knowledge base extracted from Wikipedia.
+Semantic Web, 6(2), 167--195 (2015)
 
 \bibitem{wikidata}
-Vrandečić, D., & Krötzsch, M. (2014). Wikidata: a free collaborative knowledgebase. Communications of the ACM, 57(10), 78-85.
+Vrandečić, D., & Krötzsch, M.: Wikidata: a free collaborative knowledgebase. Communications of the ACM, 57(10), 78--85 (2014)
 
@@
 \bibitem{angles2}
-Angles, R., Arenas, M., Barceló, P., Hogan, A., Reutter, J., Vrgoc, D.: Foundations of Modern Query Languages for Graph Databases. ACM Computing Surveys (CSUR), 50(5), 68. (2017)
+Angles, R., Arenas, M., Barceló, P., Hogan, A., Reutter, J., Vrgoc, D.: Foundations of Modern Query Languages for Graph Databases. ACM Computing Surveys (CSUR), 50(5), 68 (2017)
+
+\bibitem{agri}
+Abad-Navarro, F., Bernabé-Diaz, J.
+A., García-Castro, A., & Fernandez-Breis, J.
+T.: Semantic Publication of Agricultural Scientific Literature Using Property Graphs.
+Applied Sciences, 10(3), 861 (2020)
 
@@
 
+\bibitem{openCypher}
+openCypher, \url{https://www.opencypher.org/}
+
 \bibitem{pgql}
@@
 In Proceedings of the 2018 International Conference on Management of Data, pp.
-1421--1432.
-(2018)
+1421--1432 (2018)
 
@@
 Tomaszuk D., Angles R., Szeremeta L., Litman K., Cisterna D.:
-Serialization for property graphs. International Conference: Beyond Databases, Architectures and Structures, pp. 57--69. (2019)
+Serialization for property graphs. International Conference: Beyond Databases, Architectures and Structures, pp. 57--69 (2019)
 
@@
 Angles, R., Thakkar, H., Tomaszuk, D.: RDF and Property Graphs Interoperability: Status and Issues.
-Proceedings of the 13th Alberto Mendelzon International Workshop on Foundations of Data Management.
-(2019)
+Proceedings of the 13th Alberto Mendelzon International Workshop on Foundations of Data Management (2019)
 
 \bibitem{das}
-Das, S., Srinivasan, J., Perry, M., Chong, E. I., Banerjee, J.: A Tale of Two Graphs: Property Graphs as RDF in Oracle. In EDBT, pp. 762--773. (2014)
+Das, S., Srinivasan, J., Perry, M., Chong, E. I., Banerjee, J.: A Tale of Two Graphs: Property Graphs as RDF in Oracle. In EDBT, pp. 762--773 (2014)
 
@@
 \bibitem{tomaszuk1}
-Tomaszuk, D.: RDF data in property graph model. In Research Conference on Metadata and Semantics Research, pp. 104--115. (2016)
+Tomaszuk, D.: RDF data in property graph model. In Research Conference on Metadata and Semantics Research, pp. 104--115 (2016)
 
@@
 T., Campbell, M.
-P., & Lisacek, F.
-(2015).
-Property graph vs RDF triple store: A comparison on glycan substructure search.
-PloS one, 10(12), e0144578.
+P., & Lisacek, F.: Property graph vs RDF triple store: A comparison on glycan substructure search.
+PloS one, 10(12), e0144578 (2015)
 
@@
 R2RML: RDB to RDF Mapping Language, W3C Recommendation 27 September 2012 \url{https://www.w3.org/TR/r2rml/}
-
-\bibitem{openCypher}
-openCypher, \url{https://www.opencypher.org/}
-
-\bibitem{agri}
-Abad-Navarro, F., Bernabé-Diaz, J.
-A., García-Castro, A., & Fernandez-Breis, J.
-T.
-(2020).
-Semantic Publication of Agricultural Scientific Literature Using Property Graphs.
-Applied Sciences, 10(3), 861.
 
